---
title: "<br> Role Playing Brain" 
subtitle: "Initial Analysis"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    # pdf_document: 
            # toc: true
            # toc_depth: 2
            # number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---


<!-- Setup -->


```{r setup, include=FALSE}
# General R options
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation
options(repos = c(getOption("repos")["CRAN"], CRANextra = "https://mirror.clientvps.com/CRAN/"))  # use CRAN as default, set CRANextra to Nürnberg mirror


if (!require("pacman")) install.packages("pacman", dependencies = TRUE)
packages <- c(
  "papaja",
  "here", "fs",
  "conflicted",
  "rio",
  "tidyverse", 
  "psych",          
  "rstatix", 
  "ggplot2", "ggpubr", "scales",
  "ggstatsplot", "report", 
  "ggstats", 
  "lmer4", "lmerTest", "merTools", "statAPA", "sjPlot"
  # , ...
)
pacman::p_load(char = packages)

# Set here to Rnotebook directory
here::set_here()
unloadNamespace("here")                   # need new R session or unload namespace for .here file to take precedence over .Rproj
notebook_name <- fs::path_file(here::here())

# Solve conflicts in favor of tidyverse
conflicted::conflict_prefer("filter", winner = "dplyr")
conflicted::conflict_prefer("select", winner = "dplyr")
conflicted::conflict_prefer("slice", winner = "dplyr")
conflicted::conflict_prefer("rename", winner = "dplyr")
conflicted::conflict_prefer("count", winner = "dplyr")

# Set kintr options including root.dir pointing to the .here file in Rnotebook directory
knitr::opts_chunk$set(
  root.dir = here::here(),
  #fig.width = 5, fig.asp = 1/3, 
  comment = "#",
  collapse = TRUE,
  echo = TRUE, warning = TRUE, message = TRUE, cache = TRUE       # echo = False for github_document, but will be folded in html_notebook
)

# Themes for ggplot2 plotting (here used APA style)
theme_set(papaja::theme_apa())
```




<!-- Functions -->

# Define functions

```{r}
## Define function that scores questionnaire items with proper NA handling
## Assumes data already has recoded columns ending with "_recode"
score_recoded <- function(data, 
                         original_cols = NULL,    # Original column names (without suffix)
                         suffix = "_recode",      # Suffix for recoded columns
                         reversecols = NULL,      # Original column names to reverse code
                         min = NULL,              # Minimum value for reverse coding
                         max = NULL,              # Maximum value for reverse coding
                         napercent = 0.1,         # Max proportion of NAs allowed per row
                         engine = "sum",          # "sum", "mean", or "mean_na"
                         verbose = TRUE) {
  
  require(tidyverse)
  
  # If original_cols not specified, detect all columns with the suffix
  if (is.null(original_cols)) {
    recoded_cols <- names(data)[str_detect(names(data), paste0(suffix, "$"))]
    if (length(recoded_cols) == 0) {
      stop(sprintf("No columns ending with '%s' found.", suffix))
    }
    # Extract original names
    original_cols <- str_remove(recoded_cols, suffix)
    if (verbose) {
      message(sprintf("Auto-detected %d recoded columns: %s", 
                      length(recoded_cols), 
                      paste(original_cols, collapse = ", ")))
    }
  }
  
  # Construct recoded column names
  recoded_cols <- paste0(original_cols, suffix)
  
  # Check which recoded columns exist
  existing_recoded <- recoded_cols[recoded_cols %in% names(data)]
  if (length(existing_recoded) == 0) {
    stop(sprintf("No recoded columns found with suffix '%s'.", suffix))
  }
  
  # Show which columns are missing
  missing_recoded <- recoded_cols[!recoded_cols %in% names(data)]
  if (length(missing_recoded) > 0 && verbose) {
    warning(sprintf("Missing recoded columns: %s", 
                    paste(missing_recoded, collapse = ", ")))
  }
  
  # Create working dataset with existing recoded columns
  df <- data %>% select(all_of(existing_recoded))
  
  # Check if data is numeric (should be, but just in case)
  non_numeric <- names(df)[!sapply(df, is.numeric)]
  if (length(non_numeric) > 0) {
    warning(sprintf("Non-numeric columns found: %s. Attempting to coerce.", 
                    paste(non_numeric, collapse = ", ")))
    df <- df %>%
      mutate(across(all_of(non_numeric), ~ as.numeric(as.character(.))))
  }
  
  # Handle reverse coding
  if (!is.null(reversecols)) {
    # Construct recoded names for reverse columns
    reverse_recoded <- paste0(reversecols, suffix)
    
    # Check which reverse columns exist in our working df
    reverse_existing <- reverse_recoded[reverse_recoded %in% names(df)]
    if (length(reverse_existing) == 0) {
      warning("No reverse coding columns found. Skipping reverse coding.")
    } else {
      # Extract original names for reporting
      reverse_original <- str_remove(reverse_existing, suffix)
      
      # Validate min and max
      if (is.null(min) || is.null(max)) {
        # Try to detect from data
        all_vals <- unlist(df[, reverse_existing], use.names = FALSE)
        detected_min <- min(all_vals, na.rm = TRUE)
        detected_max <- max(all_vals, na.rm = TRUE)
        
        if (is.null(min)) {
          min <- detected_min
          if (verbose) message(sprintf("Auto-detected min = %d", min))
        }
        if (is.null(max)) {
          max <- detected_max
          if (verbose) message(sprintf("Auto-detected max = %d", max))
        }
      }
      
      # Apply reverse coding
      if (verbose) {
        message(sprintf("Reverse coding %d items: %s", 
                        length(reverse_existing), 
                        paste(reverse_original, collapse = ", ")))
        message(sprintf("  Using min = %d, max = %d", min, max))
      }
      
      df[, reverse_existing] <- (max + min) - df[, reverse_existing]
    }
  }
  
  # Calculate scores based on engine
  if (engine == "sum") {
    # Sum scores, with NA handling based on napercent
    scores <- ifelse(
      rowSums(is.na(df)) > ncol(df) * napercent,
      NA,
      rowSums(df, na.rm = TRUE) * NA ^ (rowSums(!is.na(df)) == 0)
    )
    
    if (verbose) {
      message(sprintf("Scoring with engine = 'sum'"))
      message(sprintf("  Allowed NA proportion per row: %.1f%%", napercent * 100))
      message(sprintf("  Number of items: %d", ncol(df)))
      message(sprintf("  Score range: %.0f to %.0f", 
                      min(scores, na.rm = TRUE), 
                      max(scores, na.rm = TRUE)))
      message(sprintf("  Rows with all NAs: %d", sum(rowSums(!is.na(df)) == 0)))
    }
    
  } else if (engine == "mean") {
    # Mean scores, with NA handling
    scores <- ifelse(
      rowMeans(is.na(df)) > ncol(df) * napercent,
      NA,
      rowMeans(df, na.rm = TRUE) * NA ^ (rowSums(!is.na(df)) == 0)
    )
    
    if (verbose) {
      message(sprintf("Scoring with engine = 'mean'"))
      message(sprintf("  Allowed NA proportion per row: %.1f%%", napercent * 100))
      message(sprintf("  Number of items: %d", ncol(df)))
      message(sprintf("  Score range: %.2f to %.2f", 
                      min(scores, na.rm = TRUE), 
                      max(scores, na.rm = TRUE)))
      message(sprintf("  Rows with all NAs: %d", sum(rowSums(!is.na(df)) == 0)))
    }
    
  } else if (engine == "mean_na") {
    # Mean with NAs set to 0
    df_zero <- df
    df_zero[is.na(df_zero)] <- 0
    scores <- rowMeans(df_zero)
    
    if (verbose) {
      message(sprintf("Scoring with engine = 'mean_na' (NAs replaced with 0)"))
      message(sprintf("  Number of items: %d", ncol(df)))
      message(sprintf("  Score range: %.2f to %.2f", 
                      min(scores, na.rm = TRUE), 
                      max(scores, na.rm = TRUE)))
    }
    
  } else {
    stop("engine must be 'sum', 'mean', or 'mean_na'")
  }
  
  # Return scores as a vector
  return(scores)
}



################

# # Example usage in workflow:
# 
# # First, recode items
# df_q <- df_q %>%
#   recode_item_columns(columns = c("who_1", "who_2", "who_3", "who_4", "who_5"))
# 
# # Now use the scoring function directly on the recoded columns
# 
# # Example 1: Auto-detect all recoded columns (sum scores)
# df_q$who_total <- score_recoded(
#   data = df_q,
#   engine = "sum"
# )
# 
# # Example 2: Specify original columns explicitly
# df_q$who_mean <- score_recoded(
#   data = df_q,
#   original_cols = c("who_1", "who_2", "who_3", "who_4", "who_5"),
#   engine = "mean"
# )
# 
# # Example 3: With reverse coding (e.g., items 2 and 4 are reversed)
# df_q$who_total_rev <- score_recoded(
#   data = df_q,
#   original_cols = c("who_1", "who_2", "who_3", "who_4", "who_5"),
#   reversecols = c("who_2", "who_4"),
#   min = 1,
#   max = 5
# )
# 
# # Example 4: Mean with more permissive NA handling (allow 20% NAs)
# df_q$who_mean_liberal <- score_recoded(
#   data = df_q,
#   original_cols = c("who_1", "who_2", "who_3", "who_4", "who_5"),
#   engine = "mean",
#   napercent = 0.2
# )
# 
# # Example 5: Mean with NAs as 0
# df_q$who_mean_zero <- score_recoded(
#   data = df_q,
#   original_cols = c("who_1", "who_2", "who_3", "who_4", "who_5"),
#   engine = "mean_na"
# )
# 
# # Complete workflow with both functions
# df_q <- df_q %>%
#   # Step 1: Recode text to numeric codes
#   recode_item_columns(columns = c("who_1", "who_2", "who_3", "who_4", "who_5")) %>%
#   
#   # Step 2: Compute scores directly from recoded columns
#   mutate(
#     who_sum = score_recoded(., 
#                            original_cols = c("who_1", "who_2", "who_3", "who_4", "who_5"),
#                            engine = "sum",
#                            verbose = FALSE),
#     
#     who_mean = score_recoded(., 
#                             original_cols = c("who_1", "who_2", "who_3", "who_4", "who_5"),
#                             engine = "mean",
#                             verbose = FALSE),
#     
#     who_sum_rev = score_recoded(., 
#                                original_cols = c("who_1", "who_2", "who_3", "who_4", "who_5"),
#                                reversecols = c("who_2", "who_4"),
#                                min = 1,
#                                max = 5,
#                                verbose = FALSE)
#   )
```


```{r}
# Function that makes diagram for JSmediation::mdt_within_wide
library(DiagrammeR)  # For creating the diagram
library(dplyr)       # For data manipulation with %>% and filter
library(JSmediation) # For the mediation model and extract_tidy_models()

plot_withinmed <- function(mediation_model, 
                                 show_total_effect = TRUE,
                                 dv_name = "DV",
                                 m_name = "Mediator") {
  
  tidy_models <- extract_tidy_models(mediation_model)
  
  # Extract coefficients
  a <- tidy_models %>% filter(model == "1 -> M_diff", term == "(Intercept)") %>% pull(estimate) %>% .[1]
  a_p <- tidy_models %>% filter(model == "1 -> M_diff", term == "(Intercept)") %>% pull(p.value) %>% .[1]
  
  c <- tidy_models %>% filter(model == "1 -> DV_diff", term == "(Intercept)") %>% pull(estimate) %>% .[1]
  c_p <- tidy_models %>% filter(model == "1 -> DV_diff", term == "(Intercept)") %>% pull(p.value) %>% .[1]
  
  b <- tidy_models %>% filter(grepl("M_diff \\+ M_mean", model), term == "M_diff") %>% pull(estimate) %>% .[1]
  b_p <- tidy_models %>% filter(grepl("M_diff \\+ M_mean", model), term == "M_diff") %>% pull(p.value) %>% .[1]
  
  c_prime <- tidy_models %>% filter(grepl("M_diff \\+ M_mean", model), term == "(Intercept)") %>% pull(estimate) %>% .[1]
  c_prime_p <- tidy_models %>% filter(grepl("M_diff \\+ M_mean", model), term == "(Intercept)") %>% pull(p.value) %>% .[1]
  
  # Format in R first
  starify <- function(p) {
    case_when(
      p < 0.001 ~ "***",
      p < 0.01 ~ "**",
      p < 0.05 ~ "*",
      TRUE ~ ""
    )
  }
  
  a_fmt <- sprintf("%.2f", a)
  b_fmt <- sprintf("%.2f", b)
  c_prime_fmt <- sprintf("%.2f", c_prime)
  c_fmt <- sprintf("%.2f", c)
  
  a_sig <- starify(a_p)
  b_sig <- starify(b_p)
  c_prime_sig <- starify(c_prime_p)
  c_sig <- starify(c_p)
  
  # Build the total effect line
  total_line <- if(show_total_effect) {
    paste0('  IV -> DV [label = "c = ', c_fmt, c_sig, ' (total)", style = dashed]\n')
  } else {
    ""
  }
  
  # IMPORTANT: Use double quotes for the label with c'
  # The backslash before the single quote escapes it in DOT
  dot_string <- paste0(
    "digraph mediation {\n",
    "  graph [layout = dot, rankdir = LR]\n",
    "  node [shape = box, style = filled, fillcolor = lightblue]\n",
    "  \n",
    "  IV [label = \"Time\\n(pre/post)\"]\n",
    "  M [label = \"", m_name, "\"]\n",
    "  DV [label = \"", dv_name, "\"]\n",
    "  \n",
    "  IV -> M [label = \"a = ", a_fmt, a_sig, "\"]\n",
    "  M -> DV [label = \"b = ", b_fmt, b_sig, "\"]\n",
    "  IV -> DV [label = \"c\\' = ", c_prime_fmt, c_prime_sig, "\"]\n",  # ESCAPED c'
    total_line,
    "}"
  )
  
  # Debug: print the DOT string
  cat(dot_string)
  
  grViz(dot_string)
}

# Use it
# plot_withinmed(
#   mediation_model = withinmed_fluent_simp,
#   dv_name = "Prosocial\\nAttitudes",
#   m_name = "Role\\nPerspective"
# )
```



<!-- Report -->

# Data
## Read Full Dataset

```{r, echo=FALSE}
df <- readRDS(here::here("df_full.RDS"))

# framework::view(df)

```

## Some transformations & fixes

```{r}
# Recode Gender
df <-
  df %>% 
    mutate(Gender = as.factor(as.character(Gen))) %>%
    mutate(Gender = forcats::fct_recode(Gender, "female" = "f", "male" = "m"))

# Fix a mistake in IRI scoring: by accident iri_ec takes values of iri_pd and iti_pd isn't scored
# iri_ec = score_recoded(., original_cols = iri_cols[c(1,5,7,12,16,23,26)], engine = "sum", napercent = 0.1),
# iri_pt = score_recoded(., original_cols = iri_cols[c(3,8,11,15,21,25,28)], engine = "sum", napercent = 0.1),
# iri_f = score_recoded(., original_cols = iri_cols[c(2,4,9,14,18,20,22)], engine = "sum", napercent = 0.1),
# iri_ec = score_recoded(., original_cols = iri_cols[c(6,10,13,17,19,24,27)], engine = "sum", napercent = 0.1)
# Test first
iri_cols <- paste0("iri_", 1:28)
# df_test <-
#   df %>% 
#   mutate( # this still works on _recode columns!
#     iri_ec = score_recoded(., original_cols = iri_cols[c(1,5,7,12,16,23,26)], engine = "sum", napercent = 0.1),
#     iri_pt = score_recoded(., original_cols = iri_cols[c(3,8,11,15,21,25,28)], engine = "sum", napercent = 0.1),
#     iri_f = score_recoded(., original_cols = iri_cols[c(2,4,9,14,18,20,22)], engine = "sum", napercent = 0.1),
#     iri_pd = score_recoded(., original_cols = iri_cols[c(6,10,13,17,19,24,27)], engine = "sum", napercent = 0.1)
#   )
# all.equal(df_test$iri_pt, as.numeric(df$iri_pt))
# all.equal(df_test$iri_f, as.numeric(df$iri_f))
# all.equal(df_test$iri_pd, as.numeric(df$iri_ec))  # all good

df <-
  df %>% 
  mutate( # this still works on _recode columns!
    iri_ec = score_recoded(., original_cols = iri_cols[c(1,5,7,12,16,23,26)], engine = "sum", napercent = 0.1),
    iri_pt = score_recoded(., original_cols = iri_cols[c(3,8,11,15,21,25,28)], engine = "sum", napercent = 0.1),
    iri_f = score_recoded(., original_cols = iri_cols[c(2,4,9,14,18,20,22)], engine = "sum", napercent = 0.1),
    iri_pd = score_recoded(., original_cols = iri_cols[c(6,10,13,17,19,24,27)], engine = "sum", napercent = 0.1)
  )
```


# Demographics

## Gender

```{r}
## Pie chart
df %>%
  ggstatsplot::ggpiestats(., 
    x = Gender,
    label = "both",
    results.subtitle = FALSE,
    ggtheme = papaja::theme_apa(base_size = 14)
  )

## Test difference by Age
df %>% 
  ggstatsplot::ggbetweenstats(., 
    x = Gender,        
    y = Age,           
    type = "parametric",
    ggtheme = papaja::theme_apa(base_size = 14)
  )
```

## Age

```{r}
## Dodged Bar plot of Age and Gender
df %>%
  mutate(Age_categ = cut(Age, 
                           breaks=c(-Inf, 25, 30, 35, 40, 45, 50, 55, Inf), 
                           labels=c("<25","25-29","30-34", "35-39", "40-44", "45-49", "50-54", "55-60"), 
                           right = FALSE)) %>%  
  dplyr::count(Age_categ, Gender, .drop = FALSE) %>%         # Group by, then count number in each group (dont drop 0 counts)
  mutate(pct = prop.table(n)) %>%                           # Calculate percent within each var
    ggplot(aes(x = Age_categ, y = pct, fill = Gender, label = scales::percent(pct))) + 
      geom_col(position = position_dodge(preserve = "single"), stat = "identity",) +    # Don't drop zero count
      geom_text(position = position_dodge(width = .9),      # move to center of bars
                vjust = -0.5,                               # nudge above top of bar
                size = 3) + 
      scale_y_continuous(labels = scales::percent) +
      ggtitle("") +
      xlab("Age") + ylab("Percentage %") + 
      guides(fill = guide_legend(title = "Gender", ncol = 1)) + 
      scale_fill_grey(start = 0.8, end = 0.2, na.value = "red", aesthetics = "fill") +
      theme(legend.position = "right", legend.direction = "vertical", 
            legend.justification = c(0, 1), panel.border = element_rect(fill = NA, colour = "black"))
```

## Actor / Non-actor

```{r}
## Pie chart
df %>%
  ggstatsplot::ggpiestats(., 
    x = Group, 
    label = "both",
    results.subtitle = FALSE,
    ggtheme = papaja::theme_apa(base_size = 14)
  )

## Test difference by Gender
df %>%
  ggstatsplot::ggpiestats(., 
    x = Gender, 
    y = Group,
    label = "both",
    ggtheme = papaja::theme_apa(base_size = 14)
  )  

## Test difference by Age
df %>% 
  ggstatsplot::ggbetweenstats(., 
    x = Gender,        
    y = Age,           
    type = "parametric",
    ggtheme = papaja::theme_apa(base_size = 14)
  )
```



```{r}
# Info RPB: 
# ●	First-Person (1P): EU
# ●	First-Person Deception (1PD): EU – DISIMULARE
# ●	Familiar Third Person (Fam3P): EA/EL
# ●	Familiar First-Person (Fam1P): EU–EA/EL
# ●	Fictional First-Person (Fic1P): NOROC
# ●	Fictional First-Person (Fic2P): SHREK

# Define the mappings
number_to_label <- c(
  "1" = "persp",
  "2" = "skin",
  "3" = "satisf",
  "4" = "fluent",
  
  "5" = "persp",
  "6" = "skin",
  "7" = "satisf",
  "8" = "fluent",
  
  "9" = "persp",
  "10" = "skin",
  "11" = "satisf",
  "12" = "close",
  "13" = "simp",
  "14" = "fluent",
  
  "15" = "persp",
  "16" = "skin",
  "17" = "satisf",
  "18" = "close",
  "19" = "simp",
  "20" = "fluent",
  
  "21" = "persp",
  "22" = "skin",
  "23" = "satisf",
  "24" = "close",
  "25" = "simp",
  "26" = "fluent",
  
  "27" = "persp",
  "28" = "skin",
  "29" = "satisf",
  "30" = "close",
  "31" = "simp",
  "32" = "fluent"
)

number_to_condition <- c(
  "1" = "1P",
  "2" = "1P",
  "3" = "1P",
  "4" = "1P",
  
  "5" = "1PD",
  "6" = "1PD",
  "7" = "1PD",
  "8" = "1PD",
  
  "9" = "Fam3P",
  "10" = "Fam3P",
  "11" = "Fam3P",
  "12" = "Fam3P",
  "13" = "Fam3P",
  "14" = "Fam3P",
  
  "15" = "Fam1P",
  "16" = "Fam1P",
  "17" = "Fam1P",
  "18" = "Fam1P",
  "19" = "Fam1P",
  "20" = "Fam1P",
  
  "21" = "Fic1P",
  "22" = "Fic1P",
  "23" = "Fic1P",
  "24" = "Fic1P",
  "25" = "Fic1P",
  "26" = "Fic1P",
  
  "27" = "Fic2P",
  "28" = "Fic2P",
  "29" = "Fic2P",
  "30" = "Fic2P",
  "31" = "Fic2P",
  "32" = "Fic2P"
)

# Create a lookup for valid combinations
all_conditions <- unique(number_to_condition)
all_rpb_variables <- unique(number_to_label)

# All Questionnaire columns
all_scale_variables <- c("fried_total", "fried_es", "fried_sc", "fried_j", 
  "paq_total", 
  "who_total", 
  "sscs_total", "sscs_cse", "sscs_cpi", 
  "iri_ec", "iri_pt", "iri_f", "iri_pd", 
  "gfps_total", 
  "sair_vig", "sair_fre", "sair_inv", 
  "apts_total", "apts_fun", "apts_uni", "apts_spo", 
  "bdi_total", "stai_total", "aps_total", "pss_total")
```


# Questionnaires

1. WHO-5 Well being 
2. SSCS – Creative Self Scale  
  Creative Self-efficacy (CSE)
  Creative Personal Identity (CPI)
  Total
3. IRI – Interpersonal Reactivity Index
  Empathic Concern (EC)
  Perspective-Taking (PT)
  Fantasy (FS)
  Personal Distress (PD)
4. GFPS - The General Flow Proneness Scale
5. SAI-R - Revised Spontaneity Assessment Inventory   
  Vigor/Pleasure
  Freedom
  Involvement/Focus
6. APTS - Adult Playfulness Trait Scale    
  Fun-seeking Motivation
  Uninhibitedness
  Spontaneity
  Total
7. BDI II – Beck Depression Inventory                
8. STAI trait - The State-Trait Anxiety Inventory  
9. APS – Adult Prosocialness Scale
10. PSS10 - perceived stress Scale
11. Friedman well-being scale 
  Emotional Stability
  Self-Confidence 
  Joyfulness 
  Total
12. Performance Anxiety Questionnaire (PAQ)

## Distributions

```{r, results = "asis"}
library(summarytools)

summary <- df %>%
  select(all_of(all_scale_variables)) %>%
  dfSummary(
    plain.ascii = FALSE,
    style = "grid",
    tmp.img.dir = "tmp",  # Short name
    varnumbers = FALSE,
    valid.col = FALSE
  )

# Save as HTML file
print(summary, method = "render")

# surveyexplorer
```

## Compare groups

```{r, results = "asis", fig.keep = "all"}
# Generate all plots
plot_list <- list()
for (i in all_scale_variables) {
  plot_list[[i]] <- df %>% 
    ggstatsplot::ggbetweenstats(
      x = Group,
      y = !!sym(i),  
      type = "parametric",
      ggtheme = papaja::theme_apa(base_size = 14)
    )
}
```

```{r}
# Display parts
for (i in names(plot_list)[1:9]) {
  print(plot_list[[i]])
}
```

```{r}
# Display parts
for (i in names(plot_list)[9:17]) {
  print(plot_list[[i]])
}
```
```{r}
# Display parts
for (i in names(plot_list)[18:25]) {
  print(plot_list[[i]])
}

rm(plot_list)
```


# RPB

## Correlations in day 3

```{r, fig.width=12}
df %>% 
  select(ID, 
         all_of(grep("day3_(1P|1PD)_(persp_S|satisf_S|fluent_S)", names(df), value = TRUE))
  ) %>% 
  pivot_longer(
    cols = -ID,
    names_to = "Variable",
    values_to = "Value"
  ) %>% 
  extract(Variable, 
          into = c("Day", "Condition", "Measure"), 
          regex = "(day3)_(1P|1PD)_(persp_S|satisf_S|fluent_S)",
          remove = FALSE) %>% 
  pivot_wider(
    id_cols = c(ID, Condition),
    names_from = Measure,
    values_from = Value
  ) %>% 
  grouped_ggcorrmat(
    data = .,
    grouping.var = Condition,
    type = "parametric",
    colors = c("#cbac43", "white", "#550000"),
    p.adjust.method = "fdr",
    matrix.type = "lower"
  )

```


```{r, fig.height=12, fig.width=12}
df %>% 
  select(ID, 
         all_of(grep("day3_(Fam3P|Fam1P|Fic1P|Fic2P)_(persp_S|satisf_S|fluent_S|close_S|simp_S)", names(df), value = TRUE))
  ) %>% 
  pivot_longer(
    cols = -ID,
    names_to = "Variable",
    values_to = "Value"
  ) %>% 
  extract(Variable, 
          into = c("Day", "Condition", "Measure"), 
          regex = "(day3)_(Fam3P|Fam1P|Fic1P|Fic2P)_(persp_S|satisf_S|fluent_S|close_S|simp_S)",
          remove = FALSE) %>% 
  pivot_wider(
    id_cols = c(ID, Condition),
    names_from = Measure,
    values_from = Value
  ) %>% 
  grouped_ggcorrmat(
    data = .,
    grouping.var = Condition,
    type = "parametric",
    colors = c("#cbac43", "white", "#550000"),
    p.adjust.method = "fdr",
    matrix.type = "lower"
  )
```


## Within-participant mediation


Checked for 3rd Persons:
ns for Simp -> Fluent 
ns for Simp -> Satisf

interesting for Close -> Fluent 
ns for Close -> Satisf


```{r}
library(JSmediation)

## Model for single analysis:
# withinmed_fluent_simp <- 
#   JSmediation::mdt_within_wide(data = df, 
#                   DV_A = day1_Fic1P_fluent_S, DV_B = day3_Fic1P_fluent_S, 
#                   M_A = day1_Fic1P_simp_S, M_B = day3_Fic1P_simp_S)
# JSmediation::add_index(withinmed_fluent_simp)
# plot_withinmed(
#   mediation_model = withinmed_fluent_simp,
#   dv_name = "DV\\nFluency",
#   m_name = "Med\\nSimpathy"
# )

withinmed_fluent_close <-
  JSmediation::mdt_within_wide(data = df,
                  DV_A = day1_Fam3P_fluent_S, DV_B = day3_Fam3P_fluent_S,
                  M_A = day1_Fam3P_close_S, M_B = day3_Fam3P_close_S)
JSmediation::add_index(withinmed_fluent_close)
plot_withinmed(
  mediation_model = withinmed_fluent_close,
  dv_name = "DV\\nFluency",
  m_name = "Med\\nCloseness"
)

withinmed_fluent_close <-
  JSmediation::mdt_within_wide(data = df,
                  DV_A = day1_Fam1P_fluent_S, DV_B = day3_Fam1P_fluent_S,
                  M_A = day1_Fam1P_close_S, M_B = day3_Fam1P_close_S)
JSmediation::add_index(withinmed_fluent_close)
plot_withinmed(
  mediation_model = withinmed_fluent_close,
  dv_name = "DV\\nFluency",
  m_name = "Med\\nCloseness"
)

withinmed_fluent_close <-
  JSmediation::mdt_within_wide(data = df,
                  DV_A = day1_Fic1P_fluent_S, DV_B = day3_Fic1P_fluent_S,
                  M_A = day1_Fic1P_close_S, M_B = day3_Fic1P_close_S)
JSmediation::add_index(withinmed_fluent_close)
plot_withinmed(
  mediation_model = withinmed_fluent_close,
  dv_name = "DV\\nFluency",
  m_name = "Med\\nCloseness"
)

withinmed_fluent_close <-
  JSmediation::mdt_within_wide(data = df,
                  DV_A = day1_Fic2P_fluent_S, DV_B = day3_Fic2P_fluent_S,
                  M_A = day1_Fic2P_close_S, M_B = day3_Fic2P_close_S)
JSmediation::add_index(withinmed_fluent_close)
plot_withinmed(
  mediation_model = withinmed_fluent_close,
  dv_name = "DV\\nFluency",
  m_name = "Med\\nCloseness"
)
```

Checked all conditions:
only some :( for Persp -> Fluent
not interesting at all for Persp -> Satisf

interesting for Fluent -> Satisf

```{r, results = "asis"}
# Model for looping conditions
# for (cond in all_conditions) {
#   cat("\n========== Cond:", cond, "==========\n")
#   
#   dv_A <- sym(paste0("day1_", cond, "_persp_S"))
#   dv_B <- sym(paste0("day3_", cond, "_persp_S"))
#   m_A <- sym(paste0("day1_", cond, "_satisf_S"))
#   m_B <- sym(paste0("day3_", cond, "_satisf_S"))
#   
#   tryCatch({
#     print(add_index(mdt_within_wide(
#       data = df,
#       DV_A = !!dv_A,
#       DV_B = !!dv_B,
#       M_A = !!m_A,
#       M_B = !!m_B
#     )))
#   }, error = function(e) {
#     cat("Error:", e$message, "\n")
#   })
# }


for (cond in all_conditions) {
  cat("\n========== Cond:", cond, "==========\n")

  dv_A <- sym(paste0("day1_", cond, "_satisf_S"))
  dv_B <- sym(paste0("day3_", cond, "_satisf_S"))
  m_A <- sym(paste0("day1_", cond, "_fluent_S"))
  m_B <- sym(paste0("day3_", cond, "_fluent_S"))

  tryCatch({
    print(add_index(mdt_within_wide(
      data = df,
      DV_A = !!dv_A,
      DV_B = !!dv_B,
      M_A = !!m_A,
      M_B = !!m_B
    )))
  }, error = function(e) {
    cat("Error:", e$message, "\n")
  })
}
```

# Questionnaires & RPB


```{r, fig.height=12, fig.width=12}
# APTS/sai-r/depresie/anxietate si satisfacție si respectiv fluența, preluare perspectiva
# subscala de imersie din IRI si preluare perspectiva

person_vars <- c("iri_pt", "iri_f", "sair_vig", "sair_fre", "sair_inv", 
                 "apts_total", "apts_fun", "apts_uni", "apts_spo", 
                 "bdi_total", "stai_total")

condition_vars <- grep("day3_(1P|1PD|Fam3P|Fam1P|Fic1P|Fic2P)_(persp_S|satisf_S|fluent_S)", 
                       names(df), value = TRUE)

# Select and reshape
df_long <- df %>%
  select(ID, all_of(person_vars), all_of(condition_vars)) %>%
  pivot_longer(
    cols = all_of(condition_vars),  # Only reshape condition-varying variables
    names_to = "Variable",
    values_to = "Value"
  ) %>%
  extract(Variable, 
          into = c("Day", "Condition", "Measure"), 
          regex = "(day3)_(1P|1PD|Fam3P|Fam1P|Fic1P|Fic2P)_(persp_S|satisf_S|fluent_S)",
          remove = FALSE) %>%
  pivot_wider(
    id_cols = c(ID, Condition, all_of(person_vars)),  # Include person-level vars
    names_from = Measure,
    values_from = Value
  )

# Now use in grouped_ggcorrmat
plot_cor_list <- list()

for (i in seq_along(person_vars)) {
plot_cor_list[[i]] <-  
  df_long %>%
    select(ID, Condition, all_of(person_vars[i]), persp_S, satisf_S, fluent_S) %>% 
    grouped_ggcorrmat(
      data = .,
      grouping.var = Condition,
      type = "parametric",
      colors = c("#cbac43", "white", "#550000"),
      p.adjust.method = "fdr",
      matrix.type = "lower"
    )
}  
```

```{r, fig.height=8, fig.width=12}
# Display 
# for (i in seq_along(plot_cor_list)) {
#   print(plot_cor_list[[i]])
# }

print(plot_cor_list[[3]])
```

```{r, fig.height=8, fig.width=12}
print(plot_cor_list[[5]])

rm(plot_cor_list)
```





<!-- Session Info and License -->

<br>

# Session Info
```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->
&nbsp;
<hr />
<p style="text-align: center;">A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a></p>
<p style="text-align: center;"><span style="color: #808080;"><em>claudiu.papasteri@gmail.com</em></span></p>
&nbsp;
