---
title: "<br> Drama Exercises" 
subtitle: "Cinetic Summer School"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    # word_document        
    # pdf_document: 
            # toc: true
            # toc_depth: 2
            # number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---


<!-- Setup -->


```{r setup, include=FALSE}
# kintr options
knitr::opts_chunk$set(
  comment = "#",
  collapse = TRUE,
  echo = TRUE, warning = FALSE, message = TRUE, cache = TRUE       # echo = False for github_document, but will be folded in html_notebook
)

# General R options and info
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation

# Load packages
if (!require("pacman")) install.packages("pacman")
packages <- c(
  "papaja",
  "tidyverse", "plyr",      
  "psych", "PerformanceAnalytics",          
  "broom", "rstatix",
  "summarytools", "tadaatoolbox",           
  "ggplot2", "ggpubr", "scales",        
  "rio"
  # , ...
)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(char = packages)

# Themes for ggplot2 ploting (here used APA style)
theme_set(theme_apa())


# Tables knitting to Word
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')  # then format tables using an if statement like:
# if (doc.type == "docx") { pander::pander(df) } else { knitr::kable(df) }
```





<!-- Report -->


# Read, Clean, Recode, Merge

```{r red_clean_recode_merge, results='hide'}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Read, Clean, Recode, Unite
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

## Read files
folder <- "E:/Cinetic idei noi/Cinetic elevi"
file <- "A13 Tabel 3.xlsx"

setwd(folder)
Data <- rio::import(file.path(folder, file),
                           skip = 1)

## Tidy up data
# Function coalesce rows: colapse when NA, unite with "_" when not NA
coalesce2 <- function(...) {
  Reduce(function(x, y) {
    i <- which(is.na(x))
    j <- which(!is.na(x) & !is.na(y))
    x[i] <- y[i]
    x[j] <- paste(x[j], y[j], sep = "_")
    x},
    list(...))
}

colnames(Data) <- coalesce2(Data[2,], Data[3,])
Data <- Data[-c(1:3),]


## Check duplicate column names due to excel
tibble::enframe(names(Data)) %>% 
  dplyr::count(value) %>% 
  dplyr::filter(n > 1)

## Make valid column names (no duplicates)
validate.names = function(df){
  rtn = df
  valid_column_names = make.names(names = names(df), unique = TRUE, allow_ = TRUE)
  names(rtn) = valid_column_names
  rtn
}

Data <- 
  Data %>% 
  validate.names() %>%                                       # make.names()
  rename_all(~stringr::str_replace_all(., "\\.", "_"))       # make.names() uses ".", change to "_"

## Delete columns with only NA
Data <-
  Data %>%
  select_if(~!(all(is.na(.)) | all(. == "")))


## Rename columns corresponding to items
# Function to paste a string before column name if it doesnt already start with that string
paste_tocolnames <- function(vec_colnames, string_paste){
  ind <- grep(pattern = string_paste, vec_colnames)                   # ignore column that already has string patterm
  vec_colnames[-ind] <- paste0(string_paste, vec_colnames[-ind])      # paste pattern to the rest of them
  return(vec_colnames)
}

colnames(Data)[6:25] <- paste_tocolnames(colnames(Data)[6:25], "PANAS_pre_")
colnames(Data)[61:64] <- paste_tocolnames(colnames(Data)[61:64], "SRS_post_")
colnames(Data)[65:84] <- paste_tocolnames(colnames(Data)[65:84], "PANAS_post_")

Data <- 
  Data %>% 
  rename_all(~stringr::str_replace_all(., "_\\d", ""))              # delete pattern "_1" that was introduced for duplicate column names

colnames(Data) <- enc2native(colnames(Data))      # fix encoding


## Recode known missing values
# str(Data_psiho, list.len = ncol(Data_psiho))
# str(Data_psiho, list.len = ncol(Data_psiho))
Data <-
  Data %>%
  replace(. == "/", NA) %>%                                     # missing values are coded "/"
  replace(. == "-", NA) %>%                                     # missing values are coded "-"
  replace(. == "NA", NA)                                        # missing values are coded "NA"


## Check for non-numeric elements in data sets
check_numeric1 <- as.data.frame(sapply(Data, varhandle::check.numeric)) 
# sapply(check_numeric1, function(x) length(which(!x)))     # look at columns with non-numeric and count of non-numeric values

nonnumeric1 <- sapply(check_numeric1, function(x) which(!x, arr.ind = TRUE))    # find row numbers for non-numeric values
nonnumeric1[lapply(nonnumeric1, length) > 0]                                   # return only columns and rown numbers were non-numeric

## Recode to numeric
Data <- 
  Data %>% 
  mutate_at(vars(6:84), funs(as.numeric(as.character(.))))  

## Recode ID 
Data <-
  Data %>%
  dplyr::rename(ID = `Indica_tiv_subiect`) 

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Scoring Questionnaires
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## Define function that calculates RowSums but only for rows with less than 10% NAs; and return NA if all row values are NA 
SpecialRowSums <- function(df, napercent = .1) {
  ifelse(rowSums(is.na(df)) > ncol(df) * napercent,
         NA,
         rowSums(df, na.rm = TRUE) * NA ^ (rowSums(!is.na(df)) == 0)
  )
}

## --  APS NOT ADMINISTERED --
## APS: simple sum 
# Data_teatru$`APS pre_Total` <- SpecialRowSums(Data_teatru[ ,sprintf("APS pre_%d", 1:16)], napercent = .13)  # not more than 2 NAs for 16 items
# Data_teatru$`APS post_Total` <- SpecialRowSums(Data_teatru[ ,sprintf("APS post_%d", 1:16)], napercent = .13)

## --  PSS NOT ADMINISTERED --
## PSS-SF 14: Items 4, 5, 6, 7, 9, 10, and 13 are scored in reverse direction.
# keys_PSS <- c(1,1,1,-1,-1,-1,-1,1,-1,-1,1,1,-1,1)
# 
# Data_teatru$`PPS pre_Total` <- 
#   SpecialRowSums(
#   psych::reverse.code(items = Data_teatru[ ,sprintf("PPS pre_%d", 1:14)], keys = keys_PSS,  mini = 0, maxi = 4),
#   napercent = .1)  # not more than 1 NAs for 14 items 
# Data_teatru$`PPS post_Total` <- 
#   SpecialRowSums(
#     psych::reverse.code(items = Data_teatru[ ,sprintf("PPS post_%d", 1:14)], keys = keys_PSS,  mini = 0, maxi = 4),
#     napercent = .1)


## PANAS: Positive Affect Score = sum items 1, 3, 5, 9, 10, 12, 14, 16, 17, 19. Negative Affect Score = sum items 2, 4, 6, 7, 8, 11, 13, 15, 18, 20.
Data$PA_pre_Total <- SpecialRowSums(Data[ ,5 + c(1,3,5,9,10,12,14,16,17,19)], napercent = .11) # not more than 1 NAs for 10 items
Data$NA_pre_Total <- SpecialRowSums(Data[ ,5 + c(2,4,6,7,8,11,13,15,18,20)], napercent = .11)

Data$PA_post_Total <- SpecialRowSums(Data[ ,64 + c(1,3,5,9,10,12,14,16,17,19)], napercent = .11) 
Data$NA_post_Total <- SpecialRowSums(Data[ ,64 + c(2,4,6,7,8,11,13,15,18,20)], napercent = .11)


## Make data frames for Etapa III and IV
Data_III <- subset(Data, Etapa == "III")
Data_IV <- subset(Data, Etapa == "IV")
```


# Sample descriptives

```{r sample_desc}
cat("## Number of subjects")
Data %>% 
 dplyr::summarise(count = dplyr::n_distinct(ID))

cat("## Number of subjects by Etapa")
Data %>%
 group_by(Etapa) %>%
 dplyr::summarise(count = dplyr::n_distinct(ID))
```


# Define Funtion for Pre-Post Comparison

```{r func_wilcox}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~   OUTCOMES PRE-POST INTERVENTION   ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## Function to run for diffrent dataframes (in this case: Etapa III and Iv)
## Func wilcox, t test & simple boxplot
func_wilcox_box <- function(df, ind, pre_var, post_var){
  df_modif <-
    df %>%
    select(ind, pre_var, post_var) %>% 
    tidyr::drop_na() %>%
    gather(pre_var, post_var, key = "Cond", value = "value") %>% 
    mutate_at(vars(c(1, 2)), funs(as.factor)) %>% 
    mutate(Cond = factor(Cond, levels = c(pre_var, post_var))) 
  
  stat_comp <- ggpubr::compare_means(value ~ Cond, data = df_modif, method = "wilcox.test", paired = TRUE)
  
  stat_comp2 <-
    df_modif %>% 
    do(tidy(t.test(.$value ~ .$Cond,
                   paired = TRUE,
                   data=.)))
  
  plot <- 
    ggpubr::ggpaired(df_modif, x = "Cond", y = "value", id = ind, 
                     color = "Cond", line.color = "gray", line.size = 0.4,
                     palette = c("#00AFBB", "#FC4E07"), legend = "none") +
      stat_summary(fun.data = mean_se,  colour = "darkred") +
      ggpubr::stat_compare_means(method = "wilcox.test", paired = TRUE, label.x = as.numeric(df_modif$Cond)-0.4, label.y = max(df_modif$value)+4) + 
      ggpubr::stat_compare_means(method = "wilcox.test", paired = TRUE, label = "p.signif", comparisons = list(c(pre_var, post_var)))
  
  cat(paste0("#### ", pre_var, " ", post_var, "\n", "\n"))
  print(stat_comp)
  print(stat_comp2)
  print(plot)
}
```

# IOS
## IOS Pre-Post Intervention - Whole Sample

```{r ios_wholesample, fig.width=6, fig.align='center', fig.height=8, results='asis'}
## Run function func_wilcox_box() on whole sample
func_wilcox_box(Data, "ID", "IOS_pre", "IOS_post") 
```


## IOS Pre-Post Intervention for each Etapa

```{r ios_etapa, fig.width=6, fig.align='center', fig.height=8, results='asis'}
## Run function func_wilcox_box() for Etapa III
cat("### Etapa III")
func_wilcox_box(Data_III, "ID", "IOS_pre", "IOS_post") 

## Run function for func_wilcox_box() Etapa IV
cat("### Etapa IV")
func_wilcox_box(Data_IV, "ID", "IOS_pre", "IOS_post") 
```

# PANAS
## PANAS Pre-Post Intervention - Whole Sample

```{r panas_wholesample, fig.width=6, fig.align='center', fig.height=8, results='asis'}
## Run function func_wilcox_box() on whole sample
func_wilcox_box(Data, "ID", "PA_pre_Total", "PA_post_Total") 
func_wilcox_box(Data, "ID", "NA_pre_Total", "NA_post_Total") 
```


## PANAS Pre-Post Intervention for each Etapa

```{r panas_etapa, fig.width=6, fig.align='center', fig.height=8, results='asis'}
## Run function func_wilcox_box() for Etapa III
cat("### Etapa III")
func_wilcox_box(Data_III, "ID", "PA_pre_Total", "PA_post_Total") 
func_wilcox_box(Data_III, "ID", "NA_pre_Total", "NA_post_Total") 

## Run function for func_wilcox_box() Etapa IV
cat("### Etapa IV")
func_wilcox_box(Data_IV, "ID", "PA_pre_Total", "PA_post_Total") 
func_wilcox_box(Data_IV, "ID", "NA_pre_Total", "NA_post_Total")
```


# VAS variables for Etapa III

```{r vas_variables_etapa3, fig.width=15, fig.height=12, results='asis'}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~   Variables multiple measurements in zi    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## Function plot pre-ex1-ex2-..-post data for Etapa III
plot_preexpost_ex <- function(df, pre_var, post_x1_var, post_x2_var, post_x3_var, post_x4_var, post_x5_var, post_x6_var){
  df_modif <-
    df %>%
    gather(pre_var, post_x1_var, post_x2_var, post_x3_var, post_x4_var, post_x5_var, post_x6_var, key = "variable", value = "value") %>%
    mutate(variable = factor(variable, levels = c(pre_var, post_x1_var, post_x2_var, post_x3_var, post_x4_var, post_x5_var, post_x6_var)))
    
  # Wilcox test
  stat.test1 <-
    df_modif %>%
    # group_by(Etapa) %>%                             # no need .. going by Etapa separatly
    tidyr::drop_na(value) %>%                                 # filter so grouping factor levels get droped and we can compare with uneven levels
    rstatix::wilcox_test(value ~ variable) %>%                # pairwise
    rstatix::add_significance("p") %>%
    filter(p.signif != "ns")
  
  # t test
  stat.test2 <-
    df_modif %>%
    # group_by(Etapa) %>%                                # no need .. going by Etapa separatly
    tidyr::drop_na(value) %>%                                 # filter so grouping factor levels get droped and we can compare with uneven levels
    rstatix::t_test(value ~ variable) %>%                # pairwise
    rstatix::add_significance("p") %>%                                    
    filter(p.signif != "ns") 
  
  p<-
    ggplot(df_modif, aes(y = value, x = variable)) +
      # facet_wrap(~Etapa, nrow = 1) +                     # no need .. going by Etapa separatly
      ggtitle(deparse(substitute(df))) + 
      geom_boxplot() + stat_summary(fun.data = mean_se,  colour = "darkred") +
      theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
      ggpubr::stat_pvalue_manual(stat.test1, label = "p.signif",
                         y.position = seq(max(df_modif$value, na.rm = TRUE)+2, max(df_modif$value, na.rm = TRUE)*2,
                                          length.out = nrow(stat.test1)))                                                  # very hacky
  cat("#### Wilcoxon test")
  return(stat.test1) %>% print(n = Inf)
  cat("#### t test")
  return(stat.test2) %>% print(n = Inf)
  p
}


cat("## VAS stres")                # names(Data[, grep("VAS_stres", names(Data))])
plot_preexpost_ex(Data_III, 
                  "VAS_stres_pre", "VAS_stres_post_ex1", 
                  "VAS_stres_post_ex2", "VAS_stres_post_ex3",
                  "VAS_stres_post_ex4", "VAS_stres_post_ex5", "VAS_stres_post_ex6")


cat("## VAS stare de bine")       # names(Data[, grep("VAS_stare_de", names(Data))])
plot_preexpost_ex(Data_III,
                  "VAS_stare_de_bine_pre", "VAS_stare_de_bine_post_ex1", 
                  "VAS_stare_de_bine_post_ex2", "VAS_stare_de_bine_post_ex3",
                  "VAS_stare_de_bine_post_ex4", "VAS_stare_de_bine_post_ex5", "VAS_stare_de_bine_post_ex6")


cat("## VAS corp")                # names(Data[, grep("VAS_corp", names(Data))])
plot_preexpost_ex(Data_III, 
                  "VAS_corp_pre", "VAS_corp_post_ex1",
                  "VAS_corp_post_ex2", "VAS_corp_post_ex3",
                  "VAS_corp_post_ex4", "VAS_corp_post_ex5", "VAS_corp_post_ex6")
```


# VAS variables for Etapa IV

```{r vas_variables_etapa4, fig.width=6, fig.height=8, results='asis'}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~   Variables multiple measurements in zi    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## Function plot pre-ex1-ex2-..-post data for Etapa III
plot_preexpost_ex4 <- function(df, pre_var, post_x1_var, post_x2_var){
  df_modif <-
    df %>%
    gather(pre_var, post_x1_var, post_x2_var, key = "variable", value = "value") %>%
    mutate(variable = factor(variable, levels = c(pre_var, post_x1_var, post_x2_var)))
    
  # Wilcox test
  stat.test1 <-
    df_modif %>%
    # group_by(Etapa) %>%                             # no need .. going by Etapa separatly
    tidyr::drop_na(value) %>%                                 # filter so grouping factor levels get droped and we can compare with uneven levels
    rstatix::wilcox_test(value ~ variable) %>%                # pairwise
    rstatix::add_significance("p") %>%
    filter(p.signif != "ns")
  
  # t test
  stat.test2 <-
    df_modif %>%
    # group_by(Etapa) %>%                                # no need .. going by Etapa separatly
    tidyr::drop_na(value) %>%                                 # filter so grouping factor levels get droped and we can compare with uneven levels
    rstatix::t_test(value ~ variable) %>%                # pairwise
    rstatix::add_significance("p") %>%                                    
    filter(p.signif != "ns") 
  
  p <-
    ggplot(df_modif, aes(y = value, x = variable)) +
      # facet_wrap(~Etapa, nrow = 1) +                     # no need .. going by Etapa separatly
      ggtitle(deparse(substitute(df))) + 
      geom_boxplot() + stat_summary(fun.data = mean_se,  colour = "darkred") +
      theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
  
  if(dim(stat.test1)[1] != 0) {     # do this only if the significance dataframe has > 0 rows
    p <- 
      p +
      ggpubr::stat_pvalue_manual(stat.test1, label = "p.signif",
                         y.position = seq(max(df_modif$value, na.rm = TRUE)+2, max(df_modif$value, na.rm = TRUE)*2,
                                          length.out = nrow(stat.test1)))                                                  # very hacky
  }
  
  cat("#### Wilcoxon test")
  return(stat.test1) %>% print(n = Inf)
  cat("#### t test")
  return(stat.test2) %>% print(n = Inf)
  p
}


cat("## VAS stres")                # names(Data[, grep("VAS_stres", names(Data))])
plot_preexpost_ex4(Data_IV, 
                  "VAS_stres_pre", "VAS_stres_post_ex1", "VAS_stres_post_ex2")


cat("## VAS stare de bine")       # names(Data[, grep("VAS_stare_de", names(Data))])
plot_preexpost_ex4(Data_IV,
                  "VAS_stare_de_bine_pre", "VAS_stare_de_bine_post_ex1", "VAS_stare_de_bine_post_ex2")


cat("## VAS corp")                # names(Data[, grep("VAS_corp", names(Data))])
plot_preexpost_ex4(Data_IV, 
                  "VAS_corp_pre", "VAS_corp_post_ex1", "VAS_corp_post_ex2")
```




<br>





<!-- Session Info and License -->

<br>

# Session Info
```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->
&nbsp;
<hr />
<p style="text-align: center;">A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a></p>
<p style="text-align: center;"><span style="color: #808080;"><em>claudiu.papasteri@gmail.com</em></span></p>
&nbsp;
