---
title: "<br> Rezidential" 
subtitle: "Network Analysis"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    # pdf_document: 
    #         toc: true
    #         toc_depth: 2
    #         number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---


<!-- Setup -->


```{r setup, include = FALSE}
# kintr options
knitr::opts_chunk$set(
  comment = "#",
  collapse = TRUE,
  echo = TRUE, 
  cache = TRUE, 
  warning = FALSE, message = FALSE   # WHEN NOTEBOOK IS FINISHED ... until then leave: warning = TRUE, message = TRUE        
)

# General R options and info
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation

# Load packages
if (!require("pacman")) install.packages("pacman")
packages <- c(
  "knitr", "kableExtra", "papaja",  
  "tidyverse", "plyr",      
  "psych", "psycho",           
  "broom", "summarytools", "tadaatoolbox", "PerformanceAnalytics",          
  "ggplot2", "ggpubr", "scales",        
  "rio",
  "Hmisc", 
  "GGally", "corrplot", "RColorBrewer", 
  "car",
  "IsingFit", "qgraph", "igraph"     # for network analyses
  # , ...
)
pacman::p_load(char = packages)

# Themes for ggplot2 ploting (here used APA style)
theme_set(theme_apa())
```

```{r working_directory, include = FALSE}
# if needed
# wd = "./Rezidential"
# setwd(wd)
```


<!-- REPORT -->

# Load data

```{r rds_data, results = 'hide', cache.extra = file.info("Data_Rezidential.RDS")}
## Read
filename <- "Data_Rezidential.RDS"   

Data <- readRDS(filename)  
```


## Modify ACE Score to take into account that all are institutionalized

```{r derived_data, dependson = "rds_data"}
Data$CYW <- ifelse(Data$CYW == 0, 0, Data$CYW - 1) 
```


## Percentage of individually reported ACEs out of ACE Score

```{r perc_indivACE}
indiv_ACE_sum <- rowSums(Data[, c(sprintf("sec1_%d", 1:10), sprintf("sec2_%d", 2:9))], na.rm = TRUE)
# sum(Data$CYW - indiv_ACE_sum < 0)    # 7 cases where indiv_ACE_sum > Data$CYW

## Summaries
cat("### summary individually reported")
summary(indiv_ACE_sum, na.rm = TRUE)
prop.table(table(indiv_ACE_sum))
cat("### summary overall reported")
summary(Data$CYW, na.rm = TRUE)
prop.table(table(Data$CYW))

# Plots
acescore_df <- data.frame(ID = Data$ID, Individual = indiv_ACE_sum, Overall = Data$CYW)
acescore_df %>%
  gather(Var, Val, -ID) %>%
    # ggviolin(., x = "Var", y = "Val", 
    #             add = c("boxplot", "mean_sd")) +
    ggerrorplot(., x = "Var", y = "Val",
            desc_stat = "mean_sd", color = "black",
            add = "violin", add.params = list(color = "darkgrey"),
            xlab = NULL, ylab = "Reported score") +
    stat_compare_means(comparisons = list( c("Individual", "Overall")), label = "p.signif")+ # Add significance levels
    stat_compare_means(label.y = 20, label.x = 0.55)


cat("### simple percent of sums of events")
sum(acescore_df$Individual) / sum(acescore_df$Overall) * 100     # so they report only 70% of ACEs individually

acescore_df %>%
  pivot_longer(-ID, names_to = "vars", values_to = "value") %>%
  rstatix::wilcox_test(value ~ vars, detailed = TRUE)

plot1 <- 
  acescore_df %>%
    dplyr::rename("Particular" = Individual) %>%
    pivot_longer(-ID, names_to = "vars", values_to = "value") %>%
    #dplyr::mutate(vars = as.factor(vars)) %>%
    ggstatsplot::ggwithinstats(
    data = .,
    x = vars,
    y = value,
    xlab = "",
    ylab = "Number of reported ACEs",
    type = "np",
    outlier.tagging = FALSE,
    pairwise.comparisons = TRUE,
    pairwise.display = "all",
    bf.message = FALSE, 
    p.adjust.method = "none",
    point.path = TRUE,
    ggtheme = ggprism::theme_prism(),
    # package = "RColorBrewer",  # "ggsci",
    # palette = "Dark",         # "default_jco",
    violin.args = list(width = 0.9, alpha = 0.2, size = 1, color = "black"),
    centrality.plotting = FALSE,
    centrality.type = "np",
    centrality.point.args = list(size = 5, color = "darkred"),
    #centrality.label.args = FALSE,
    ggplot.component = list(
      theme(
        plot.title = element_text(hjust = 0, size = 16),
        plot.subtitle = element_text(hjust = 0, size = 12), 
        plot.caption = element_text(hjust = 0, size = 12), 
        text = element_text(size = 14)
    ))
    ) + scale_colour_grey(start = 0.2, end = 0.2) 

# ggplot2::ggsave(filename = "plot1.png", plot1, device = "png", path = NULL,
#                 units = "in", dpi = 300, width = 6, height = 6)
```


# Network

```{r ACE_net}
## Dataframe
Ace_col_names <- c(sprintf("sec1_%d", 1:10), sprintf("sec2_%d", 2:9))
Ace_new_names <- c("divort", "incarcerare", "boala mintala", "amenintare", "umilire", 
                   "abuz sexual", "lipsuri", "abuz fizic", "adictie", "nesiguranta", 
                   "bullying", "deces", "emigrare", "boala", "violenta", 
                   "rautate", "politie", "abuz partener") 

netword_df <- Data[, c("ID", sprintf("sec1_%d", 1:10), sprintf("sec2_%d", 2:9))]
netword_df <- 
  netword_df %>%
  replace(is.na(.), 0) %>%
  rename_at(vars(Ace_col_names), ~ Ace_new_names)

## Fit eLasso net  
eLasso_net <- IsingFit::IsingFit(netword_df[, names(netword_df) != "ID"], 
                                family = "binomial",
                                AND = TRUE, gamma = 0.25, 
                                plot = TRUE, progressbar = FALSE,
                                title = "eLasso")

## Reproduce graph for community analysis (Walktrap clustering)
net_plot <- qgraph::qgraph(eLasso_net$weiadj, 
                           layout = "spring", weighted = TRUE, 
                           labels = rownames(eLasso_net$weiadj),
                           title = "eLasso - reproduced qgraph")  # put labels to avoid abbrev
# plot(net_plot)
centr_net_plot <- centralityPlot(eLasso_net$weiadj) # centrality_auto(eLasso_net$weiadj) to get matrix

## Community analysis (Walktrap clustering)
# ig_eLasso <- igraph::graph_from_adjacency_matrix(eLasso_net$weiadj, mode = "undirected" ,weighted = TRUE)
ig_eLasso <- igraph::as.igraph(net_plot)
plot(ig_eLasso, main = "eLasso - reproduced igraph")  # just check
ig_eLasso_communities <- igraph::cluster_walktrap(ig_eLasso)
ig_eLasso_commun_mem <- as.factor(ig_eLasso_communities$membership)

## Plot qgraph with community results
# Coloured
qgraph::qgraph(net_plot, 
               groups = ig_eLasso_commun_mem,
               legend.cex = 0.7,                          # borders = FALSE, pastel = TRUE,
               color = c("lightblue", "lightsalmon", "lightgreen", "lightgrey"),
               title = NULL)
# Greyscale
qgraph::qgraph(net_plot, 
               groups = ig_eLasso_commun_mem,
               edge.color = "black", fade = TRUE,
               legend.cex = 0.7,                          
               color = c("grey90", "grey59", "grey35", "white"),
               title = NULL)
              
              
```


# Network - eng

```{r ACE_net_eng}
## Dataframe
Ace_col_names <- c(sprintf("sec1_%d", 1:10), sprintf("sec2_%d", 2:9))
Ace_new_names <- c("o. divorce", "o. incarceration", "o. mental illness", "o. violence", "emotional abuse",
                    "sexual abuse", "physical neglect", "physical abuse", "o. addiction", "emotional neglect",
                    "bullying", "dead parent", "emigration", "illness", "unsafe n/hood",
                    "discrimination", "arrest", "partner abuse")
Ace_new_names_hyphen <- c("o.\ndivorce", "o.\nincarce-\nration", "o.\nmental\nillness", "o.\nvio-\nlence", "emo-\ntional\nabuse",
                    "sexual\nabuse", "physical\nneglect", "physical\nabuse", "o.\naddic-\ntion", "emo-\ntional\nneglect",
                    "bullying", "dead\nparent", "emigra-\ntion", "illness", "unsafe\nn/hood",
                    "discrimi-\nnation", "arrest", "partner\nabuse")




netword_df <- Data[, c("ID", sprintf("sec1_%d", 1:10), sprintf("sec2_%d", 2:9))]
netword_df <- 
  netword_df %>%
  replace(is.na(.), 0) %>%
  rename_at(vars(Ace_col_names), ~ Ace_new_names)

## Fit eLasso net  
eLasso_net <- IsingFit::IsingFit(netword_df[, names(netword_df) != "ID"], 
                                family = "binomial",
                                AND = TRUE, gamma = 0.30, 
                                plot = TRUE, progressbar = FALSE,
                                title = "eLasso")

## Reproduce graph for community analysis (Walktrap clustering)
net_plot <- qgraph::qgraph(eLasso_net$weiadj, 
                           layout = "spring", weighted = TRUE, 
                           labels = rownames(eLasso_net$weiadj),
                           title = "eLasso - reproduced qgraph")  # put labels to avoid abbrev
# plot(net_plot)




centr_net_plot <- centralityPlot(eLasso_net$weiadj, 
                                 include = c("Strength", "Closeness", "Betweenness"),
                                 orderBy = "Strength") +
                  theme(strip.text.x = element_text(size = 8), 
                        axis.text = element_text(size = 7))
# ggsave("net_centr.tiff", units = "in", width = 3.5, height = 4.6)


# centrality_auto(eLasso_net$weiadj) to get matrix

## Community analysis (Walktrap clustering)
# ig_eLasso <- igraph::graph_from_adjacency_matrix(eLasso_net$weiadj, mode = "undirected" ,weighted = TRUE)
ig_eLasso <- igraph::as.igraph(net_plot)
plot(ig_eLasso, main = "eLasso - reproduced igraph")  # just check
ig_eLasso_communities <- igraph::cluster_walktrap(ig_eLasso)
ig_eLasso_commun_mem <- as.factor(ig_eLasso_communities$membership)

## Plot qgraph with community results
# Coloured
qgraph::qgraph(net_plot, 
               groups = ig_eLasso_commun_mem,
               legend.cex = 0.7,                          # borders = FALSE, pastel = TRUE,
               color = c("lightblue", "lightsalmon", "lightgreen", "lightgrey"))

# tiff("net.tiff", units = "in", width = 5, height = 5, res = 300)
clor_net <- qgraph::qgraph(net_plot, 
               groups = ig_eLasso_commun_mem,
               legend.cex = 0.7,                          # borders = FALSE, pastel = TRUE,
               color = c("lightblue", "lightsalmon", "lightgreen", "lightgrey"),
               vsize = 8, border.color = "black", 
               labels = Ace_new_names_hyphen, label.cex = 1, 
               title = NULL,
               usePCH = FALSE, node.resolution = 300)
# dev.off()


# Greyscale              
# tiff("net.tiff", units = "in", width = 5, height = 5, res = 300)
clor_net <- qgraph::qgraph(net_plot, 
               groups = ig_eLasso_commun_mem,
               legend.cex = 0.7,                    # borders = FALSE, pastel = TRUE,
               edge.color = "black",    
               color = c("grey90", "grey59", "grey29", "white"),
               vsize = 8, border.color = "black", 
               labels = Ace_new_names_hyphen, label.cex = 1, 
               title = NULL,
               usePCH = FALSE, node.resolution = 300)
# dev.off()
              
```



# Remake ACE descriptives for article

```{r descr_ace, fig.width = 12, fig.asp = 1.6}
# Data$sec2_1    is redundant because all should be 1, even tough there are 403 NA and 872 of 1
Ace_col_names <- c(sprintf("sec1_%d", 1:10), sprintf("sec2_%d", 2:9))

Ace_new_names <- c("o. divorce", "o. incarceration", "o. mental illness", "o. violence", "emotional abuse",
                    "sexual abuse", "physical neglect", "physical abuse", "o. addiction", "emotional neglect",
                    "bullying", "dead parent", "emigration", "illness", "unsafe n/hood",
                    "discrimination", "arrest", "partner abuse") 

# Plot function and Data function
ace_plot <- function(df){ 
  ggplot(df, aes(x = variable, y = percent, fill = variable)) + 
     geom_bar(stat = "identity") +
     geom_text(aes(label = paste0(round(percent), "%")), vjust = -0.23, size = 2.1) +
     guides(fill = "none") + 
     theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
     ylab("Percentage") +  xlab("") +
    scale_fill_grey(start = .1, end = .7) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1.1),   # hjust = 1.1
    axis.text = element_text(size = 8),
    axis.title=element_text(size = 10))
}

ace_data <- function(df, ace_levels, filter_col, filter_level){
  filter_col <- rlang::enquo(filter_col)
  df %>% 
    filter(!!filter_col %in% filter_level) %>% 
    select(Ace_col_names) %>%
    summarise_all(funs(sum(!is.na(.)) / length(.) * 100)) %>% 
    gather(variable, percent) %>%
    mutate(variable = stringr::str_replace(variable, Ace_col_names, Ace_new_names)) %>%
    arrange(desc(percent)) %>%
    mutate(variable = factor(variable, ace_levels)) 
}  
  
# ACEs data & plots
Data_ACE <- 
  Data %>%    # barplot(colSums(Data[, Ace_col_names], na.rm = TRUE))
    select(Ace_col_names) %>%
    summarise_all(funs(sum(!is.na(.)) / length(.) * 100)) %>% 
    gather(variable, percent) %>%
    mutate(variable = stringr::str_replace(variable, Ace_col_names, Ace_new_names)) %>%
    arrange(desc(percent)) %>%
    mutate(variable = factor(variable, variable))     # this makes levels order match row order!
ace_levels <- levels(Data_ACE$variable)  


# NEW
Data_ACE %>%
  ggplot(aes(x = variable, y = percent, fill = variable)) + 
     geom_bar(stat = "identity") +
     geom_text(aes(label = paste0(round(percent), "%")), vjust = -0.25, size = 2.6) +
     guides(fill = "none") + 
     ylab("Percentage") +  xlab("")  +
  scale_fill_grey(start = .1, end = .7) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1.1),   # hjust = 1.1
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 10))

# ggsave("ace_distrib.tiff", units = "in", width = 5, height = 3.8)



ace_plot1 <- 
  Data_ACE %>%
    ace_plot() + 
      ggtitle("ACE") 

ace_plot2 <-  
  ace_data(Data, ace_levels, gen, filter_level = "f") %>%
    ace_plot() +
      ggtitle("Girls") 

ace_plot3 <-
  ace_data(Data, ace_levels, gen, filter_level = "m") %>%
    ace_plot() +
      ggtitle("Boys") 

ace_plot4 <-
  ace_data(Data, ace_levels, tip_chestionar, filter_level = c("5-8ani", "5-8intarziere")) %>%
    ace_plot() +
      ggtitle("Ages 5-8") 

ace_plot5 <-
  ace_data(Data, ace_levels, tip_chestionar, filter_level = "9-18ani") %>%
    ace_plot() +
      ggtitle("Ages 9-18")


ggpubr::ggarrange(                                                
          ggarrange(ace_plot2, ace_plot3, ncol = 2, labels = c("A", "B")), 
          ggarrange(ace_plot4, ace_plot5, ncol = 2, labels = c("C", "D")),
          nrow = 2) # %>%
  # ggpubr::ggexport(filename = "ace_distrib_detail.tiff", width = 2300, height = 2450, res = 300)


           
#Data %>%
  #select(ID, tip_chestionar, gen, sprintf("sec1_%d", 1:10), sprintf("sec2_%d", 1:9)) %>%
  #gather(variable, value, sec1_1:sec2_9, -c(tip_chestionar, gen), na.rm = FALSE, convert = FALSE) %>%
  #mutate(value = replace_na(value, 0)) %>%
  
```



# Remake ACE score freqs for article

```{r}
ace_plot <- function(df){ 
  ggplot(df, aes(x = variable, y = percent, fill = variable)) + 
     geom_bar(stat = "identity") +
     geom_text(aes(label = paste0(round(percent, 1), "%")), vjust = -0.23, size = 2.1) +
     guides(fill = "none") + 
     #theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
     ylab("Percentage") +  xlab("") +
    scale_fill_grey(start = .1, end = .7) +
  theme(
    #axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1.1),   # hjust = 1.1
    axis.text = element_text(size = 8),
    axis.title=element_text(size = 10))
}

Data %>%
  dplyr::select(CYW) %>%
  dplyr::mutate(CYW = as.factor(CYW)) %>%
  dplyr::count(CYW, .drop = FALSE) %>%                          # Group by, then count number in each group (dont drop 0 counts)
  dplyr::mutate(percent = prop.table(n) * 100) %>%                           # Calculate percent within each var
  dplyr::rename("variable" = CYW) %>% 
  ace_plot()

# ggsave("acescore_distrib.tiff", units = "in", width = 5, height = 3.8) 

percents <- Data %>%
  dplyr::select(CYW) %>%
  dplyr::mutate(CYW = as.factor(CYW)) %>%
  dplyr::count(CYW, .drop = FALSE) %>%                          # Group by, then count number in each group (dont drop 0 counts)
  dplyr::mutate(percent = prop.table(n) * 100) %>%
  dplyr::pull(percent)

percents[1]
sum(percents[2:6])
sum(percents[7:18])

100 - sum(percents[1:2])   # >1 ACE
```


```{r}
tiff("rootogram.tiff", units = "in", width = 12, height = 8, res = 300)
gf <- vcd::goodfit(Data$CYW, type = "poisson", method = "ML")    # based on load the vcd package
hroot_plot1 <- plot(gf, type = "hanging", shade = TRUE, main = "Hanging Rootogram", return_grob = TRUE)
droot_plot1 <- plot(gf, type = "deviation", shade = TRUE, main = "Deviation Rootogram", return_grob = TRUE)
vcd::mplot(hroot_plot1, droot_plot1, gp_sub = grid::gpar(fontsize = 11))
dev.off()
```




```{r}
tiff("poissonness.tiff", units = "in", width = 6, height = 5, res = 300)
## Poissonness plots
dist_plot1 <- vcd::distplot(Data$CYW, type = "poisson", xlab = "ACE Total Score", return_grob = TRUE)
dev.off()
```

```{r}
# Neg Binom
tiff("nbinomial.tiff", units = "in", width = 6, height = 5, res = 300)
gf2 <- vcd::goodfit(Data$CYW, type = "nbinomial")
dist_plot2 <- vcd::distplot(Data$CYW, type = "nbinomial", xlab = "ACE", return_grob = TRUE)
dev.off()
```

```{r}
tiff("ordplot.tiff", units = "in", width = 6, height = 5, res = 300)
## Ord plots: Diagnostic slope and intercept for four discrete distributions
vcd::Ord_plot(Data$CYW, main = "Ord plot", gp = grid::gpar(cex = 1), pch = 16)
dev.off()
```

# Remake Gender anaysis

```{r}
plot2 <- 
  Data %>%
    dplyr::select(gen, CYW) %>%
    #dplyr::mutate(gen = as.factor(gen)) %>%
    ggstatsplot::ggbetweenstats(
    data = .,
    x = gen,
    y = CYW,
    xlab = "",
    ylab = "Number of reported ACEs",
    type = "p",
    outlier.tagging = FALSE,
    pairwise.comparisons = TRUE,
    pairwise.display = "all",
    bf.message = FALSE, 
    p.adjust.method = "none",
    point.path = TRUE,
    ggtheme = ggprism::theme_prism(),
    # package = "RColorBrewer",  # "ggsci",
    # palette = "Dark",         # "default_jco",
    violin.args = list(width = 0.9, alpha = 0.2, size = 1, color = "black"),
    centrality.plotting = FALSE,
    centrality.type = "np",
    centrality.point.args = list(size = 5, color = "darkred"),
    #centrality.label.args = FALSE,
    ggplot.component = list(
      theme(
        plot.title = element_text(hjust = 0, size = 16),
        plot.subtitle = element_text(hjust = 0, size = 12), 
        plot.caption = element_text(hjust = 0, size = 12), 
        text = element_text(size = 14)
    ))
    ) + scale_colour_grey(start = 0.2, end = 0.2) 

# ggplot2::ggsave(filename = "plot1.png", plot1, device = "png", path = NULL,
#                 units = "in", dpi = 300, width = 6, height = 6)

Data %>%
  dplyr::select(CYW, v_mama_nastere) %>%
  ggstatsplot::ggbetweenstats(
    data = .,
    x = v_mama_nastere,
    y = CYW,
    xlab = "",
    ylab = "",
    type = "p",
    outlier.tagging = FALSE,
    pairwise.comparisons = TRUE,
    pairwise.display = "all",
    bf.message = FALSE, 
    p.adjust.method = "none",
    point.path = TRUE,
    ggtheme = ggprism::theme_prism(),
    # package = "RColorBrewer",  # "ggsci",
    # palette = "Dark",         # "default_jco",
    violin.args = list(width = 0.9, alpha = 0.2, size = 1, color = "black"),
    centrality.plotting = FALSE,
    centrality.type = "np",
    centrality.point.args = list(size = 5, color = "darkred"),
    #centrality.label.args = FALSE,
    ggplot.component = list(
      theme(
        plot.title = element_text(hjust = 0, size = 16),
        plot.subtitle = element_text(hjust = 0, size = 12), 
        plot.caption = element_text(hjust = 0, size = 12), 
        text = element_text(size = 14)
    ))
    ) + scale_colour_grey(start = 0.2, end = 0.2) 


Data %>%
  dplyr::select(CYW, v_mama_nastere) %>%
  dplyr::filter(v_mama_nastere %in% c("20-25", "26–34")) %>%
  ggstatsplot::ggbetweenstats(
    data = .,
    x = v_mama_nastere,
    y = CYW,
    xlab = "",
    ylab = "",
    type = "p",
    outlier.tagging = FALSE,
    pairwise.comparisons = TRUE,
    pairwise.display = "all",
    bf.message = FALSE, 
    p.adjust.method = "none",
    point.path = TRUE,
    ggtheme = ggprism::theme_prism(),
    # package = "RColorBrewer",  # "ggsci",
    # palette = "Dark",         # "default_jco",
    violin.args = list(width = 0.9, alpha = 0.2, size = 1, color = "black"),
    centrality.plotting = FALSE,
    centrality.type = "np",
    centrality.point.args = list(size = 5, color = "darkred"),
    #centrality.label.args = FALSE,
    ggplot.component = list(
      theme(
        plot.title = element_text(hjust = 0, size = 16),
        plot.subtitle = element_text(hjust = 0, size = 12), 
        plot.caption = element_text(hjust = 0, size = 12), 
        text = element_text(size = 14)
    ))
    ) + scale_colour_grey(start = 0.2, end = 0.2)

 
```

# Remake Gender Age

```{r}
Data %>%
  dplyr::select(gen, varsta) %>%
  ggstatsplot::ggbetweenstats(
    data = .,
    x = gen,
    y = varsta,
    xlab = "",
    ylab = "",
    type = "p",
    outlier.tagging = FALSE,
    pairwise.comparisons = TRUE,
    pairwise.display = "all",
    bf.message = FALSE, 
    p.adjust.method = "none",
    point.path = TRUE,
    ggtheme = ggprism::theme_prism(),
    # package = "RColorBrewer",  # "ggsci",
    # palette = "Dark",         # "default_jco",
    violin.args = list(width = 0.9, alpha = 0.2, size = 1, color = "black"),
    centrality.plotting = FALSE,
    centrality.type = "np",
    centrality.point.args = list(size = 5, color = "darkred"),
    #centrality.label.args = FALSE,
    ggplot.component = list(
      theme(
        plot.title = element_text(hjust = 0, size = 16),
        plot.subtitle = element_text(hjust = 0, size = 12), 
        plot.caption = element_text(hjust = 0, size = 12), 
        text = element_text(size = 14)
    ))
    ) + scale_colour_grey(start = 0.2, end = 0.2)
```



# Remake Risk fact descriptives

```{r}
Risk_col_names <- c("expunere_tox", "boli", "TCC", "asfixie", "abuz_sub", "grad_h", "intarziere", "tras_dez", "tulb_cond", 
                    "neglijare", "temperam", "repetenta", "scoala_spec", "inabil_sc", "schimb_dom", "pierd_loc", "comunit")

Risk_col_names_eng <- c("prenatal exposure", "chronic disease", "CCT", "birth asphyxia", "substance abuse", "disability grade", "cognitive delay", "TRAS_DEZ",                            "conduct disorder", 
                        "inst. due to neglect", "TEMPERAM", "grade retention", "special education", "inadequate schooling", "frequent moving", "homelessness", "disorganized community")

# prenatal exposure  
# chronic disease
# CCT
# birth asphyxia 
# substance abuse
# disability grade
# cognitive delay
# ## maladaptive traits (trasaturi dezadaptative)
# conduct disorder
# inst. due to abuse/neglect
# ## difficult personality (temperament)
# grade retention
# special education
# inadequate schooling
# frequent moving 
# homelessness
# disorganized community


# Plot function and Data function
risk_plot <- function(df){ 
  ggplot(df, aes(x = variable, y = percent, fill = variable)) + 
     geom_bar(stat = "identity") +
     geom_text(aes(label = paste0(round(percent), "%")), vjust = -0.23, size = 2.1) +
     guides(fill = "none") + 
     theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
     ylab("Percentage") +  xlab("") +
    scale_fill_grey(start = .1, end = .7) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1.1),   # hjust = 1.1
    axis.text = element_text(size = 8),
    axis.title=element_text(size = 10))
}

risk_data <- function(df, risk_levels, filter_col, filter_level){
  filter_col <- rlang::enquo(filter_col)
  df %>% 
    rename_at(vars(Risk_col_names), ~ Risk_col_names_eng) %>%
    filter(!!filter_col %in% filter_level) %>% 
    select(Risk_col_names_eng) %>%
    dplyr::select(-c("TRAS_DEZ", "TEMPERAM")) %>%
    summarise_all(funs(sum(!is.na(.)) / length(.) * 100)) %>% 
    gather(variable, percent) %>%
    arrange(desc(percent)) %>%
    mutate(variable = factor(variable, risk_levels)) 
}
# Rsik data & plots
Data_Risk <- 
  Data %>%    
    dplyr::select(Risk_col_names) %>%
    rename_at(vars(Risk_col_names), ~ Risk_col_names_eng) %>%
    summarise_all(funs(sum(!is.na(.)) / length(.) * 100)) %>% 
    gather(variable, percent) %>%
    dplyr::filter(! variable %in% c("TRAS_DEZ", "TEMPERAM")) %>%
    arrange(desc(percent)) %>%
    mutate(variable = factor(variable, variable))     # this makes levels order match row order!
risk_levels <- levels(Data_Risk$variable)  



# NEW
Data_Risk %>%
  ggplot(aes(x = variable, y = percent, fill = variable)) + 
     geom_bar(stat = "identity") +
     geom_text(aes(label = paste0(round(percent), "%")), vjust = -0.25, size = 2.6) +
     guides(fill = "none") + 
     ylab("Percentage") +  xlab("")  +
  scale_fill_grey(start = .1, end = .7) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1.1),   # hjust = 1.1
    axis.text = element_text(size = 8),
    axis.title=element_text(size = 10))

# ggsave("risk_distrib.tiff", units = "in", width = 5, height = 3.8)

risk_plot1 <- 
  Data_Risk %>%
    risk_plot() +
      ggtitle("Risk") 


risk_plot2 <-
  risk_data(Data, risk_levels, gen, filter_level = "f") %>%
    risk_plot() +
      ggtitle("Girls") 
risk_plot3 <-
  risk_data(Data, risk_levels, gen, filter_level = "m") %>%
    risk_plot() +
      ggtitle("Boys") 
risk_plot4 <-
  risk_data(Data, risk_levels, tip_chestionar, filter_level = c("5-8ani", "5-8intarziere")) %>%
    risk_plot() +
      ggtitle("Ages 5-8") 
risk_plot5 <-
  risk_data(Data, risk_levels, tip_chestionar, filter_level = "9-18ani") %>%
    risk_plot() +
      ggtitle("Ages 9-18")


ggpubr::ggarrange(                                                
          ggarrange(risk_plot2, risk_plot3, ncol = 2, labels = c("A", "B")), 
          ggarrange(risk_plot4, risk_plot5, ncol = 2, labels = c("C", "D")),
          nrow = 2) # %>%
  # ggpubr::ggexport(filename = "risk_distrib_detail.tiff", width = 2300, height = 2450, res = 300)

```

# Remake family

```{r}
PerformanceAnalytics::chart.Correlation(Data[, c("varsta_inst", "nr_frati", "nr_frati_inst", "CYW")])

Data[, c("varsta_inst", "nr_frati", "nr_frati_inst", "CYW")] %>%
  correlation::correlation()

Data[, c("varsta_inst", "nr_frati", "nr_frati_inst", "v_mama_nastere")] %>%
  rstatix::get_summary_stats()


Data %>%
  dplyr::select(v_mama_nastere) %>%
  dplyr::count(v_mama_nastere) %>%
  mutate(percent = round(n / sum(n) * 100, 2))

# str(Data$v_mama_nastere)
# fam_Data <- Data[, c("varsta_inst", "nr_frati", "nr_frati_inst", "v_mama_nastere", "CYW")]
# fam_Data$v_mama_nastere <- as.numeric(fam_Data$v_mama_nastere)
# str(fam_Data$v_mama_nastere)
# 
# fam_Data %>%
#   correlation::correlation(p_adjust = "none")
```


# New ACE net descriptives

```{r}
Ace_col_names <- c(sprintf("sec1_%d", 1:10), sprintf("sec2_%d", 2:9))

Ace_new_names <- c("divorce", "incarceration", "mental illness", "threat", "humiliation",
                    "sexual abuse", "physical neglect", "physical abuse", "addiction", "unsupported",
                    "bullying", "dead parent", "emigration", "illness", "violence",
                    "discrimination", "arrest", "partner abuse")

Data %>%
  dplyr::select(Ace_col_names, varsta) %>%
  dplyr::rename_at(vars(Ace_col_names), ~ Ace_new_names) %>%
  dplyr::mutate_at(vars(Ace_new_names), ~ tidyr::replace_na(., 0)) %>%
  tidyr::pivot_longer(-varsta, names_to = "variable", values_to = "value") %>%
  dplyr::filter(value == 1) %>%
  group_by(variable) %>%
  dplyr::summarise(mean_age = mean(varsta)) %>%
  arrange(mean_age)
```



## Remake Poisson vs NB model rootogram

```{r}
## Data for GLMs
Data_glm <-
  Data %>%    # recode v_mama_nastere to binary
    mutate(v_mama_nastere_d = fct_recode(v_mama_nastere, "1" = "<19" , "0" = "20-25", "0" = "26?34", "0" = "35>")) %>%
    mutate_at(vars(v_mama_nastere_d), funs(as.numeric(as.character(.)))) %>%
    select(CYW, varsta, gen, 9:29, v_mama_nastere_d) %>%
    mutate_at(vars(expunere_tox:comunit), funs(replace_na(., 0)))

# NB2
mod_nb2 <- MASS::glm.nb(CYW ~ expunere_tox + varsta_inst + schimb_dom + 
                              varsta + intarziere + TCC + neglijare + scoala_spec + tulb_cond,
                              data = Data_glm)
summary(mod_nb2) # tidy(mod_nb2) %>% mutate_if(is.numeric, round, 2)  %>% xlsx::write.xlsx(., file = "mod_nb2.xlsx") 

# Poisson
mod_pois_new <- glm(formula = CYW ~ expunere_tox + varsta_inst + schimb_dom + 
                                    varsta + intarziere + TCC + neglijare + scoala_spec + tulb_cond,
                                    family = poisson, data = Data_glm)
summary(mod_pois_new) # tidy(mod_pois_new) %>% mutate_if(is.numeric, round, 2)  %>% xlsx::write.xlsx(., file = "mod_pois_new.xlsx") 


# install.packages("countreg", repos = "http://R-Forge.R-project.org", dep = TRUE)
library(countreg)

# tiff("rootogram_pois_mod.tiff", units = "in", width = 8, height = 6, res = 300)
countreg::rootogram(mod_pois_new, ylim = c(-7, 18), main = "Poisson", xlab = "ACE Total Score")     # rootogram on the fitted model 
# dev.off()

# tiff("rootogram_nb2_mod.tiff", units = "in", width = 8, height = 6, res = 300)
countreg::rootogram(mod_nb2, ylim = c(-7, 18), main = "Negative Binomial") 
# dev.off()
```


# New Plot for Gender X Age

```{r}
## Dodged Bar plot of Age and Gender
Data_genvarsta <- Data[, c("gen", "varsta")] %>%
  dplyr::rename_at(vars("gen", "varsta"), ~ c("Gender_ro", "Age_num"))

Data_genvarsta  %>%
  mutate(Age = cut(Age_num, 
                   breaks = c(-Inf, 6:18), 
                   labels = c("[5,6]", "(6,7]", "(7,8]", "(8,9]", "(9,10]", "(10,11]", 
                              "(11,12]", "(12,13]", "(13,14]", "(14,15]", "(15,16]", "(16,17]", "(17,18]"), 
                   right = TRUE)) %>% 
  mutate(Varsta = as.factor(Age),
         Gender = dplyr::case_when(Gender_ro == "f" ~ "Girls", Gender_ro == "m" ~ "Boys"),
         Gender = as.factor(as.character(Gender))) %>%
  dplyr::count(Age, Gender, .drop = FALSE) %>%         # Group by, then count number in each group (dont drop 0 counts)
  mutate(pct = prop.table(n)) %>%                           # Calculate percent within each var
  mutate(label = round(pct, 3) * 100,
         label = paste(label, "%")) %>%
    ggplot(aes(x = Age, y = pct, fill = Gender, label = label)) + 
      geom_col(position = position_dodge(preserve = "single"), stat = "identity") +    # Don't drop zero count
      geom_text(position = position_dodge(width = .9),      # move to center of bars
                vjust = -0.5,                               # nudge above top of bar
                size = 3.5) + 
      scale_y_continuous(labels = scales::percent, n.breaks = 7) +
      ggtitle("") +
      xlab("") + ylab("Percentage %") + 
      guides(fill = guide_legend(title = "")) +   # ncol = 1
      scale_fill_grey(start = 0.7, end = 0.2, na.value = "red", aesthetics = "fill") +
      theme(legend.position = "bottom", legend.direction = "horizontal", 
            # legend.justification = c(0, 1), panel.border = element_rect(fill = NA, colour = "black"),
            axis.text = element_text(size = 13),
            axis.title = element_text(size = 15),
            legend.title = element_text(size = 15),
            legend.text = element_text(size = 14)) 

ggplot2::ggsave(filename = "age_gender_distrib.png", device = "png", path = NULL,
                units = "in", dpi = 300, width = 12, height = 7)
```



<!-- Session Info and License -->

<br>

<br>

# Session Info
```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->
&nbsp;
<hr />
<p style="text-align: center;">A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a></p>
<p style="text-align: center;"><span style="color: #808080;"><em>claudiu.papasteri@gmail.com</em></span></p>
&nbsp;
