---
title: "<br> O1A Report" 
subtitle: "Final Report"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    pdf_document: 
            toc: true
            toc_depth: 2
            number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---


<!-- Setup -->


```{r setup, include = FALSE}
# kintr options
knitr::opts_chunk$set(
  comment = "#",
  collapse = TRUE,
  echo = TRUE, warning = TRUE, message = TRUE, cache = TRUE       # echo = False for github_document, but will be folded in html_notebook
)

# General R options and info
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation

# Load packages
if (!require("pacman")) install.packages("pacman")
packages <- c(
  "tidyverse",      # best thing that happend to me
  "psych",          # general purpose toolbox for personality, psychometric theory and experimental psychology
  "papaja",         # for APA style
  "broom",          # for tidy modelling
  "ggplot2",        # best plots
  "ggpubr",         # ggplot2 to publication quality
  "DT",             # nice searchable and downloadable tables
  "summarytools"
  # , ...
)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(char = packages)

# Themes for ggplot2 ploting (here used APA style)
theme_set(theme_apa())
```

```{r working_directory, include = FALSE}
# if needed
# wd = "./o1a-report"
# setwd(wd)
```


<!-- Report -->


# Load data

```{r raw_data, results = 'hide', cache.extra = file.info("diamonds.csv")}
# Read
file = "DATE O1A Complete.xlsx"

Date <- readxl::read_xlsx(file, sheet = "Date zilnice", skip = 5, col_names = FALSE)
```


## Processing data

```{r processed_data, cache = TRUE, dependson = "raw_data"}
# Clean
varnames <- c("Nr_crt", "ID", "Nume_Prenume", "Zi", "Vas_stres_pre", "Vas_bine_pre",
             sprintf("Stais_pre_%01d", seq(1,20)),
             "SOP",
             "IOS_mama", "IOS_tata", "IOS_iubit", "IOS_prieten", "IOS_personalitate",
             "Vas_rel_global", "Vas_rel_arousal",
             "CRQ_1", "CRQ_2", "CRQ_3", "CRQ_4", "CRQ_5", "CRQ_6",
             "Vas_stres_post", "Vas_bine_post",
             sprintf("Stais_post_%01d", seq(1,20))
)
names(Date) <- varnames   # nume noi
Date <- Date[-c(1:2),]    # scoatem randurile cu numele precedente
Date$Nr_crt <- 1:nrow(Date)   # era gol, asa ca numerotam randurile ca sa avem acesta variabila 

# Process NAs
Date <- Date %>% 
    na_if("na") %>%  
    mutate(NA_per_row = rowSums(is.na(.)))     # count NAs by row

Date <- Date %>% 
    filter(NA_per_row < 20)         # arbitrary cutoff for NAs on columns ... it is normal to have 4 NAs for all columns

# Convert to numeric
varsnumeric <- c("Zi", "Vas_stres_pre", "Vas_bine_pre",
                 sprintf("Stais_pre_%01d", seq(1,20)),
                 "IOS_mama", "IOS_tata", "IOS_iubit", "IOS_prieten", "IOS_personalitate",
                 "Vas_rel_global", "Vas_rel_arousal",
                 "CRQ_1", "CRQ_2", "CRQ_3", "CRQ_4", "CRQ_5", "CRQ_6",
                 "Vas_stres_post", "Vas_bine_post",
                  sprintf("Stais_post_%01d", seq(1,20)))

Date <- Date %>% 
  mutate_at(varsnumeric, as.numeric)

# which(Date$Stais_post_11 == 47)    # typo Stais_post_11 value of 47 -> corrected to 4
Date$Stais_post_11[Date$Stais_post_11 == 47] <- 4
```

<!-- Inspect Data - switched off -->
```{r inspectdata, echo=FALSE, results="hide"} 
# print(summarytools::dfSummary(Date, style = 'grid', plain.ascii = FALSE, graph.magnif = 0.85),    # suppress output
#       method = 'render', headings = FALSE)
# str(Date, list.len=ncol(Date))  # data types are fine
```


## Compute new variables

```{r derived_data, cache = TRUE, dependson = "processed_data"}
# Compute new variables 
Conditie <- Date %>% 
    select(Nr_crt, ID, IOS_mama, IOS_tata, IOS_iubit, IOS_prieten, IOS_personalitate) %>% 
    gather(type, value, -c(Nr_crt, ID)) %>% 
    mutate(Conditie = ifelse(!is.na(value), type, NA) ) %>%
    mutate(Conditie = str_replace(Conditie, "IOS_", "")) %>%
    arrange(Nr_crt) %>%
    select(Conditie) %>% na.omit() 
Date$Conditie <- Conditie$Conditie     # tidyverse returns tibble, must do this
IOS <- Date %>% 
  mutate(IOS = coalesce(IOS_mama, IOS_tata, IOS_iubit, IOS_prieten, IOS_personalitate)) %>%
  select(IOS)
Date$IOS <- IOS$IOS   # tidyverse returns tibble, must do this
rm(Conditie, IOS)    # remove 2 tibbles

# Scoring Stai   (convert numeric - VAS)
itemiVAS <- c(5, 6, 41, 42)

itemiStaiS_pre <- 7:26
itemiStaiS_post <- 43:62
ReversedItems <- c(1,2,5,8,10,11,15,16,19,20)

Date <- Date %>%                 
  replace(Date == "na", NA) %>%        # scimbam codarea cu na a Doinei
  mutate_at(vars(itemiStaiS_pre), funs(as.numeric)) %>%        # facem coloanele numerice pt STAI
  mutate_at(vars(itemiStaiS_post), funs(as.numeric)) %>% 
  mutate_at(vars(itemiVAS), funs(as.numeric))

Date[ ,itemiStaiS_pre[ReversedItems]] = 5 - Date[ ,itemiStaiS_pre[ReversedItems]]
Date[ ,itemiStaiS_post[ReversedItems]] = 5 - Date[ ,itemiStaiS_post[ReversedItems]]

Date$StaiS_pre = rowSums(Date[ ,itemiStaiS_pre], na.rm=T ) * NA ^ (rowSums(!is.na(Date[ ,itemiStaiS_pre])) == 0)
Date$StaiS_post = rowSums(Date[ ,itemiStaiS_post], na.rm=T ) * NA ^ (rowSums(!is.na(Date[ ,itemiStaiS_post])) == 0)
```


## Table of derived variables

```{r table_derived_data}
varnottable <- c("Nume_Prenume", "NA_per_row", 
                 sprintf("Stais_pre_%01d", seq(1,20)), 
                 sprintf("Stais_post_%01d", seq(1,20)))

Date %>%                              
  select(-varnottable) %>%
    DT::datatable(                                  # excel downloadable  DT table
      extensions = 'Buttons',
      options = list(pageLength = 20,
                     scrollX='500px', 
                     dom = 'Bfrtip', 
                     buttons = c('excel', "csv")))
```


<br>
<br>


# Conditions

```{r cond_count}
## Number of subjects per Condition
Date %>% 
  count(Conditie) %>%
  knitr::kable(caption = "Number of subjects per Condition")
```

```{r cond_plot, fig.width = 10, fig.asp = 0.8}
## Means for all variables by Condition
# Date %>% 
#   select(ID, 
#          Vas_rel_global, Vas_rel_arousal, 
#          CRQ_1, CRQ_2, CRQ_3, CRQ_4, CRQ_5, CRQ_6, 
#          Conditie, IOS) %>%
#   group_by(Conditie) %>%
#   summarise_if(.predicate = function(x) is.numeric(x),
#              .funs = funs(mean="mean"))

## Plot CRQ items
my_comparisons <- 
  gtools::combinations(n = length(unique(Date$Conditie)), r = 2, v = Date$Conditie, repeats.allowed = FALSE) %>%
  as.data.frame() %>% 
  mutate_if(is.factor, as.character) %>%
  purrr::pmap(list) %>% 
  lapply(unlist)
  
Date %>% 
  select(ID, Conditie, 
         CRQ_1, CRQ_2, CRQ_3, CRQ_4, CRQ_5, CRQ_6) %>%
  gather(variable, value, CRQ_1:CRQ_6) %>%
  mutate(Conditie = factor(Conditie, levels = sort(unique(Conditie)))) %>%   # relevel just to match combination pattern for comparison
    ggboxplot(x = "Conditie", y = "value", facet.by = "variable" ) + 
    stat_compare_means(comparisons = my_comparisons,            # can't do paired t test because not all arguments have the same length  
                       label = "p.signif", paired = FALSE, method = "t.test",  na.rm = TRUE) +
    scale_x_discrete(labels = abbreviate)

## Plot VAS Rel and IOS
func_boxcomp_cond <- function(var){
    Date %>% 
      select(Conditie, var) %>%
      mutate(Conditie = factor(Conditie, levels = sort(unique(Conditie)))) %>%   # relevel just to match combination pattern for comparison
        ggboxplot(x = "Conditie", y = var, title = var) +
        stat_compare_means(comparisons = my_comparisons,            # can't do paired t test because not all arguments have the same length  
                           label = "p.signif", paired = FALSE, method = "t.test",  na.rm = TRUE)
}

plot_vasglob <- func_boxcomp_cond("Vas_rel_global")
plot_vasarou <- func_boxcomp_cond("Vas_rel_arousal")
plot_ios <- func_boxcomp_cond("IOS")
ggarrange(plot_vasglob, 
          plot_ios, 
          plot_vasarou, 
          ncol = 2, nrow = 2)
```


<br>
<br>

# STAI-Y

## Plots with p values
```{r stai_plot, fig.width = 10, fig.asp = 0.8}
## STAI plot 
Staimelt <- Date[, c("ID", "Conditie", "StaiS_pre","StaiS_post")] %>% 
  gather("StaiS_pre", "StaiS_post", key = "Stai_cond", value = "value") %>% 
  mutate_at(vars(c(1, 2, 3)), funs(as.factor)) %>% 
  mutate(Stai_cond = factor(Stai_cond, levels = c("StaiS_pre","StaiS_post"))) # %>%    # change factor order for plot pre, post

ggplot(Staimelt, aes(x = Stai_cond, y = value)) +
  geom_boxplot() +
  facet_wrap(~Conditie) +
  ggpubr::stat_compare_means(method = "t.test", paired = TRUE, comparisons = list(c("StaiS_pre","StaiS_post")))
```

## t tests
```{r stai_ttest}
## STAI tables
Date %>% 
  group_by(Conditie) %>% 
  do(broom::tidy(t.test(.$StaiS_pre, 
                        .$StaiS_post, 
                        mu = 0, 
                        alt = "two.sided", 
                        paired = TRUE, 
                        conf.level = 0.95))) %>%
  knitr::kable(digits = 2)
```


<br>

# VAS Stres

## Plots with p values
```{r vasS_plot, fig.width = 10, fig.asp = 0.8}
## Vas Stres plot 
Vasstresmelt <- Date[, c("ID", "Conditie", "Vas_stres_pre","Vas_stres_post")] %>% 
  gather("Vas_stres_pre","Vas_stres_post", key = "Vas_stres_cond", value = "value") %>% 
  mutate_at(vars(c(1,2,3)), funs(as.factor)) %>% 
  mutate_at(vars(c(4)), funs(as.numeric)) %>% 
  mutate(Vas_stres_cond = factor(Vas_stres_cond, levels = c("Vas_stres_pre","Vas_stres_post"))) # change factor order for plot pre, post

ggplot(Vasstresmelt, aes(x = Vas_stres_cond, y = value)) +
  geom_boxplot() +
  facet_wrap(~Conditie) +
  ggpubr::stat_compare_means(method = "t.test", paired = TRUE, comparisons = list(c("Vas_stres_pre","Vas_stres_post")))
```

## t tests
```{r vasS_ttest}
## Vas Stres tables
Date %>% 
  group_by(Conditie) %>% 
  do(broom::tidy(t.test(.$Vas_stres_pre, 
                        .$Vas_stres_post, 
                        mu = 0, 
                        alt = "two.sided", 
                        paired = TRUE, 
                        conf.level = 0.95))) %>%
  knitr::kable(digits = 2)
```


<br>

# VAS Wellbeing

## Plots with p values
```{r vasB_plot, fig.width = 10, fig.asp = 0.8}
## Vas Stres plot 
Vasbinemelt <- Date[, c("ID", "Conditie", "Vas_bine_pre","Vas_bine_post")] %>% 
  gather("Vas_bine_pre","Vas_bine_post", key = "Vas_stres_cond", value = "value") %>% 
  mutate_at(vars(c(1,2,3)), funs(as.factor)) %>% 
  mutate_at(vars(c(4)), funs(as.numeric)) %>% 
  mutate(Vas_stres_cond = factor(Vas_stres_cond, levels = c("Vas_bine_pre","Vas_bine_post"))) # change factor order for plot pre, post

ggplot(Vasbinemelt, aes(x = Vas_stres_cond, y = value)) +
  geom_boxplot() +
  facet_wrap(~Conditie) +
  ggpubr::stat_compare_means(method = "t.test", paired = TRUE, comparisons = list(c("Vas_bine_pre","Vas_bine_post")))
```

## t tests
```{r vasB_ttest}
## Vas Stres tables
Date %>% 
  group_by(Conditie) %>% 
  do(broom::tidy(t.test(.$Vas_bine_pre, 
                        .$Vas_bine_post, 
                        mu = 0, 
                        alt = "two.sided", 
                        paired = TRUE, 
                        conf.level = 0.95))) %>%
  knitr::kable(digits = 2)
```

<br>
<br>

# Conditioning on VAS global

## STAI-Y
```{r reg_stai_vasglobal}
## STAY
lm_stai <- lm(StaiS_post ~ StaiS_pre + Vas_rel_global, data = Date)
apa_lm_stai <- apa_print(lm_stai)
# apa_table(apa_lm_stai$table,
#   caption = "Table",
#   escape = FALSE,
#   format = "markdown")               # doesnt render the caption and it cant be removed
knitr::kable(apa_lm_stai$table)

# apa_lm_stai$full_result$modelfit$r2

par(mfrow = c(1, 2)); termplot(lm_stai, partial.resid = TRUE, se = TRUE)

```

<span style="font-size:150%;">*Is there an interaction Condition x Vas rel global?*</span>
```{r interac_stai_vasglobal}
lm_stai_inter <- lm(StaiS_post ~ StaiS_pre + Conditie * Vas_rel_global, data = Date)

knitr::kable(apa_print(lm_stai_inter)$table)

plot(visreg::visreg(lm_stai_inter, xvar = "Vas_rel_global", by = "Conditie", plot = FALSE),
            overlay = TRUE, partial = FALSE, rug = FALSE,
            xlab = "Vas_rel_global", ylab = "Predicted STAI",
            line = list(
            lty = c(1:4, 6),     # 5 is long dash and doesnt look nice   
            col = c("black", "grey90", "grey70", "grey50", "grey30")),
            band = FALSE)
```


```{r stai_plot_cond, fig.width = 10, fig.asp = 0.8}
## STAI plot Cond
Staimelt_cond <- 
  Date %>%
  filter(Vas_rel_global >= 7) %>%
  select(ID, Conditie, StaiS_pre, StaiS_post) %>%
  gather("StaiS_pre", "StaiS_post", key = "Stai_cond", value = "value") %>% 
  mutate_at(vars(c(1, 2, 3)), funs(as.factor)) %>% 
  mutate(Stai_cond = factor(Stai_cond, levels = c("StaiS_pre","StaiS_post"))) # %>%    # change factor order for plot pre, post

ggplot(Staimelt_cond, aes(x = Stai_cond, y = value)) +
  geom_boxplot() +
  facet_wrap(~Conditie) +
  ggpubr::stat_compare_means(method = "t.test", paired = TRUE, comparisons = list(c("StaiS_pre","StaiS_post")))
```

## VAS Stres
```{r reg_vasS_vasglobal}
## STAY
lm_vasS <- lm(Vas_stres_post ~ Vas_stres_pre + Vas_rel_global, data = Date)
apa_lm_vasS <- apa_print(lm_vasS)
knitr::kable(apa_lm_vasS$table)

par(mfrow=c(1,2)); termplot(lm_vasS, partial.resid = TRUE, se = TRUE)
```

<span style="font-size:150%;">*Is there an interaction Condition x Vas rel global?*</span>
```{r interac_vasS_vasglobal}
lm_vasS_inter <- lm(Vas_stres_post ~ Vas_stres_pre + Conditie * Vas_rel_global, data = Date)

knitr::kable(apa_print(lm_vasS_inter)$table)

plot(visreg::visreg(lm_vasS_inter, xvar = "Vas_rel_global", by = "Conditie", plot = FALSE),
            overlay = TRUE, partial = FALSE, rug = FALSE,
            xlab = "Vas_rel_global", ylab = "Predicted VAS Stress",
            line = list(
            lty = c(1:4, 6),     # 5 is long dash and doesnt look nice   
            col = c("black", "grey90", "grey70", "grey50", "grey30")),
            band = FALSE)
```

```{r vasS_plot_cond, fig.width = 10, fig.asp = 0.8}
## Vas Stres plot 
Vasstresmelt_cond <- 
  Date %>%
  filter(Vas_rel_global >= 7) %>%
  select(ID, Conditie, Vas_stres_pre, Vas_stres_post) %>%
  gather("Vas_stres_pre","Vas_stres_post", key = "Vas_stres_cond", value = "value") %>% 
  mutate_at(vars(c(1,2,3)), funs(as.factor)) %>% 
  mutate_at(vars(c(4)), funs(as.numeric)) %>% 
  mutate(Vas_stres_cond = factor(Vas_stres_cond, levels = c("Vas_stres_pre","Vas_stres_post"))) # change factor order for plot pre, post

ggplot(Vasstresmelt_cond, aes(x = Vas_stres_cond, y = value)) +
  geom_boxplot() +
  facet_wrap(~Conditie) +
  ggpubr::stat_compare_means(method = "t.test", paired = TRUE, comparisons = list(c("Vas_stres_pre","Vas_stres_post")))
```

## VAS Wellbeing
```{r reg_vasB_vasglobal}
## STAY
lm_vasB <- lm(Vas_bine_post ~ Vas_bine_pre + Vas_rel_global, data = Date)
apa_lm_vasB <- apa_print(lm_vasB)
knitr::kable(apa_lm_vasB$table)

par(mfrow=c(1,2)); termplot(lm_vasB, partial.resid = TRUE, se = TRUE)
```

<span style="font-size:150%;">*Is there an interaction Condition x Vas rel global?*</span>
```{r interac_vasB_vasglobal}
lm_vasB_inter <- lm(Vas_bine_post ~ Vas_bine_pre + Conditie * Vas_rel_global, data = Date)

knitr::kable(apa_print(lm_vasB_inter)$table)

plot(visreg::visreg(lm_vasB_inter, xvar = "Vas_rel_global", by = "Conditie", plot = FALSE),
            overlay = TRUE, partial = FALSE, rug = FALSE,
            xlab = "Vas_rel_global", ylab = "Predicted VAS Wellbeing",
            line = list(
            lty = c(1:4, 6),     # 5 is long dash and doesnt look nice   
            col = c("black", "grey90", "grey70", "grey50", "grey30")),
            band = FALSE)
```

```{r vasB_plot_cond, fig.width = 10, fig.asp = 0.8}
## Vas Stres plot 
Vasbinemelt_cond <- 
  Date %>%
  filter(Vas_rel_global >= 7) %>%
  select(ID, Conditie, Vas_bine_pre, Vas_bine_post) %>%
  gather("Vas_bine_pre","Vas_bine_post", key = "Vas_bine_cond", value = "value") %>% 
  mutate_at(vars(c(1,2,3)), funs(as.factor)) %>% 
  mutate_at(vars(c(4)), funs(as.numeric)) %>% 
  mutate(Vas_bine_cond = factor(Vas_bine_cond, levels = c("Vas_bine_pre","Vas_bine_post"))) # change factor order for plot pre, post

ggplot(Vasbinemelt_cond, aes(x = Vas_bine_cond, y = value)) +
  geom_boxplot() +
  facet_wrap(~Conditie) +
  ggpubr::stat_compare_means(method = "t.test", paired = TRUE, comparisons = list(c("Vas_bine_pre","Vas_bine_post")))
```

<br>
<br>
<br>
<br>

# Melt dataframe for future analyses

```{r wideformat_data}
# Data from Long to Wide
meltDate <- 
  Date %>% 
    select(ID, Conditie, 
           Vas_stres_pre, Vas_stres_post,
           Vas_bine_pre, Vas_bine_post,
           StaiS_pre, StaiS_post) %>%
      gather(variable, value, Vas_stres_pre:StaiS_post) %>%
      unite(VarCond, variable, Conditie) %>% 
      spread(VarCond, value)

# Some rownames are typos (ID 1 and 26)
func_collapseduplicate <- function(x) {           # collapses duplicate rows, but if all are NA returns NA
  sum(x, na.rm=T ) * NA ^ (sum(!is.na(x)) == 0)
}

meltDate <-
  meltDate %>%
    mutate(ID = word(ID, 1)) %>%
    group_by(ID) %>% 
    summarise_all(func_collapseduplicate)

  
# Test if all results are the same -- all seems good
# t.test(meltDate$Vas_bine_pre_prieten, meltDate$Vas_bine_post_prieten, 
#                         mu = 0, 
#                         alt = "two.sided", 
#                         paired = TRUE, 
#                         conf.level = 0.95)

meltDate %>%
      DT::datatable(                                  # excel downloadable  DT table
      extensions = 'Buttons',
      options = list(pageLength = 20,
                     scrollX='500px', 
                     dom = 'Bfrtip', 
                     buttons = c('excel', "csv")))
```



<!-- Session Info and License -->

<br>

# Session Info
```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->
&nbsp;
<hr />
<p style="text-align: center;">A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a></p>
<p style="text-align: center;"><span style="color: #808080;"><em>claudiu.papasteri@gmail.com</em></span></p>
&nbsp;
