---
title: "<br> QMet therapists study" 
subtitle: "Initial Analysis"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    # pdf_document: 
            # toc: true
            # toc_depth: 2
            # number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---


<!-- Setup -->


```{r setup, include=FALSE}
# General R options
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation
options(repos = c(getOption("repos")["CRAN"], CRANextra = "https://mirror.clientvps.com/CRAN/"))  # use CRAN as default, set CRANextra to Nürnberg mirror

if (!require("pacman")) install.packages("pacman", dependencies = TRUE)
if (!require("tidyverse")) install.packages("tidyverse", dependencies = TRUE)
packages <- c(
  "papaja",
  "here", "fs",
  "conflicted",
  "rio",
  "psych",          
  "ggstatsplot",
  "ggplot2", "scales",
  "report",
  "gtsummary",
  "XML",
  "qmethod"
  # , ...
)
pacman::p_load(char = packages, update = FALSE)

# Set here to Rnotebook directory
here::set_here()
unloadNamespace("here")                   # need new R session or unload namespace for .here file to take precedence over .Rproj
notebook_name <- fs::path_file(here::here())

# Solve conflicts in favor of tidyverse
conflicted::conflict_prefer("filter", winner = "dplyr")
conflicted::conflict_prefer("select", winner = "dplyr")
conflicted::conflict_prefer("slice", winner = "dplyr")
conflicted::conflict_prefer("rename", winner = "dplyr")
conflicted::conflict_prefer("count", winner = "dplyr")
conflicted::conflict_prefer("recode", winner = "dplyr")
conflicted::conflict_prefer("fill", winner = "tidyr")

# Set kintr options including root.dir pointing to the .here file in Rnotebook directory
knitr::opts_chunk$set(
  root.dir = here::here(),
  #fig.width = 5, fig.asp = 1/3, 
  comment = "#",
  collapse = TRUE,
  echo = TRUE, warning = TRUE, message = TRUE, cache = TRUE       # echo = False for github_document, but will be folded in html_notebook
)

# Themes for ggplot2 plotting (here used APA style)
theme_set(papaja::theme_apa())
```





<!-- Functions -->

# Define functions

```{r}
## Define function that recodes to numeric, but watches out to coercion to not introduce NAs
colstonumeric <- function(df){
  tryCatch({
    df_num <- as.data.frame(
      lapply(df,
             function(x) { as.numeric(as.character(x))})) 
  },warning = function(stop_on_warning) {
    message("Stoped the execution of numeric conversion: ", conditionMessage(stop_on_warning))
  }) 
}
##
## Define function that reverse codes items
ReverseCode <- function(df, tonumeric = FALSE, min = NULL, max = NULL) {
  if(tonumeric) df <- colstonumeric(df)
  df <- (max + min) - df
}
##
## Define function that scores only rows with less than 10% NAs (returns NA if all or above threshold percentage of rows are NA); can reverse code if vector of column indexes and min, max are provided.
ScoreLikert <- function(df, napercent = .1, tonumeric = FALSE, reversecols = NULL, min = NULL, max = NULL, engine = "sum") {
  reverse_list <- list(reversecols = reversecols, min = min, max = max)
  reverse_check <- !sapply(reverse_list, is.null)
  
  # Recode to numeric, but watch out to coercion to not introduce NAs
  colstonumeric <- function(df){
    tryCatch({
      df_num <- as.data.frame(
        lapply(df,
               function(x) { as.numeric(as.character(x))})) 
    },warning = function(stop_on_warning) {
      message("Stoped the execution of numeric conversion: ", conditionMessage(stop_on_warning))
    }) 
  }
  
  if(tonumeric) df <- colstonumeric(df)
  
  if(all(reverse_check)){
    df[ ,reversecols] <- (max + min) - df[ ,reversecols]
  }else if(any(reverse_check)){
    stop("Insuficient info for reversing. Please provide: ", paste(names(reverse_list)[!reverse_check], collapse = ", "))
  }
  
  if(engine == "sum") {
    return(
      ifelse(rowSums(is.na(df)) > ncol(df) * napercent,
             NA,
             rowSums(df, na.rm = TRUE) * NA ^ (rowSums(!is.na(df)) == 0)
      )
    )  
  }
  
  if(engine == "mean") {
    return(
      ifelse(rowMeans(is.na(df)) > ncol(df) * napercent,
             NA,
             rowMeans(df, na.rm = TRUE) * NA ^ (rowSums(!is.na(df)) == 0)
      )       
    )
  }
  
    if(engine == "mean_na") {
      df[is.na(df)] <- 0
      rowMeans(df)
    }
}
```

## Quick ggbetweenstats function

```{r}
# For publication
library(ggprism)
savefolder <- r'(E:\PROJECTS\QMet therapist study\zzz graphs)'

my_ggbetweenstats <- function(data, title, x, y, outlier.label, xlab, ylab, 
                              outlier.tagging = FALSE, results.subtitle = FALSE, 
                              centrality.label.args = FALSE, point.path = TRUE,
                              ...) {  # ... for limits and breaks
  x <- rlang::enquo(x)
  y <- rlang::enquo(y)
  outlier.label <- rlang::enquo(outlier.label)
  
  if(centrality.label.args){
    centrality.label.args <- list(size = 3, nudge_x = 0.2, segment.linetype = 5, fill = "#FFF8E7")
  }else{
    centrality.label.args <- list(size = 0, nudge_x = 0.2, segment.linetype = 0, alpha = 0) # very hacky way of not showing label
  }
  
  plot <- 
    data %>%
      ggstatsplot::ggbetweenstats(
        x = !!x,
        y = !!y,
        title = title,
        xlab = xlab,
        ylab = ylab,
        outlier.tagging = outlier.tagging,                    # whether outlines need to be tagged
        outlier.label = !!outlier.label,                      # variable to be used for tagging outliers
        outlier.coef = 2,
        pairwise.comparisons = TRUE,
        pairwise.display = "significant",
        results.subtitle = results.subtitle,
        type = "np",
        bf.message = FALSE, 
        p.adjust.method = "none",
        point.path = point.path,
        ggtheme = ggprism::theme_prism(palette = "black_and_white"),
        # package = "RColorBrewer",  # "ggsci",
        # palette = "Dark",         # "default_jco",
        violin.args = list(width = 0.9, alpha = 0.2, size = 1, color = "black"),
        centrality.plotting = TRUE,
        centrality.type = "np",
        centrality.point.args = list(size = 5, color = "black"),
        centrality.path.args = list(color = "black", size = 1, alpha = 1),
        centrality.label.args = centrality.label.args,
        ggplot.component = list(
          theme(
            plot.title = element_text(hjust = 0, size = 16),
            plot.subtitle = element_text(hjust = 0, size = 12), 
            plot.caption = element_text(hjust = 0, size = 12), 
            text = element_text(family = "Sans", size = 14)
        ))
      ) + scale_colour_grey(start = 0.2, end = 0.2) +  # hacky way to change point color
      scale_y_continuous(...)
  
  plot
}

# Fast ggsave - saves plot with filename of R plot object
fast_ggsave <- function(plot, device = "tiff", path = NULL,
                        units = "in", dpi = 300, width = 5, height = 5, ...){ 
  plot_name <- deparse(substitute(plot))
  ggplot2::ggsave(filename = paste0(plot_name, ".", device), plot = plot,
                  device = device, path = path,
                  units = units, dpi = dpi,
                  width = width, height = height,
                  ...
  )
  
} # use: fast_ggsave(jrad_ox_p, path = savefolder)

# Fast tiff save
fast_tiffsave <- function(plot, path = NULL,
                          units = "in", res = 300, width = 5, height = 5, ...){ 
  plot_name <- deparse(substitute(plot))
  tiff(filename = file.path(path, paste0(plot_name, ".", "tiff")),
       units = units, res = res,
       width = width, height = height,
       ...
  )
  plot(plot)
  dev.off()
}  # use: fast_tiffsave(jrad_ox_p, path = savefolder)

# Errors with ggplot2  --- can use this to save:
# Cairo::Cairo(
#   width = 5, 
#   height = 5, 
#   file = file.path(savefolder, paste0("jrad_ox_p", ".", "tiff")),
#   type = "png", 
#   bg =  "white",    # "transparent" 
#   dpi = 300,
#   units = "in"
# )
# plot(jrad_ox_p) 
# dev.off()
```

<!-- Report -->

# Read survey structure

```{r}
# LimeSurvey export survey as .txt (.xml is good too, but easier to work with .txt)
survey_df <- readr::read_delim("limesurvey_survey_192485.txt", delim = '\t')
survey_df <- 
  survey_df %>%
  select_if(~ !all(is.na(.)))

survey_codetext <-
  survey_df %>%
  select(name, text) %>%
  slice(
    seq(
      from = min(which(str_detect(name, "nt Informat"))),
      to = nrow(.)
  )) %>%
  mutate(row_no = row_number()) %>%
  relocate(row_no)
```


```{r, eval=FALSE}
DT::datatable(                # give error on Notbook render
  survey_codetext[3:nrow(survey_codetext),],
  extensions = "Buttons",
  fillContainer = TRUE,
  rownames = FALSE,
  selection = "multiple",
  # style = "bootstrap", 
  # class = "compact", #width = "1000px",
  options = list(
    #autowidth = TRUE,
    deferRender = FALSE,
    pageLength = 30,
    scrollX = "100px",
    # scrollY = "400px"
    dom = "Bfrtip",
    buttons = c("excel", "csv")
  )
)
```



# Item coding based on survey structure

```{r}
item_codetext <-
  survey_codetext %>%
  slice(
    seq(
      from = which(str_detect(name, "Demografice")) + 1,
      to = nrow(.)
  )) %>%
  mutate(
    clean_text = str_remove_all(text, "<.*?>"),                           # remove HTML tags
    is_question = str_detect(name, "^G0.*"),                               # tag questions
    is_subquestion = str_detect(name, "^SQ.*"),                            # tag subquestions
    is_answer = str_detect(name, "^AO.*"),                                 # tag answer definitions
    quest_no = cumsum(is_question),                                       # number all questions
    question = if_else(is_question, name, NA_character_),                 # get question codes
    subquestion = if_else(is_subquestion, name, NA_character_),           # get subquestion codes
    question_text = if_else(is_question, clean_text, NA_character_),                 # get question texts
    subquestion_text = if_else(is_subquestion, clean_text, NA_character_),           # get subquestion texts
    answer = 
      if_else(is_answer, 
        paste0("\"", name, "\"", " = ", "\"", clean_text, "\""), 
        NA_character_
      )                                                                   # paste definition of each answer
  ) %>%
  fill(question, .direction = "down") %>%                   # fill with same question, it appies for subquestions and answers
  filter(is_question | is_subquestion | is_answer)                        # drop sections and other useless info

# Full info on items as list-columns dataframe
item_info <-
  item_codetext %>%
  select(question, subquestion, question_text, subquestion_text, answer) %>%
  pivot_longer(cols = -question, values_drop_na = TRUE) %>%
  pivot_wider(names_from = name, values_from = value, values_fn = list)


# Meant to be used as: 
# def <- c("foo" = "bar", "zar" = "far")
# dplyr::recode(as.character(col), !!!def)
# e.g. item_def$answer[item_def$question == "G02Q03"]
#      eval(parse(text = item_def$answer[item_def$question == "G02Q03"]))

item_def <-
  item_codetext %>%
  filter(is_answer) %>%
  select(question, answer) %>%
  group_by(question) %>%
  mutate(answer = paste0(answer, collapse = ", "),
         answer = paste0("c(", answer, ")")) %>%
  distinct()

#e.g. on how to use item_def
# test_df <- 
#   df %>%
#   mutate(
#     across(
#       .cols = starts_with("G02Q03"),
#       .fns = ~recode(., !!!eval(parse(text = item_def$answer[item_def$question == "G02Q03"])))     
#     )
#   )  
```

```{r, eval=FALSE}
DT::datatable(                # give error on Notbook render
  item_def,
  extensions = "Buttons",
  fillContainer = TRUE,
  rownames = FALSE,
  selection = "multiple",
  # style = "bootstrap", 
  # class = "compact", #width = "1000px",
  options = list(
    #autowidth = TRUE,
    deferRender = FALSE,
    pageLength = 15,
    scrollX = "100px",
    # scrollY = "400px"
    dom = "Bfrtip",
    buttons = c("excel", "csv")
  )
)
```

# Read data & transform

```{r}
df <- readr::read_csv("survey_192485_R_data_file.csv")

# test_df <- 
#   map_dfc(
#     item_def$question,
#     \(x) {
#       map(
#         df %>%
#           select(contains(x)),
#         \(y) recode(y, !!!eval(parse(text = item_def$answer[str_detect(item_def$question, x)])))
#       )
#     }
#   )

# Need to find a way to iterate this with purrr
df_recoded <-
  df %>%
  mutate(
    across(
      .cols = starts_with(item_def$question[1]),
      .fns = ~recode(., !!!eval(parse(text = item_def$answer[str_detect(item_def$question, item_def$question[1])])))
    ),
    across(
      .cols = starts_with(item_def$question[2]),
      .fns = ~recode(., !!!eval(parse(text = item_def$answer[str_detect(item_def$question, item_def$question[2])])))
    ),
    across(
      .cols = starts_with(item_def$question[3]),
      .fns = ~recode(., !!!eval(parse(text = item_def$answer[str_detect(item_def$question, item_def$question[3])])))
    ),
    across(
      .cols = starts_with(item_def$question[4]),
      .fns = ~recode(., !!!eval(parse(text = item_def$answer[str_detect(item_def$question, item_def$question[4])])))
    ),
    across(
      .cols = starts_with(item_def$question[5]),
      .fns = ~recode(., !!!eval(parse(text = item_def$answer[str_detect(item_def$question, item_def$question[5])])))
    ),
    across(
      .cols = starts_with(item_def$question[6]),
      .fns = ~recode(., !!!eval(parse(text = item_def$answer[str_detect(item_def$question, item_def$question[6])])))
    ),
    across(
      .cols = starts_with(item_def$question[7]),
      .fns = ~recode(., !!!eval(parse(text = item_def$answer[str_detect(item_def$question, item_def$question[7])])))
    ),
    across(
      .cols = starts_with(item_def$question[8]),
      .fns = ~recode(., !!!eval(parse(text = item_def$answer[str_detect(item_def$question, item_def$question[8])])))
    ),
    across(
      .cols = starts_with(item_def$question[9]),
      .fns = ~recode(., !!!eval(parse(text = item_def$answer[str_detect(item_def$question, item_def$question[9])])))
    ),
    across(
      .cols = starts_with(item_def$question[10]),
      .fns = ~recode(., !!!eval(parse(text = item_def$answer[str_detect(item_def$question, item_def$question[10])])))
    )
  )

# To numeric and rescale questionnaire items 
# for numeric extraction: str_extract(x, "[0-9]")   # "[0-9]+" for more digits, but Liker scales have only 1 digit
# [8]  = G04Q10 = Reactiv [1, 7]
# [9]  = G05Q11 = Empath [0, 4]
# [10] = G06Q12 = Online_Terap [1, 5]
#        G07Q13 = QSort (is already numeric, but needs to be on scale [-4, +4])

df_recoded2 <-
  df_recoded %>%
  mutate(
    across(
      .cols = starts_with(c("G04Q10", "G05Q11", "G06Q12")),
      .fns = ~as.numeric(str_extract(., "[0-9]"))     # get only digits and to numeric
    ),
    across(
      .cols = starts_with("G07Q13"),
      .fns = ~((.-5)*(-1))                           # to [-4, +4], where 1=+4, 9=-4
    )
  )
# check - everything fine
# df_recoded2 %>% select(starts_with("G04Q10")) %>% summary()
# df_recoded2 %>% select(starts_with("G05Q11")) %>% summary()
# df_recoded2 %>% select(starts_with("G06Q12")) %>% summary()
# df_recoded2 %>% select(starts_with("G07Q13")) %>% summary()

```

## Scoring IRI

```{r}
## IRI
# Scales with reversed c(3,4,7,12,13,14,15,18,19)         min = 0, max = 4
# Empathic Concern   - IRI_EC c(1,5,7,12,16,23,26)
# Perspective Taking - IRI_PT c(3,8,11,15,21,25,28)
# Fantasy            - IRI_F  c(2,4,9,14,18,20,22)
# Personal Distress  - IRI_PD c(6,10,13,17,19,24,27)
idx_iri <- df_recoded2 %>% select(starts_with("G05Q11")) %>% colnames()
idx_item_iri_rev <- c(3,4,7,12,13,14,15,18,19) %>% sprintf('%0.3d', .) %>% paste0("G05Q11[SQ", . ,"]")
idx_item_iri_ec <- c(1,5,7,12,16,23,26) %>% sprintf('%0.3d', .) %>% paste0("G05Q11[SQ", . ,"]")
idx_item_iri_pt <- c(3,8,11,15,21,25,28) %>% sprintf('%0.3d', .) %>% paste0("G05Q11[SQ", . ,"]")
idx_item_iri_f <- c(2,4,9,14,18,20,22) %>% sprintf('%0.3d', .) %>% paste0("G05Q11[SQ", . ,"]")
idx_item_iri_pd <- c(6,10,13,17,19,24,27) %>% sprintf('%0.3d', .) %>% paste0("G05Q11[SQ", . ,"]")

df_recoded2$IRI_EC <- ScoreLikert(df_recoded2[idx_item_iri_ec], reversecols = intersect(idx_item_iri_rev, idx_item_iri_ec), napercent = .9, min = 0, max = 4)
df_recoded2$IRI_PT <- ScoreLikert(df_recoded2[idx_item_iri_pt], reversecols = intersect(idx_item_iri_rev, idx_item_iri_pt), napercent = .9, min = 0, max = 4)
df_recoded2$IRI_F  <- ScoreLikert(df_recoded2[idx_item_iri_f], reversecols = intersect(idx_item_iri_rev, idx_item_iri_f), napercent = .9, min = 0, max = 4)
df_recoded2$IRI_PD <- ScoreLikert(df_recoded2[idx_item_iri_pd], reversecols = intersect(idx_item_iri_rev, idx_item_iri_pd), napercent = .9, min = 0, max = 4)

```

## Scoring UTAUT (Online Therapy)

```{r}
# UTAUT
# Scales with reversed c(5,9,11,20,21)         min = 1, max = 5
# Therapy Quality Expectation: 1,2,5R,6,9R,11R,15,17,21R; - UT_QE c(1,2,5,6,9,11,15,17,21)
# Ease of use: 12,14,18,20R;                              - UT_EU c(12,14,18,20)
# Pressure from others: 4,16;                             - UT_PO c(4,16)
# Professional Support: 8,19;                             - UT_PS c(8,19) 
# Convenience: 3,13;                                      - UT_C  c(3,13)
# Behavior intention: 7,10                                - UT_BI c(7,10)
idx_ut <- df_recoded2 %>% select(starts_with("G06Q12")) %>% colnames()
idx_item_ut_rev <- c(5,9,11,20,21) %>% sprintf('%0.3d', .) %>% paste0("G06Q12[SQ", . ,"]")
idx_item_ut_qe <- c(1,2,5,6,9,11,15,17,21) %>% sprintf('%0.3d', .) %>% paste0("G06Q12[SQ", . ,"]")
idx_item_ut_eu <- c(12,14,18,20) %>% sprintf('%0.3d', .) %>% paste0("G06Q12[SQ", . ,"]")
idx_item_ut_po <- c(4,16) %>% sprintf('%0.3d', .) %>% paste0("G06Q12[SQ", . ,"]")
idx_item_ut_ps <- c(8,19) %>% sprintf('%0.3d', .) %>% paste0("G06Q12[SQ", . ,"]")
idx_item_ut_c <- c(3,13) %>% sprintf('%0.3d', .) %>% paste0("G06Q12[SQ", . ,"]")
idx_item_ut_bi <- c(7,10) %>% sprintf('%0.3d', .) %>% paste0("G06Q12[SQ", . ,"]")

df_recoded2$UT_QE <- ScoreLikert(df_recoded2[idx_item_ut_qe], reversecols = intersect(idx_item_ut_rev, idx_item_ut_qe), napercent = .9, min = 1, max = 5)
df_recoded2$UT_EU <- ScoreLikert(df_recoded2[idx_item_ut_eu], reversecols = intersect(idx_item_ut_rev, idx_item_ut_eu), napercent = .9, min = 1, max = 5)
df_recoded2$UT_PO <- ScoreLikert(df_recoded2[idx_item_ut_po], napercent = .9)
df_recoded2$UT_PS <- ScoreLikert(df_recoded2[idx_item_ut_ps], napercent = .9)
df_recoded2$UT_C <- ScoreLikert(df_recoded2[idx_item_ut_c], napercent = .9)
df_recoded2$UT_BI <- ScoreLikert(df_recoded2[idx_item_ut_bi], napercent = .9)

df_recoded2$UT_Total <- rowSums(df_recoded2[, c("UT_QE", "UT_EU", "UT_PO", "UT_PS", "UT_C", "UT_BI")], na.rm = TRUE)
```


# Q Method

```{r}
# ----------------------------------------
# Item texts
item_qsort_text <- read_lines("JHP_operationalis_items.txt") %>% as.vector() 

# Grid
# 2 + 
#   3 + 
#     4 +           # 9 Important
#       5 + 
#         7 +
#       5 +         # 17 Some what important / Neutral
#     4 +
#   3 +
# 2                 # 9 Unimportant

distro <- c(
  rep(-4, 2), rep(-3, 3), rep(-2, 4), 
  rep(-1, 5), rep(0, 7), rep(1, 5),
  rep(2, 4), rep(3, 3), rep(4, 2)
)

# ----------------------------------------
# Prepare data for QMethod
# QMethod needs statements on rows and sorts on columns (t())
idx_qsort <- df_recoded2 %>% select(starts_with("G07Q13")) %>% colnames()
df_qsort_data <-
  df_recoded2[, c("id", idx_qsort)] %>%
  column_to_rownames(var = "id") %>%
  t() %>% 
  as.data.frame() 
df_qsort_text <- paste(rownames(df_qsort_data), item_qsort_text) %>% data.frame(item_text = .)
list_qsort <- list(df_qsort_data, df_qsort_text)

# ----------------------------------------
# Number of factors to extract
screeplot(prcomp(df_qsort_data), main = "Screeplot of unrotated factors", type = "l")  # 3 factors?
# psych::fa.parallel(df_recoded2[idx_qsort])
# ----------------------------------------

# Run the analysis using centroid factor extraction instead of PCA, and without rotation:
results <- qmethod::qmethod(
  df_qsort_data, nfactors = 3,
  forced = FALSE, silent = TRUE,
  distribution = distro
)
# qmethod:::summary.QmethodRes(results)
# ----------------------------------------

# Print results
results$loa %>% knitr::kable(caption = "Q-sort factor loadings")
results$flagged %>% knitr::kable(caption = "Flagged Q-sorts")  

# I think flagged  is based on some cutoff on loadings
# try_calc_flag <- !results$loa - apply(results$loa, 1, max) & abs(results$loa) >= .37
# identical(try_calc_flag, results$flagged)
# all.equal(try_calc_flag, results$flagged)   # close enough ... so it's max loading and some cutoff probably

results$zsc %>% knitr::kable(caption = "Statement z-scores")
results$zsc_n %>% knitr::kable(caption = "Statement factor scores")

results$f_char$characteristics %>% knitr::kable(caption = "Factor characteristics")
results$f_char$cor_zsc %>% knitr::kable(caption = "Correlation between factor z-scores")
results$f_char$sd_dif %>% knitr::kable(caption = "Standard error of differences between factors")
 
results$qdc %>% knitr::kable(caption = "Distinguishing and consensus statements")

# ----------------------------------------
# Plot
qmethod:::plot.QmethodRes(
  results,
  xlab = "z-scores", ylab = "",                        
  leg.pos = "topright", sort.items = FALSE
) 
# ----------------------------------------

# Order the results by the scores of each factor:
scores <- cbind(results$zsc_n, df_qsort_text)
# for (i in 1:length(results$loa)) {                 # this old code from doi:10.32614/RJ-2014-032 gives warning and additional ordering for 
#   View(                                            # unexistant factor
#     scores[base::order(scores[i], decreasing = TRUE), ],
#     title = paste0("Order for f", i)
#   )
# }

order_f1 <- 
  scores %>%
  select(fsc_f1, item_text) %>%
  arrange(desc(fsc_f1)) 
order_f1 %>% knitr::kable(caption = "Order f1") 

order_f2 <- 
  scores %>%
  select(fsc_f2, item_text) %>%
  arrange(desc(fsc_f2)) 
order_f2 %>% knitr::kable(caption = "Order f2") 

order_f3 <- 
  scores %>%
  select(fsc_f3, item_text) %>%
  arrange(desc(fsc_f3)) 
order_f3 %>% knitr::kable(caption = "Order f3") 

# ----------------------------------------

# Merge flagged/membership back to data

df_recoded2$QSort_mem <- factor(
  (results$flagged %*% (1:ncol(results$flagged))), 
  labels = c(NA_character_, colnames(results$flagged))
)
# cbind(as.data.frame(results$flagged), df_recoded2$QSort_mem) # test -- all fine

```

## New for write-up

```{r}
# for gt APA tables
devtools::source_gist("https://gist.github.com/pdparker/1b61b6d36d09cb295bf286a931990159")

results$loa %>%    # results$flagged
  as.data.frame() %>% 
  rownames_to_column(var = "id") %>%
  mutate(id = as.numeric(id)) %>% 
  left_join(df_recoded2, by = "id") %>% 
  select(id, G02Q03, G03Q10, G03Q05, f1, f2, f3) %>% 
  mutate(f1 = round(f1, 3),
         f2 = round(f2, 3),
         f3 = round(f3, 3)) %>% 
  gt::gt() %>% 
  tab_caption("Q-sort factor loadings") %>% 
  apa_style()
```

```{r}
results$f_char$characteristics %>%    # criteria to decide on the number of factors in Watts & Stenner (2012, pp.105-110)
  as.data.frame() %>% 
  rownames_to_column(var = "id") %>%
  gt::gt() %>% 
  tab_caption("Factor characteristics") %>% 
  fmt_number(columns = everything(), decimals = 3) %>%   
  apa_style()
```

```{r}
# qdc2[which(abs(qdc1[[n]]) <= sedth.05), n] <- ""
# qdc2[which(abs(qdc1[[n]]) > sedth.05), n] <- "*"
# qdc2[which(abs(qdc1[[n]]) > sedth.01), n] <- "**"
# qdc2[which(abs(qdc1[[n]]) > sedth.001), n] <- "***"
# qdc2[which(abs(qdc1[[n]]) > sedth.000001), n] <- "6*"

results$qdc %>%                # use https://journal.r-project.org/archive/2014-2/zabala.pdf
  as.data.frame() %>% 
  rownames_to_column(var = "id") %>%
  mutate(                      # strange "6*" notation is for < .000001
    sig_f1_f2 = if_else(sig_f1_f2 == "6*", "****", sig_f1_f2),
    sig_f1_f3 = if_else(sig_f1_f3 == "6*", "****", sig_f1_f3),
    sig_f2_f3 = if_else(sig_f2_f3 == "6*", "****", sig_f2_f3) 
  ) %>% 
  mutate(f1_f2 = paste(round(f1_f2, 3), sig_f1_f2, sep = " ")) %>% 
  mutate(f1_f3 = paste(round(f1_f3, 3), sig_f1_f3, sep = " ")) %>% 
  mutate(f2_f3 = paste(round(f2_f3, 3), sig_f2_f3, sep = " ")) %>% 
  select(-sig_f1_f2, -sig_f1_f3, -sig_f2_f3) %>% 
  gt::gt() %>% 
  tab_caption("Distinguishing and consensus statements") %>% 
  # fmt_number(columns = everything(), decimals = 3) %>%   
  apa_style()
```




```{r}
df_recoded222 <- 
  df_recoded2 %>% 
  mutate(QSort_mem = as.factor(na_if(as.character(QSort_mem), "NA"))) %>% 
  mutate(
    xp = case_when(
      str_detect(G03Q10, "mai pu") ~ 1L,
      str_detect(G03Q10, "1-2 ani") ~ 2L,
      str_detect(G03Q10, "2-3 ani") ~ 3L,
      str_detect(G03Q10, "3-5 ani") ~ 4L,
      str_detect(G03Q10, "5-10 ani") ~ 5L,
      str_detect(G03Q10, "peste 10 ani") ~ 6L,
      .default = NA_integer_
      ),
    Experience = case_when(
      str_detect(G03Q10, "mai pu") ~ "< 1",
      str_detect(G03Q10, "1-2 ani") ~ "1-2",
      str_detect(G03Q10, "2-3 ani") ~ "2-3",
      str_detect(G03Q10, "3-5 ani") ~ "3-5",
      str_detect(G03Q10, "5-10 ani") ~ "5-10",
      str_detect(G03Q10, "peste 10 ani") ~ "> 10",
      .default = NA_character_
      ),
    Experience = factor(Experience, 
                        levels = c("< 1", "1-2", "2-3", "3-5", "5-10", "> 10"))
  ) %>% 
  mutate( 
    G03Q05 = case_when(
      str_detect(G03Q05, "Integrativa") ~ "IE",
      str_detect(G03Q05, "Cognitiva / comportamentala") ~ "CBT",
      str_detect(G03Q05, "Umanist experien") ~ "HE",
      str_detect(G03Q05, "Psihodinamica") ~ "PD",
      .default = NA_character_
      ),
  ) %>% 
  mutate(
      Gender = G02Q03,
      School = G03Q05,
      n_course = G03Q06,
      xp_cat = G03Q10,
      tech = G03Q08) %>% 
  mutate(
    Gender = case_when(
      Gender == "Feminin" ~ "Female",
      Gender == "Masculin" ~ "Male",
      .default = NA_character_
    )
  ) %>% 
  mutate(
    Membership = case_when(
      QSort_mem == "flag_f1" ~ "F1",
      QSort_mem == "flag_f2" ~ "F2",
      QSort_mem == "flag_f3" ~ "F3",
      .default = NA_character_
    )
  ) %>% 
  select(Gender, School, n_course, tech, xp_cat, QSort_mem, Membership, xp, Experience, starts_with("IRI"), starts_with("UT"))



df_recoded2_nona <- 
  df_recoded2 %>% 
  mutate(QSort_mem = as.factor(na_if(as.character(QSort_mem), "NA"))) %>% 
  drop_na(QSort_mem) %>%
  mutate(
    xp = case_when(
      str_detect(G03Q10, "mai pu") ~ 1L,
      str_detect(G03Q10, "1-2 ani") ~ 2L,
      str_detect(G03Q10, "2-3 ani") ~ 3L,
      str_detect(G03Q10, "3-5 ani") ~ 4L,
      str_detect(G03Q10, "5-10 ani") ~ 5L,
      str_detect(G03Q10, "peste 10 ani") ~ 6L,
      .default = NA_integer_
      ),
    Experience = case_when(
      str_detect(G03Q10, "mai pu") ~ "< 1",
      str_detect(G03Q10, "1-2 ani") ~ "1-2",
      str_detect(G03Q10, "2-3 ani") ~ "2-3",
      str_detect(G03Q10, "3-5 ani") ~ "3-5",
      str_detect(G03Q10, "5-10 ani") ~ "5-10",
      str_detect(G03Q10, "peste 10 ani") ~ "> 10",
      .default = NA_character_
      ),
    Experience = factor(Experience, 
                        levels = c("< 1", "1-2", "2-3", "3-5", "5-10", "> 10"))
  ) %>% 
  mutate( 
    G03Q05 = case_when(
      str_detect(G03Q05, "Integrativa") ~ "IE",
      str_detect(G03Q05, "Cognitiva / comportamentala") ~ "CBT",
      str_detect(G03Q05, "Umanist experien") ~ "HE",
      str_detect(G03Q05, "Psihodinamica") ~ "PD",
      .default = NA_character_
      ),
  ) %>% 
  mutate(
      Gender = G02Q03,
      School = G03Q05,
      n_course = G03Q06,
      xp_cat = G03Q10,
      tech = G03Q08) %>% 
  mutate(
    Gender = case_when(
      Gender == "Feminin" ~ "Female",
      Gender == "Masculin" ~ "Male",
      .default = NA_character_
    )
  ) %>% 
  mutate(
    Membership = case_when(
      QSort_mem == "flag_f1" ~ "F1",
      QSort_mem == "flag_f2" ~ "F2",
      QSort_mem == "flag_f3" ~ "F3",
      .default = NA_character_
    )
  ) %>% 
  select(Gender, School, n_course, tech, xp_cat, QSort_mem, Membership, xp, Experience, starts_with("IRI"), starts_with("UT"))


# ggplot(df_recoded2_nona, aes(x = xp, y = UT_Total)) +
#   geom_smooth(method = "lm") +
#   geom_point(aes(color = school))
ggscatterstats(df_recoded2_nona, 
              x = xp, 
              y = UT_Total, 
              # label.var = school
              point.args = list(aes(color = School), size = 3.5),
              smooth.line.args = list(linewidth = 1, color = "black", method = "lm", formula = y ~ x),
              xsidehistogram.args = list(fill = "grey", color = "black", na.rm = TRUE),
              ysidehistogram.args = list(fill = "grey", color = "black", na.rm = TRUE)
)

ggscatterstats(df_recoded2_nona, 
              x = xp, 
              y = UT_Total, 
              # label.var = school
              point.args = list(aes(color = Membership), size = 3.5),
              smooth.line.args = list(linewidth = 1, color = "black", method = "lm", formula = y ~ x),
              xsidehistogram.args = list(fill = "grey", color = "black", na.rm = TRUE),
              ysidehistogram.args = list(fill = "grey", color = "black", na.rm = TRUE)
)



ggpiestats(  
  data = df_recoded2_nona, 
  x = QSort_mem,
  y = Gender,
  type = "np"
)

ggpiestats(  
  data = df_recoded2_nona, 
  x = QSort_mem,
  y = tech,
  type = "np"
)

pie_gender_xp_51 <- 
  ggpiestats(  
      data = df_recoded2_nona, 
      x = Experience,
      y = Gender,
      type = "np",
      results.subtitle = FALSE,
      package = "RColorBrewer",
      palette = "Blues"  
  ) + scale_fill_grey(start = 0.2, end = 1)
# fast_tiffsave(pie_gender_xp_51, path = savefolder, width = 8, height = 7)

pie_gender_xp_62 <- 
  ggpiestats(  
      data = df_recoded222, 
      x = Experience,
      y = Gender,
      type = "np",
      results.subtitle = FALSE,
      package = "RColorBrewer",
      palette = "Blues"  
  ) + scale_fill_grey(start = 0.2, end = 1)
# fast_tiffsave(pie_gender_xp_62, path = savefolder, width = 8, height = 7)


pie_gender_mem <- 
  ggpiestats(  
      data = df_recoded2_nona, 
      x = Membership,
      y = Gender,
      type = "np",
      results.subtitle = FALSE,
      package = "RColorBrewer",
      palette = "Dark2"   
  ) + scale_fill_grey(start = 0.2, end = 0.8)
# fast_tiffsave(pie_gender_mem, path = savefolder, width = 8, height = 7)

pie_mem_gender <- 
  ggpiestats(  
      data = df_recoded2_nona, 
      x = Gender,
      y = Membership,
      type = "np",
      results.subtitle = FALSE,
      package = "RColorBrewer",
      palette = "Dark2"   
  ) + scale_fill_grey(start = 0.2, end = 0.8)
# fast_tiffsave(pie_mem_gender, path = savefolder, width = 8, height = 7)

pie_xp_mem <- 
  ggpiestats(  
      data = df_recoded222, 
      x = Experience,
      y = Membership,
      type = "np",
      results.subtitle = FALSE,
      package = "RColorBrewer",
      palette = "Blues"  
  ) + scale_fill_grey(start = 0.2, end = 1)
# fast_tiffsave(pie_xp_mem, path = savefolder, width = 8, height = 7)

ggpiestats(  
  data = df_recoded2_nona, 
  x = QSort_mem,
  y = Experience,
  type = "np"
)


ggpiestats(  
  data = df_recoded2_nona, 
  x = Membership,
  y = School,
  type = "np"
)

pie_mem_school <- 
  ggpiestats(  
      data = df_recoded2_nona, 
      x = Membership,
      y = School,
      type = "np",
      results.subtitle = FALSE,
      package = "RColorBrewer",
      palette = "Dark2"  
  ) + scale_fill_grey(start = 0.2, end = 0.8)
# fast_tiffsave(pie_mem_school, path = savefolder, width = 8, height = 7) 
```

## based on membership

```{r}
###
# IRI
# ggbetweenstats(
#   data = df_recoded2_nona,
#   x = QSort_mem,
#   y = IRI_EC,
#   type = "np",
#   p.adjust.method = "none"    # "fdr"
# )

mem_iri_ec <- 
  my_ggbetweenstats(
    data = df_recoded2_nona, 
    x = Membership,
    y = IRI_EC,
    # outlier.label = ID, 
    title = "",
    xlab = "Membership",
    ylab = "Empathic Concern",
    # breaks = seq(from = 20, to = 50, by = 5),
    limits = c(0, 28)
  )
mem_iri_ec
# fast_tiffsave(mem_iri_ec, path = savefolder) 


# ggbetweenstats(
#   data = df_recoded2_nona,
#   x = QSort_mem,
#   y = IRI_PT,
#   type = "np",
#   p.adjust.method = "none"    # "fdr"
# )

mem_iri_pt <- 
  my_ggbetweenstats(
    data = df_recoded2_nona, 
    x = Membership,
    y = IRI_PT,
    # outlier.label = ID, 
    title = "",
    xlab = "Membership",
    ylab = "Perspective Taking",
    # breaks = seq(from = 20, to = 50, by = 5),
    limits = c(0, 28)
  )
mem_iri_pt
# fast_tiffsave(mem_iri_pt, path = savefolder)

# ggbetweenstats(
#   data = df_recoded2_nona,
#   x = QSort_mem,
#   y = IRI_F,
#   type = "np",
#   p.adjust.method = "none"    # "fdr"
# )

mem_iri_f <- 
  my_ggbetweenstats(
    data = df_recoded2_nona, 
    x = Membership,
    y = IRI_F,
    # outlier.label = ID, 
    title = "",
    xlab = "Membership",
    ylab = "Fantasy",
    # breaks = seq(from = 20, to = 50, by = 5),
    limits = c(0, 28)
  )
mem_iri_f
# fast_tiffsave(mem_iri_f, path = savefolder)


# ggbetweenstats(
#   data = df_recoded2_nona,
#   x = QSort_mem,
#   y = IRI_PD,
#   type = "np",
#   p.adjust.method = "none"    # "fdr"
# )

mem_iri_pd <- 
  my_ggbetweenstats(
    data = df_recoded2_nona, 
    x = Membership,
    y = IRI_PD,
    # outlier.label = ID, 
    title = "",
    xlab = "Membership",
    ylab = "Personal Distress",
    # breaks = seq(from = 20, to = 50, by = 5),
    limits = c(0, 28)
  )
mem_iri_pd
# fast_tiffsave(mem_iri_pd, path = savefolder)



###
# UT
# ggbetweenstats(   # MARGINAL
#   data = df_recoded2_nona, 
#   x = QSort_mem,
#   y = UT_QE,
#   type = "np",
#   p.adjust.method = "none"    # "fdr"
# )

mem_ut_qe <- 
  my_ggbetweenstats(
    data = df_recoded2_nona, 
    x = Membership,
    y = UT_QE,
    # outlier.label = ID, 
    title = "",
    xlab = "Membership",
    ylab = "Therapy Quality Expectation",
    # breaks = seq(from = 20, to = 50, by = 5),
    # limits = c(17, 51)
  )
mem_ut_qe
# fast_tiffsave(mem_ut_qe, path = savefolder)



# ggbetweenstats(
#   data = df_recoded2_nona, 
#   x = QSort_mem,
#   y = UT_EU,
#   type = "np",
#   p.adjust.method = "none"   # "fdr"              
# )
# 
# ggbetweenstats(
#   data = df_recoded2_nona, 
#   x = QSort_mem,
#   y = UT_PO,
#   type = "np",
#   p.adjust.method = "none"   # "fdr"              
# )
# 
# ggbetweenstats(
#   data = df_recoded2_nona, 
#   x = QSort_mem,
#   y = UT_PS,
#   type = "np",
#   p.adjust.method = "none"   # "fdr"              
# )

# ggbetweenstats(   # SIG. HERE
#   data = df_recoded2_nona, 
#   x = QSort_mem,
#   y = UT_C,
#   type = "np",
#   p.adjust.method = "none"    # "fdr"              
# )

mem_ut_c <- 
  my_ggbetweenstats(
    data = df_recoded2_nona, 
    x = Membership,
    y = UT_C,
    # outlier.label = ID, 
    title = "",
    xlab = "Membership",
    ylab = "UT_C",
    # breaks = seq(from = 20, to = 50, by = 5),
    # limits = c(17, 51)
  )
mem_ut_c
# fast_tiffsave(mem_ut_c, path = savefolder)

# ggbetweenstats(
#   data = df_recoded2_nona, 
#   x = QSort_mem,
#   y = UT_BI,
#   type = "np",
#   p.adjust.method = "none"   # "fdr"              
# )

# ggbetweenstats(   # MARGINAL -- SIG. if no adjustment
#   data = df_recoded2_nona, 
#   x = QSort_mem,
#   y = UT_Total,
#   type = "np",
#   p.adjust.method = "none"   # "fdr"
# )  # %>%   extract_stats()

mem_ut_total <- 
  my_ggbetweenstats(
    data = df_recoded2_nona, 
    x = Membership,
    y = UT_C,
    # outlier.label = ID, 
    title = "",
    xlab = "Membership",
    ylab = "Acceptance and Use of Technology (Total)",
    # breaks = seq(from = 20, to = 50, by = 5),
    # limits = c(17, 51)
  )
mem_ut_total
# fast_tiffsave(mem_ut_total, path = savefolder)
```

## based on school

```{r}
###
# IRI
# ggbetweenstats(
#   data = df_recoded2_nona, 
#   x = School,
#   y = IRI_EC,
#   type = "np",
#   p.adjust.method = "none"    # "fdr"
# )
# 
# ggbetweenstats(
#   data = df_recoded2_nona, 
#   x = School,
#   y = IRI_PT,
#   type = "np",
#   p.adjust.method = "none"    # "fdr"              
# )
# 
# ggbetweenstats(
#   data = df_recoded2_nona, 
#   x = School,
#   y = IRI_F,
#   type = "np",
#   p.adjust.method = "none"    # "fdr"              
# )
# 
# ggbetweenstats(
#   data = df_recoded2_nona, 
#   x = School,
#   y = IRI_PD,
#   type = "np",
#   p.adjust.method = "none"    # "fdr"              
# )


###
# UT
# ggbetweenstats(          # SIG. HERE
#   data = df_recoded2_nona, 
#   x = School,
#   y = UT_QE,
#   type = "np",
#   p.adjust.method = "none"    # "fdr"
# )

school_ut_qe <- 
  my_ggbetweenstats(
    data = df_recoded2_nona, 
    x = School,
    y = UT_QE,
    # outlier.label = ID, 
    title = "",
    xlab = "School",
    ylab = "Therapy Quality Expectation",
    # breaks = seq(from = 20, to = 50, by = 5),
    # limits = c(17, 51)
  )
school_ut_qe
# fast_tiffsave(school_ut_qe, path = savefolder)

# ggbetweenstats(
#   data = df_recoded2_nona, 
#   x = G03Q05,
#   y = UT_EU,
#   type = "np",
#   p.adjust.method = "none"   # "fdr"              
# )

# ggbetweenstats(            # SIG. HERE
#   data = df_recoded2_nona, 
#   x = G03Q05,
#   y = UT_PO,
#   type = "np",
#   p.adjust.method = "none"   # "fdr"              
# )

school_ut_po <- 
  my_ggbetweenstats(
    data = df_recoded2_nona, 
    x = School,
    y = UT_PO,
    # outlier.label = ID, 
    title = "",
    xlab = "School",
    ylab = "UT_PO",
    # breaks = seq(from = 20, to = 50, by = 5),
    # limits = c(17, 51)
  )
school_ut_po
# fast_tiffsave(school_ut_po, path = savefolder)


# ggbetweenstats(
#   data = df_recoded2_nona, 
#   x = G03Q05,
#   y = UT_PS,
#   type = "np",
#   p.adjust.method = "none"   # "fdr"              
# )

# ggbetweenstats(             # SIG. HERE
#   data = df_recoded2_nona, 
#   x = G03Q05,
#   y = UT_C,
#   type = "np",
#   p.adjust.method = "none"    # "fdr"              
# )

school_ut_c <- 
  my_ggbetweenstats(
    data = df_recoded2_nona, 
    x = School,
    y = UT_C,
    # outlier.label = ID, 
    title = "",
    xlab = "School",
    ylab = "UT_C",
    # breaks = seq(from = 20, to = 50, by = 5),
    # limits = c(17, 51)
  )
school_ut_c
# fast_tiffsave(school_ut_c, path = savefolder)


# ggbetweenstats(             # SIG. HERE
#   data = df_recoded2_nona, 
#   x = G03Q05,
#   y = UT_BI,
#   type = "np",
#   p.adjust.method = "none"   # "fdr"              
# )

school_ut_bi <- 
  my_ggbetweenstats(
    data = df_recoded2_nona, 
    x = School,
    y = UT_BI,
    # outlier.label = ID, 
    title = "",
    xlab = "School",
    ylab = "UT_BI",
    # breaks = seq(from = 20, to = 50, by = 5),
    # limits = c(17, 51)
  )
school_ut_bi
# fast_tiffsave(school_ut_bi, path = savefolder)



# ggbetweenstats(              # SIG. HERE
#   data = df_recoded2_nona, 
#   x = School,
#   y = UT_Total,
#   type = "np",
#   p.adjust.method = "none"   # "fdr"
# )  # %>%   extract_stats()

school_ut_total <- 
  my_ggbetweenstats(
    data = df_recoded2_nona, 
    x = School,
    y = UT_Total,
    # outlier.label = ID, 
    title = "",
    xlab = "School",
    ylab = "Acceptance and Use of Technology (Total)",
    # breaks = seq(from = 20, to = 50, by = 5),
    # limits = c(17, 51)
  )
school_ut_total
# fast_tiffsave(school_ut_total, path = savefolder)
```





## Data mining

```{r}
# df_recoded2_nona %>% explore::explore()


```



# Analyses

## Descriptives

```{r}
# "G02Q03" = gen
# "G03Q05" = scoala formare
# "G02Q06" = no cursuri formare
# "G03Q08" = tehnici scoala
# "G03Q10" = ani practica

desc_table <- 
  df_recoded2 %>%
    select(G02Q03, G03Q05, G03Q06, G03Q08, G03Q10, QSort_mem) %>%
    gtsummary::tbl_summary()
gtsummary:::print.gtsummary(desc_table, print_engine = "kable")


# df_recoded2_nona2 %>% 
#   select(QSort_mem) %>%
#   gtsummary::tbl_summary() %>%
#   gtsummary:::print.gtsummary(print_engine = "kable")

```

# QSort mem by school

```{r}
ggpiestats(  
  data = df_recoded2, 
  x = QSort_mem,
  y = G03Q05,
  type = "np"
)
```

## IRI

```{r}
ggbetweenstats(
  data = df_recoded2, 
  x = G03Q05,
  y = IRI_EC,
  type = "np"
)

ggbetweenstats(
  data = df_recoded2, 
  x = G03Q05,
  y = IRI_PT,
  type = "np"              
)

ggbetweenstats(
  data = df_recoded2, 
  x = G03Q05,
  y = IRI_F,
  type = "np"              
)

ggbetweenstats(
  data = df_recoded2, 
  x = G03Q05,
  y = IRI_PD,
  type = "np"              
)
```

```{r}
ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = IRI_EC,
  type = "np"
)

ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = IRI_PT,
  type = "np"              
)

ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = IRI_F,
  type = "np"              
)

ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = IRI_PD,
  type = "np"              
)
```

## UT 

```{r}
ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = UT_QE,
  type = "np"
)

ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = UT_EU,
  type = "np"              
)

ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = UT_PO,
  type = "np"              
)

ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = UT_PS,
  type = "np"              
)

ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = UT_C,
  type = "np"              
)

ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = UT_BI,
  type = "np"              
)

ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = UT_Total,
  type = "np"              
)
```



```{r}
grouped_ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = IRI_EC,
  grouping.var = G03Q05,
  type = "np"
)

grouped_ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = IRI_PT,
  grouping.var = G03Q05,
  type = "np"              
)

grouped_ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = IRI_F,
  grouping.var = G03Q05,
  type = "np"              
)

grouped_ggbetweenstats(
  data = df_recoded2, 
  x = QSort_mem,
  y = IRI_PD,
  grouping.var = G03Q05,
  type = "np"              
)
```



```{r export}
if(!dir.exists("Data export")) dir.create("Data export")
rio::export(df_recoded2, here::here("Data export", "Full_data.xlsx"))
rio::export(df_recoded222, here::here("Data export", "Analyses_data.xlsx"))
rio::export(item_codetext, here::here("Data export", "item_codetext.xlsx"))
rio::export(df_qsort_data, here::here("Data export", "Analyses_data_qsort.xlsx"))
rio::export(df_qsort_text, here::here("Data export", "item_codetext_qsort.xlsx"))
```






<!-- Session Info and License -->

<br>

# Session Info
```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->
&nbsp;
<hr />
<p style="text-align: center;">A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a></p>
<p style="text-align: center;"><span style="color: #808080;"><em>claudiu.papasteri@gmail.com</em></span></p>
&nbsp;
