---
title: "<br> O1A Report" 
subtitle: "Oxytocin and Cortisol"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    # pdf_document: 
            # toc: true
            # toc_depth: 2
            # number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---


<!-- Setup -->


```{r setup, include = FALSE}
# kintr options
knitr::opts_chunk$set(
  comment = "#",
  collapse = TRUE,
  echo = TRUE, warning = TRUE, message = TRUE, cache = TRUE       # echo = False for github_document, but will be folded in html_notebook
)

# General R options and info
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation

# Load packages
if (!require("pacman")) install.packages("pacman")
packages <- c(
  "tidyverse",      # best thing that happend to me
  "psych",          # general purpose toolbox for personality, psychometric theory and experimental psychology
  "papaja",         # for APA style
  "broom",          # for tidy modelling
  "ggplot2",        # best plots
  "ggpubr",         # ggplot2 to publication quality
  "DT",             # nice searchable and downloadable tables
  "summarytools",
  "plyr", 
  "rio"
  # , ...
)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(char = packages)


# Themes for ggplot2 ploting (here used APA style)
theme_set(theme_apa())
```

```{r working_directory, include = FALSE}
wd <- "C:/Users/Mihai/Desktop/R Notebooks/notebooks/o1a-report-oxy"
setwd(wd)
```


<!-- Report -->


# Load data

```{r raw_data, results = 'hide'}
## Read
Data <- rio::import("rezultate_oxitocina_pre_post_O1a_id28corectat.xlsx", sheet = "oxitocina+cortizol")
Data_PsySOP <- readRDS("Date_merged_Psy&SOP.RDS")
```


# Processing data

```{r processed_data, cache = TRUE, dependson = "raw_data"}
## Clean
Data <-
  Data %>%
    dplyr::filter(rowSums(is.na(.)) < 8) %>%               # filter out rows (no more than 7 NA on row)
    dplyr::select(which(colMeans(is.na(.)) < 0.5))         # filter out columns with Catalina's statistics (no more than 1/2 NA on column values)


## Transform in oder to be consistent with past behavioral data 
oldnames = colnames(Data)
newnames = c("ID_pre","Cortizol_pre", "Oxitocina_pre", "ID_post","Cortizol_post", "Oxitocina_post", "Conditie")

Data <-
  Data %>% 
  dplyr::rename_at(vars(oldnames), ~ newnames) %>%
  dplyr::select(-ID_post) %>%
  dplyr::mutate(ID_pre = stringr::str_remove_all(ID_pre, c(" proba A|/proba A"))) %>%     # small inconsistency "/proba"
  tidyr::separate(ID_pre,  c("ID", "Ziua", "Nr_zi"), "\\s+") %>%                          # split on white space
  dplyr::mutate(Ziua = rep("zi", length.out = n())) %>%
  tidyr::unite("Zi", c("Ziua", "Nr_zi"), sep = "", remove = TRUE) %>%
  mutate(ID = as.numeric(str_extract(ID, "[^/]+"))) %>%                                   # [^/]+ matches 1 or more chars other than /
  mutate(ID = as.character(ID))                                                             # ID Psy&SOP are char, not numeric...for merge

## Melt -- not needed here
Data_melt <-
  Data %>% 
  gather(variable, value, -ID, -Zi, -Conditie) %>%
  tidyr::separate(variable,  c("variable", "PrePost"), "_") %>%
  spread(variable, value) %>%
  mutate(PrePost = factor(PrePost, levels = c("pre","post"))) %>%
  dplyr::arrange(ID)
```

<!-- Inspect Data - switched off -->
```{r inspectdata, echo=FALSE, results="hide"} 
# print(summarytools::dfSummary(Date, style = 'grid', plain.ascii = FALSE, graph.magnif = 0.85),    # suppress output
#       method = 'render', headings = FALSE)
# str(Date, list.len=ncol(Date))  # data types are fine
```


# Merge with SOP

```{r merged_data, cache = TRUE, dependson = "processed_data"}
## Merge with Psy&SOP data
Data_merged <- left_join(Data_PsySOP, Data, by = c("ID", "Conditie"))             # all good: ID 1,4,36,42 dont have Oxy&Cort 

varnottable <- c("Nume_Prenume", "NA_per_row",
                 "IOS_mama", "IOS_tata", "IOS_iubit", "IOS_prieten", "IOS_personalitate",
                 sprintf("Stais_pre_%01d", seq(1,20)), 
                 sprintf("Stais_post_%01d", seq(1,20)))

Data_merged <- 
  Data_merged %>%
  rename_at(vars(ends_with("Pre")), funs(gsub("Pre", "pre", .))) %>%              # _Pre and _Post -> tolower ... helps for automation
  rename_at(vars(ends_with("Post")), funs(gsub("Post", "post", .))) %>%
  select(-varnottable)
```


## Table of Merged O.1.A (Psy&SOP&Oxy)

```{r table_merged_data}
Data_merged %>%                              
    DT::datatable(                                  # excel downloadable  DT table
      extensions = 'Buttons',
      options = list(pageLength = 20,
                     scrollX='500px', 
                     dom = 'Bfrtip', 
                     buttons = c('excel', "csv")))
```


<br>
<br>


# Define Functions

```{r def_func}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Define Function for mining correlations
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## Function for p-value significance -- both for func_ancova_multibox(), Get_Top_Relationships() and Correlations_With_One()
stars_signif <- function(pval) {
  stars = "ns"
  if(pval <= 0.001)
    stars = "***"
  if(pval > 0.001 & pval <= 0.01)
    stars = "**"
  if(pval > 0.01 & pval <= 0.05)
    stars = "*"
  if(pval > 0.05 & pval <= 0.1)
    stars = "."
  stars
}


## Function that returns correlations of all variables in descending order.
# Arg for threshold with default at .3 will keep only correlantions above .3 and below -.3. Also has threshhold for p-value. 
Get_Top_Relationships <- function(data_set, 
                                  correlation_abs_threshold=0.3,
                                  pvalue_threshold=0.05) {
  require(psych)
  require(dplyr)
  feature_names <- names(data_set)
  # strip var names to index for pair-wise identification
  names(data_set) <- seq(1:ncol(data_set))
  # calculate correlation and significance numbers
  cor_data_df <- psych::corr.test(data_set)
  # apply var names to correlation matrix over index
  rownames(cor_data_df$r) <- feature_names
  colnames(cor_data_df$r) <- feature_names
  # top cor and sig
  relationships_set <- cor_data_df$ci[,c('r','p')]
  # apply var names to data over index pairs
  relationships_set$feature_1 <- feature_names[as.numeric(sapply(strsplit(rownames(relationships_set), "-"), `[`, 1))]
  relationships_set$feature_2 <- feature_names[as.numeric(
    sapply(strsplit(rownames(relationships_set), "-"), `[`, 2))]
  relationships_set <- dplyr::select(relationships_set, feature_1, feature_2, r, p) %>% dplyr::rename(correlation = r, p.value = p)
  # return only the most insteresting relationships
  return(relationships_set %>%
         filter(abs(correlation) > correlation_abs_threshold &
                  p.value < pvalue_threshold) %>%
         arrange(p.value) %>%
         mutate(p.signif = sapply(p.value, function(x) stars_signif(x)))) %>%
         mutate(p.value = round(p.value, 3)) 

}


## Function for ploting correlation data frames resulting from Get_Top_Relationships and Correlations_With_One()
func_dotplot_cor <- function(df){                                        # https://www.r-pkg.org/pkg/ggpubr
  dotplotcor_scale_fill <- function(...){                                # Fix colors to signif factor levels even if missing
    ggplot2:::manual_scale(                                   
      'color', 
      values = setNames(
        c("darkgreen", "green3", "lawngreen", "yellow", "red"), 
        c("***", "**", "*", ".", "ns")), 
      ...
    )
  }                                           
  
  dtoplot_theme <- 
    ggpubr::theme_pubr() +
    theme(axis.text.y = element_text(size = 10))
  
  if(!"Variable" %in% colnames(df)){                                             # in oder to work for both Get_Top_Relationships and Correlations_With_One()
  df <- 
    df %>%                                            
      unite(cor_between, c("feature_1", "feature_2"), sep = " X ")               # unite 2 columns to x name from plot
  }else df <- df %>% dplyr::rename(cor_between = Variable)                       # change Variable to x name from plot
  
  df %>%
    ggpubr::ggdotchart(x = "cor_between", y = "correlation",
                       color = "p.signif",                                       # Color by sig
                       #   palette = c("#00AFBB", "#E7B800", "#FC4E07"),         # Custom color palette
                       sorting = "descending",                                   # Sort value in descending order
                       add = "segments",                                         # Add segments from y = 0 to dots
                       add.params = list(color = "lightgray", size = 2),         # Change segment color and size
                       group = "p.signif",                                       # Order by groups
                       dot.size = 8,                                             # Large dot size
                       xlab = "",
                       rotate = TRUE,                                            # Rotate vertically
                       label = round(.$correlation, 1),                          # Add mpg values as dot labels
                       font.label = list(color = "white", size = 9, 
                                         vjust = 0.5),                           # Adjust label parameters
                       ggtheme = dtoplot_theme) +                                # ggplot2 theme
    dotplotcor_scale_fill() +                                            # Fix colors to signif factor levels even if missing
    geom_hline(yintercept = 0, linetype = 2, color = "lightgray")
}

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## Function for t test and boxplot
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
func_t_box <- function(df, ID, Conditie, pre_var, post_var){
  df_modif <-
    df %>%
    select(ID, Conditie, pre_var, post_var) %>% 
    tidyr::drop_na() %>%
    gather(pre_var, post_var, key = "PrePost", value = "value") %>% 
    mutate_at(vars(c(1, 2)), funs(as.factor)) %>% 
    mutate(PrePost = factor(PrePost, levels = c(pre_var, post_var))) 
  
  stat_comp <-
    df_modif %>% 
    group_by(Conditie) %>% 
    do(tidy(t.test(.$value ~ .$PrePost,
                   paired = TRUE,
                   data=.)))
  
  plot <- 
    ggpubr::ggpaired(df_modif, x = "PrePost", y = "value", id = ID, 
                     color = "PrePost", line.color = "gray", line.size = 0.4,
                     palette = c("#00AFBB", "#FC4E07"), legend = "none") +
    facet_wrap(~Conditie) +
    stat_summary(fun.data = mean_se,  colour = "darkred") +
    ggpubr::stat_compare_means(method = "t.test", paired = TRUE, label.x = as.numeric(df_modif$PrePost) * 0.90, label.y = max(df_modif$value) * 1.15) + 
    ggpubr::stat_compare_means(method = "t.test", paired = TRUE, label = "p.signif", comparisons = list(c(pre_var, post_var)))
  
  cat(paste0("#### ", pre_var, " ", post_var, "\n", "\n"))
  print(stat_comp)
  print(plot)
}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```


# Analyses

## Pre-Post differences on Oxytocin and Cortisol

```{r t_oxy_cort, fig.width=10, fig.height=11, results='asis'}
func_t_box(Data, "ID", "Conditie", "Cortizol_pre", "Cortizol_post")  
func_t_box(Data, "ID", "Conditie", "Oxitocina_pre", "Oxitocina_post") 
```


## Correlations between Difference Scores

```{r cor_diff, fig.width=10, fig.height=12}
## Automatic Post-Pre Difference Scores
var_prepost <- colnames(Data_merged[, grepl(".*pre|.*post", colnames(Data_merged))])    # find variables that have "pre" and "post"
var_prepost <-  gsub("_pre", "", var_prepost)                                           # delete pre and post from colname
var_prepost <-  gsub("_post", "", var_prepost)
var_prepost <- unique(var_prepost)                                                      # keep unique -- all good         
new_diffvar_name <- vector(mode="character", length = length(var_prepost))              # initialize vector for for()

for(i in seq_along(var_prepost)){
    var_name_pre <- paste0(var_prepost[i], "_pre")
    var_name_post <- paste0(var_prepost[i], "_post")
    new_diffvar_name[i] <- paste0(var_prepost[i], "_Diff")
    Data_merged[, new_diffvar_name[i]] <- Data_merged[, var_name_post] - Data_merged[, var_name_pre]
}

# Select variables
vars_cor <- new_diffvar_name[!new_diffvar_name %in% c("AllButtons_Diff", "AllButtons45_Diff", 
                                                      "Ones_Diff", "Ones45_Diff",
                                                      "Threes_Diff", "Threes45_Diff", 
                                                      "Twos_Diff", "Twos45_Diff")]       # exclude these
vars_cor <- c(vars_cor,
              c("Vas_rel_global", "Vas_rel_arousal", "CRQ_1", "CRQ_2", "CRQ_3", "CRQ_4", "CRQ_5", "CRQ_6"))

## Correlations
Get_Top_Relationships(Data_merged[, vars_cor])
Get_Top_Relationships(Data_merged[, vars_cor]) %>% func_dotplot_cor()
```


<br>

# Conditioning on VAS global

## Pre-Post differences on Oxytocin and Cortisol

```{r cond_t_oxy_cort, fig.width=10, fig.height=11, results='asis'}
Data_merged %>%
  filter(Vas_rel_global >= 7) %>%
  func_t_box(., "ID", "Conditie", "Cortizol_pre", "Cortizol_post") 

Data_merged %>%
  filter(Vas_rel_global >= 7) %>%
  func_t_box(., "ID", "Conditie", "Oxitocina_pre", "Oxitocina_post") 
```


<br>

# Moderation Analysis

```{r mod_oxy_cort, fig.width=7, fig.height=6, results='asis', warning=FALSE, message=FALSE}
## Define Function
func_moderation <- function(Data, dep, mod, pred){
  moderation <- 
    Data %>%
      medmod::mod(., dep = dep, mod = mod, pred = pred,
                  ci = TRUE, estMethod = 'standard', test = TRUE, simpleSlopeEst = FALSE, simpleSlopePlot = TRUE)
  
  cat(paste("<b> Moderation: ", "Dep = ", dep, "Pred = ", pred, "Mod = ", mod, "</b>"))
  moderation$mod %>% 
    knitr::kable(caption = "Moderation", digits = 3) %>%
    print()
  moderation$simpleSlope$plot %>%
    print()
}

## Apply Function
func_moderation(Data = Data_merged, dep = "Oxitocina_post", mod = "Vas_rel_arousal", pred = "Oxitocina_pre")
func_moderation(Data = Data_merged, dep = "Cortizol_post", mod = "Vas_rel_arousal", pred = "Cortizol_pre")

# bla <-
#   Data_merged %>%
#   mutate(Conditie = as.numeric(as.factor(Conditie)))
# 
# psych::mediate(data = bla, Oxitocina_post ~ Oxitocina_pre + Conditie + Vas_rel_global)   # moderation with covariate and diagram
```


# Mediation Analysis

```{r med_oxy_cort, fig.width=7, fig.height=6, results='asis', warning=FALSE, message=FALSE,   include=FALSE}
## Define Function
func_mediation <- function(Data, dep, med, pred){
  mediation <- 
    Data %>%
      medmod::med(., dep = dep, med = med, pred = pred,
                  ci = TRUE, label = TRUE, paths = TRUE, pm = TRUE, estPlot = TRUE)
  
  cat(paste("<b> Mediation: ", "Dep = ", dep, "Pred = ", pred, "Med = ", med, "</b>"))
  mediation$med %>% 
    knitr::kable(caption = "Moderation", digits = 3) %>%
    print()
  mediation$estPlot %>%
    print()
}

## Apply Function
func_mediation(Data = Data_merged, dep = "Oxitocina_post", med = "CRQ_4", pred = "Oxitocina_pre")
func_mediation(Data = Data_merged, dep = "Cortizol_post", med = "CRQ_4", pred = "Cortizol_pre")
```



<br>
<br>

<!-- Session Info and License -->

<br>

# Session Info
```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->
&nbsp;
<hr />
<p style="text-align: center;">A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a></p>
<p style="text-align: center;"><span style="color: #808080;"><em>claudiu.papasteri@gmail.com</em></span></p>
&nbsp;
