---
title: "<br> Go Study" 
subtitle: "Initial Analysis"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    # pdf_document: 
            # toc: true
            # toc_depth: 2
            # number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---


<!-- Setup -->


```{r setup, include=FALSE}
# General R options
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation
options(repos = c(getOption("repos")["CRAN"], CRANextra = "https://mirror.clientvps.com/CRAN/"))  # use CRAN as default, set CRANextra to Nürnberg mirror


if (!require("pacman")) install.packages("pacman", dependencies = TRUE)
packages <- c(
  "papaja",
  "here", "fs",
  "conflicted",
  "rio",
  "tidyverse", 
  "psych",          
  "rstatix", 
  "ggplot2", "ggpubr", "scales",
  "ggstatsplot", "report", 
  "ggstats", 
  "lmer4", "lmerTest", "merTools", "statAPA", "sjPlot"
  # , ...
)
pacman::p_load(char = packages)

# Set here to Rnotebook directory
here::set_here()
unloadNamespace("here")                   # need new R session or unload namespace for .here file to take precedence over .Rproj
notebook_name <- fs::path_file(here::here())

# Solve conflicts in favor of tidyverse
conflicted::conflict_prefer("filter", winner = "dplyr")
conflicted::conflict_prefer("select", winner = "dplyr")
conflicted::conflict_prefer("slice", winner = "dplyr")
conflicted::conflict_prefer("rename", winner = "dplyr")
conflicted::conflict_prefer("count", winner = "dplyr")

# Set kintr options including root.dir pointing to the .here file in Rnotebook directory
knitr::opts_chunk$set(
  root.dir = here::here(),
  #fig.width = 5, fig.asp = 1/3, 
  comment = "#",
  collapse = TRUE,
  echo = TRUE, warning = TRUE, message = TRUE, cache = TRUE       # echo = False for github_document, but will be folded in html_notebook
)

# Themes for ggplot2 plotting (here used APA style)
theme_set(papaja::theme_apa())
```




<!-- Functions -->

# Define functions

```{r}
# Main function to plot repeated measures for blocks 1-3 and 4-6
my_ggwithinstats <- function(df, var_name, problems = 1:3, id_column = "id", indiv_lines = TRUE) {
  
  # Create pattern for specified problems
  cols <- paste0(var_name, "_", problems)
  
  # Reshape to long format
  df_long <- df %>%
    select(all_of(c(id_column, cols))) %>%
    pivot_longer(
      cols = all_of(cols),
      names_to = "problem",
      values_to = "value"
    ) %>%
    mutate(problem = factor(problem, levels = cols))
  
  # Create the plot
  p <- 
    ggwithinstats(
      data = df_long,
      x = problem,
      y = value,
      subject.id = !!rlang::sym(id_column),
      title = paste0(var_name, " (Problems ", paste(range(problems), collapse = "-"), ")") 
    ) +
    ylim(1, 7)
  
  if(indiv_lines) {
    p <- p +
      geom_line(
          data = df_long,
          aes(x = problem, y = value, group = !!rlang::sym(id_column)),
          alpha = 0.3, 
          linetype = "dashed",
          linewidth = 0.5,
          color = "gray40"
        )
  }
  
  p
}


# Function
# Loop through each variable and create/print/store the plot
# my_ggwithinstats(df, "certain_continuation", problems = 1:3)

# Loop through each variable and create/print/store the plot
create_ggwithinstats_plots <- function(df = df, var_names, problems) {
  for(var in var_names) {
    problems_suffix <- paste(problems, collapse = "")
    plot_name <- paste0("withinplot_", var, "_", problems_suffix)
    assign(plot_name, my_ggwithinstats(df, var, problems = problems))
    print(get(plot_name))
  }
}
```

```{r}
# Function to plot individual lines (one line per id)
plot_trajectory <- function(df, var_name, problems = 1:3,
                                   id_column = "id",
                                   color_var = "MTI_cat",
                                   linetype_var = "rank_cat") {
  
  cols <- paste0(var_name, "_", problems)
  
  df_long <- df %>%
    select(all_of(c(id_column, color_var, linetype_var, cols))) %>%
    pivot_longer(cols = all_of(cols),
                 names_to = "problem",
                 values_to = "value") %>%
    mutate(problem = factor(problem, levels = cols))
  
  ggplot(df_long, aes(x = problem, y = value, 
                      group = !!sym(id_column),
                      color = !!sym(color_var),
                      linetype = !!sym(linetype_var))) +
    geom_line(size = 1, alpha = 0.8) +
    geom_point(size = 2, alpha = 0.8) +
    scale_color_manual(values = c("medium" = "orange", "high" = "darkred")) +  # pick your colors
    scale_linetype_manual(values = c("1Dan-2Dan" = "dashed", "3Dan-5Dan" = "solid")) +
    labs(title = paste0(var_name, " (Problems ", paste(range(problems), collapse = "-"), ")"),
         x = "Problem", y = "Score") +
    ylim(1, 7) +
    theme_minimal() +
    theme(legend.position = "bottom")
}

# Function
# Loop through each variable and create/print/store the plot
# create_trajectory_plots(df_story, var_names = EG_colnames, problems = 1:3)
create_trajectory_plots <- function(df, var_names, problems) {
  for (var in var_names) {
    problems_suffix <- paste(problems, collapse = "")
    plot_name <- paste0("traj_", var, "_", problems_suffix)
    p <- plot_trajectory(df, var, problems = problems)
    assign(plot_name, p, envir = .GlobalEnv)
    print(p)
  }
}
```


```{r}
# Quick ggbetweenstats function
# For publication
library(ggprism)

my_ggbetweenstats <- function(data, title, x, y, outlier.label, xlab, ylab, 
                              outlier.tagging = FALSE, results.subtitle = FALSE, 
                              centrality.label.args = FALSE, point.path = TRUE,
                              ...) {  # ... for limits and breaks
  x <- rlang::enquo(x)
  y <- rlang::enquo(y)
  outlier.label <- rlang::enquo(outlier.label)
  
  if(centrality.label.args){
    centrality.label.args <- list(size = 3, nudge_x = 0.2, segment.linetype = 5, fill = "#FFF8E7")
  }else{
    centrality.label.args <- list(size = 0, nudge_x = 0.2, segment.linetype = 0, alpha = 0) # very hacky way of not showing label
  }
  
  plot <- 
    data %>%
      ggstatsplot::ggbetweenstats(
        x = !!x,
        y = !!y,
        title = title,
        xlab = xlab,
        ylab = ylab,
        outlier.tagging = outlier.tagging,                    # whether outlines need to be tagged
        outlier.label = !!outlier.label,                      # variable to be used for tagging outliers
        outlier.coef = 2,
        pairwise.comparisons = TRUE,
        pairwise.display = "significant",
        results.subtitle = results.subtitle,
        type = "np",
        bf.message = FALSE, 
        p.adjust.method = "holm",
        point.path = point.path,
        ggtheme = ggprism::theme_prism(palette = "black_and_white"),
        # package = "RColorBrewer",  # "ggsci",
        # palette = "Dark",         # "default_jco",
        violin.args = list(width = 0.9, alpha = 0.2, size = 1, color = "black"),
        centrality.plotting = TRUE,
        centrality.type = "np",
        centrality.point.args = list(size = 5, color = "black"),
        centrality.path.args = list(color = "black", size = 1, alpha = 1),
        ggsignif.args = list(textsize = 3, tip_length = 0.01, na.rm = TRUE,
                             test.args = list(exact = FALSE)),
        centrality.label.args = centrality.label.args,
        ggplot.component = list(
          theme(
            plot.title = element_text(hjust = 0, size = 16),
            plot.subtitle = element_text(hjust = 0, size = 12), 
            plot.caption = element_text(hjust = 0, size = 12), 
            text = element_text(family = "Sans", size = 14)
        ))
      ) + scale_colour_grey(start = 0.2, end = 0.2) +  # hacky way to change point color
      scale_y_continuous(...)
  
  plot
}

# Fast ggsave - saves plot with filename of R plot object
fast_ggsave <- function(plot, device = "tiff", path = NULL,
                        units = "in", dpi = 300, width = 5, height = 5, ...){ 
  plot_name <- deparse(substitute(plot))
  ggplot2::ggsave(filename = paste0(plot_name, ".", device), plot = plot,
                  device = device, path = path,
                  units = units, dpi = dpi,
                  width = width, height = height,
                  ...
  )
  
} # use: fast_ggsave(jrad_ox_p, path = savefolder)

# Fast tiff save
fast_tiffsave <- function(plot, path = NULL,
                          units = "in", res = 300, width = 5, height = 5, ...){ 
  plot_name <- deparse(substitute(plot))
  tiff(filename = file.path(path, paste0(plot_name, ".", "tiff")),
       units = units, res = res,
       width = width, height = height,
       ...
  )
  plot(plot)
  dev.off()
}  # use: fast_tiffsave(jrad_ox_p, path = savefolder)

# Errors with ggplot2  --- can use this to save:
# Cairo::Cairo(
#   width = 5, 
#   height = 5, 
#   file = file.path(savefolder, paste0("jrad_ox_p", ".", "tiff")),
#   type = "png", 
#   bg =  "white",    # "transparent" 
#   dpi = 300,
#   units = "in"
# )
# plot(jrad_ox_p) 
# dev.off()
```


<!-- Report -->

# Data
## Read data

```{r}
last_csv_file <-
  dir(here::here(), pattern = "Go Study Form_Submissions.*csv", full.names = TRUE) %>%
  file.info() %>%
  dplyr::arrange(dplyr::desc(ctime)) %>%
  dplyr::slice(1) %>%
  row.names()

df <- rio::import(file = last_csv_file)
```

## Questionnare info

```{r}
# MTI ------------------------------------------------------------------------------------
MTI_items_index <- c(10:17) # colnames(df[, MTI_items_index])
MTI_items_text <- 
  c(
  "1. I believe in my ability to achieve my goals",
  "2. I am able to regulate my focus when performing tasks",
  "3. I am able to use my emotions to perform the way I want to",
  "4. I strive for continued success",
  "5. I execute my knowledge of what is required to achieve my goals",
  "6. I consistently overcome adversity",
  "7. I am able to execute appropriate skills or knowledge when challenged",
  "8. I can find a positive in most situations"
  )

colnames(df[, 18, drop=FALSE]) == "What is your rank?"

# EG ------------------------------------------------------------------------------------
# Create EG_1_index through EG_6_index in a loop
for (i in 1:6) {      # EG_1_index <- c(19:26) # colnames(df[, EG_1_index])
  # Create the index variable
  assign(paste0("EG_", i, "_index"), c(19:26) + (i - 1) * 8)
  
  # Retrieve the index vector for this iteration
  idx <- get(paste0("EG_", i, "_index"))
  
  # Print the corresponding column names
  cat("\n--- EG_", i, " ---\n", sep = "")
  print(colnames(df[, idx]))    # rm(list = ls(pattern = "EG_[0-9]_index"))
}
  
EG_text <- 
  c(
  "1. How certain are you that this is the correct continuation?",       
  "2. How confident are you that you are winning this game?",
  "3. How unpredictable does the outcome of the game feel?",
  "4. How unstable or chaotic does this position feel?",
  "5. How in control do you feel in this game?",
  "6. How mentally overwhelming does this position feel?",
  "7. How mentally off-balance does this position make you feel?",
  "8. How frustrating does the current state of the game feel?"
  )

EG_colnames <-
  c(
  "certain_continuation",       
  "confident_winning",
  "unpredictable_outcome",
  "chaotic",
  "in_control",
  "overwhelming",
  "off-balance",
  "frustrating"
  )

# EG_likert_levels <- 
#   
# 1	Not at all
# 2	Very slightly
# 3	Slightly
# 4	Moderately
# 5	Quite a bit
# 6	Very much
# 7	Extremely  


# Change column names in loop
for (i in 1:6) {
  # Get the column indices for block i
  idx <- get(paste0("EG_", i, "_index"))
  # Create new names by appending _i to each base name
  new_names <- paste0(EG_colnames, "_", i)
  # Rename columns
  colnames(df)[idx] <- new_names
}
```

## Data munging

```{r}
# Rename EG cols
for (i in 1:6) {   # names(df[,EG_5_index])
  # Get current column names for this block
  idx <- get(paste0("EG_", i, "_index"))
  old_names <- colnames(df)[idx]
  
  # Create new names
  new_names <- paste0(EG_colnames, "_", i)
  # Create a named vector for renaming
  rename_vector <- setNames(new_names, old_names)
  # Apply rename
  df <- df %>% rename(all_of(rename_vector))
}
  
# Rename MTI cols
df <- df %>% rename_with(
  ~ paste0("mti_", seq_along(MTI_items_index)),
  .cols = all_of(MTI_items_index)
)

# Rename & convert rank
df <- 
  df %>% 
  rename_with(~ "rank", .cols = 18) %>% 
  mutate(rank = as.factor(rank))

# Score MTI
df <- df %>%
  mutate(MTI_total = rowSums(across(all_of(MTI_items_index)), na.rm = TRUE)) %>% 
  rowwise() %>%
  mutate(MTI_total_check = sum(c_across(matches("^mti_\\d+$")), na.rm = TRUE)) %>%
  ungroup()  
if(all(df$MTI_total == df$MTI_total_check, na.rm = TRUE)) {
  df <- df %>% select(-MTI_total_check)
  message("MTI_total_check verified and removed")
} else {
  message("Mismatch found: MTI_total_check retained for inspection")
}  

# Rename and check id
colnames(df)[2] <- "id"
length(unique(df$id)) == nrow(df)

# Create composite scores for variables based on problems
for(var in EG_colnames) {
  # Create composite_14 = mean of _1 and _4
  df[[paste0(var, "_14")]] <- rowMeans(df[, c(paste0(var, "_1"), paste0(var, "_4"))], na.rm = TRUE)
  
  # Create composite_25 = mean of _2 and _5
  df[[paste0(var, "_25")]] <- rowMeans(df[, c(paste0(var, "_2"), paste0(var, "_5"))], na.rm = TRUE)
  
  # Create composite_36 = mean of _3 and _6
  df[[paste0(var, "_36")]] <- rowMeans(df[, c(paste0(var, "_3"), paste0(var, "_6"))], na.rm = TRUE)
}

# Drop first row (my test)
df <- df[-1, ]
```
# Results


## Descriptives

### Rank

```{r}
# df %>% 
#   mutate(rank = factor(rank, ordered = TRUE, 
#         levels = c("DDK", "9kyu-5kyu", "4kyu-1kyu", "1Dan-2Dan", "3Dan-5Dan", "5Dan+"))
#   ) %>% 
#   ggplot(aes(x = rank)) +
#   geom_bar(aes(y = after_stat(prop), group = 1), fill = "steelblue", color = "black") +
#   scale_y_continuous(labels = scales::percent) +
#   labs(title = "Proportion of Player Ranks", x = "Rank", y = "Percent")   

df %>% 
  mutate(rank = factor(rank, ordered = TRUE, 
        levels = c("DDK", "9kyu-5kyu", "4kyu-1kyu", "1Dan-2Dan", "3Dan-5Dan", "5Dan+"))
  ) %>% 
  count(rank) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(x = rank, y = prop, fill = rank)) +
  geom_col(color = "black") +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Proportion of Player Ranks", x = "Rank", y = "Percent") +
  scale_fill_brewer(palette = "GnBu", direction = 1) +
  guides(fill = "none")
```


### MTI

```{r}
# df %>%
#   ggplot(aes(x = MTI_total, fill = after_stat(x))) +
#   geom_histogram(binwidth = 4, color = "black", alpha = 0.8) +
#   scale_fill_distiller(palette = "GnBu", direction = 1, name = "Score") +
#   scale_x_continuous(breaks = seq(0, 100, by = 5)) +
#   labs(title = "Distribution of MTI Total Scores",
#        x = "Total Score", y = "Count")

df %>%
  ggplot(aes(x = MTI_total, y = after_stat(count / sum(count)), fill = after_stat(x))) +
  geom_histogram(binwidth = 4, color = "black", alpha = 0.8) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_distiller(palette = "GnBu", direction = 1, name = "Score") +
  scale_x_continuous(breaks = seq(0, 100, by = 5)) +
  labs(title = "Distribution of MTI Total Scores",
       x = "Total Score", y = "Percent")
```

```{r}
df %>% 
  select(matches("^mti_\\d+$")) %>% 
  mutate(across(everything(), ~ factor(.x, levels = 1:7))) %>% 
  gglikert(variable_labels = setNames(MTI_items_text, paste0("mti_", seq_along(MTI_items_text))), symmetric = TRUE) +
    guides(fill = guide_legend(nrow = 1)) 

```



## Preliminary results

### 1-3

```{r}
create_ggwithinstats_plots(df, var_names = EG_colnames, problems = 1:3)
```

### Selection

```{r}
plot_uo13 <- my_ggwithinstats(df, "unpredictable_outcome", problems = 1:3)
plot_uo46 <- my_ggwithinstats(df, "unpredictable_outcome", problems = 4:6)
# fast_tiffsave(plot_uo13, here::here(), width = 5, height = 5)
# fast_tiffsave(plot_uo46, here::here(), width = 5, height = 5)

plot_cw13 <- my_ggwithinstats(df, "confident_winning", problems = 1:3)
plot_cw46 <- my_ggwithinstats(df, "confident_winning", problems = 4:6)
# fast_tiffsave(plot_cw13, here::here(), width = 5, height = 5)
# fast_tiffsave(plot_cw46, here::here(), width = 5, height = 5)
```


### StrongRank 1-3

```{r}
df %>%
  filter(!rank %in% c("9kyu-5kyu", "DDK")) %>%
  create_ggwithinstats_plots(., var_names = EG_colnames, problems = 1:3)
```


### 4-6

```{r}
create_ggwithinstats_plots(df, var_names = EG_colnames, problems = 4:6)
```

### StrongRank 4-6

```{r}
df %>%
  filter(!rank %in% c("9kyu-5kyu", "DDK")) %>%
  create_ggwithinstats_plots(., var_names = EG_colnames, problems = 4:6)
```



### Composites 14, 25, 36

```{r}
create_ggwithinstats_plots(df, var_names = EG_colnames, problems = c(14, 25, 36))
```


### StrongRank Composites 14, 25, 36

```{r}
df %>%
  filter(!rank %in% c("9kyu-5kyu", "DDK")) %>%
  create_ggwithinstats_plots(., var_names = EG_colnames, problems = c(14, 25, 36))
```


```{r}
df %>% 
  select(MTI_total, ends_with(c("_14", "_25", "_36"))) %>%
  ggcorrmat(
    data     = .,
    title    = "Correlalogram",
    subtitle = "..."
  )
```



## HLM

<!--

```{r}
df_comp <- df %>%
  select(id, rank, ends_with(c("_14", "_25", "_36"))) %>%
  pivot_longer(
    cols = -c(id, rank),
    names_to = c("variable", "time"),
    names_pattern = "(.*)_(\\d+)",
    values_to = "value"
  ) %>%
  mutate(
    time = case_when(
      time == "14" ~ 1,
      time == "25" ~ 2,
      time == "36" ~ 3
    )
  ) %>%
  pivot_wider(
    names_from = variable,
    values_from = value
  )


lmm_mod_1 <-  
  lme4::lmer(
    data = df_comp,
    formula = 
      `off-balance` ~  1 + 
      # certain_continuation +
      # confident_winning +
      unpredictable_outcome +
      chaotic +
      # in_control +
      overwhelming +  
      frustrating +
      (1 + time | id), 
    REML = FALSE,
    control = lme4::lmerControl(
      optimizer = "optimx", optCtrl=list(method = "nlminb") # solve failed convergence
    )
  ) 

lmm_mod_1 %>%
  lmerTest::as_lmerModLmerTest() %>%
  lmerTest:::summary.lmerModLmerTest() 
```


```{r}
df_comp_r <-
  df_comp %>% 
  filter(!rank %in% c("9kyu-5kyu", "DDK"))

lmm_mod_2 <-  
  lme4::lmer(
    data = df_comp_r,
    formula = 
      `off-balance` ~  1 + 
      certain_continuation +
      confident_winning +
      unpredictable_outcome +
      chaotic +
      # in_control +
      overwhelming +  
      frustrating +
      (1 + time | id), 
    REML = FALSE,
    control = lme4::lmerControl(
      optimizer = "optimx", optCtrl=list(method = "nlminb") # solve failed convergence
    )
  ) 

lmm_mod_2 %>%
  lmerTest::as_lmerModLmerTest() %>%
  lmerTest:::summary.lmerModLmerTest() 

```

-->


### Data

```{r}
df_lmm <- df %>%
  select(id, rank, MTI_total, all_of(paste0(rep(EG_colnames, times = 6), "_", rep(1:6, each = length(EG_colnames))))) %>%
  # filter(!rank %in% c("9kyu-5kyu", "DDK")) %>%
  pivot_longer(
    cols = -c(id, rank, MTI_total),
    names_to = c("variable", "time"),
    names_pattern = "(.*)_(\\d+)",
    values_to = "value"
  ) %>% 
  mutate(problem = case_when(time %in% c(1, 2, 3) ~ "C6", time %in% c(4, 5, 6) ~ "C8", .unmatched = "error")) %>% 
  mutate(blunder = if_else(time %in% c(3, 6), 1, 0)) %>% 
  mutate(time_old = as.numeric(time)) %>% 
  mutate(time = if_else(time_old < 4, time_old, time_old - 3)) %>% 
  pivot_wider(
    names_from = variable,
    values_from = value
  ) %>% 
  mutate(tilt = `off-balance` + frustrating) %>% 
  mutate(time = factor(time)) # 1→2 isn't necessarily equal to 2→3; need time as factor orig → modif → blunder
```  
    
### Model

```{r}
# off-balance -> yes

df_lmm_ob <- df_lmm %>% mutate(off_balance = `off-balance`)

lmm_mod_f1 <-  
  lme4::lmer(
    data = df_lmm_ob,
    formula = 
      off_balance ~ problem + time + (1 | id), 
    REML = FALSE,
    control = lme4::lmerControl(
      optimizer = "optimx", optCtrl=list(method = "nlminb") # solve failed convergence
    )
  ) 

lmm_mod_f1 %>%
  lmerTest::as_lmerModLmerTest() %>%
  lmerTest:::summary.lmerModLmerTest() 


lmm_mod_f_t <-  
  lme4::lmer(
    data = df_lmm_ob,
    formula = 
      tilt ~ problem + time + (1 | id), 
    REML = FALSE,
    control = lme4::lmerControl(
      optimizer = "optimx", optCtrl=list(method = "nlminb") # solve failed convergence
    )
  ) 

lmm_mod_f_f <-  
  lme4::lmer(
    data = df_lmm_ob,
    formula = 
      frustrating ~ problem + time + (1 | id), 
    REML = FALSE,
    control = lme4::lmerControl(
      optimizer = "optimx", optCtrl=list(method = "nlminb") # solve failed convergence
    )
  )


lmm_mod_f1mod <-  
  lme4::lmer(
    data = df_lmm_ob,
    formula = 
      off_balance ~ problem + time + MTI_total + (1 | id), 
    REML = FALSE,
    control = lme4::lmerControl(
      optimizer = "optimx", optCtrl=list(method = "nlminb") # solve failed convergence
    )
  ) 

lmm_mod_f1mod %>%
  lmerTest::as_lmerModLmerTest() %>%
  lmerTest:::summary.lmerModLmerTest() 
```

```{r}
report::report(lmm_mod_f1)

sjPlot::tab_model(lmm_mod_f1)
sjPlot::tab_model(lmm_mod_f_t)
sjPlot::tab_model(lmm_mod_f_f)
# sjPlot::tab_model(lmm_mod_f1mod)
# statAPA::apa_multilevel(lmm_mod_f1, lmm_mod_f1mod)

```



```{r}
# frustrating -> no

# lmm_mod_f2 <-
#   lme4::lmer(
#     data = df_lmm,
#     formula =
#       frustrating ~ problem + time + MTI_total + (1 | id),
#     REML = FALSE,
#     control = lme4::lmerControl(
#       optimizer = "optimx", optCtrl=list(method = "nlminb") # solve failed convergence
#     )
#   )
# 
# lmm_mod_f2 %>%
#   lmerTest::as_lmerModLmerTest() %>%
#   lmerTest:::summary.lmerModLmerTest()
```


```{r}
sjPlot::tab_model(lmm_mod_f1)
# sjPlot::tab_model(lmm_mod_f1mod)
# statAPA::apa_multilevel(lmm_mod_f1, lmm_mod_f1mod)

```


```{r}
# in_control

lmm_mod_f3 <-  
  lme4::lmer(
    data = df_lmm,
    formula = 
      in_control ~ problem + time + (1 | id), 
    REML = FALSE,
    control = lme4::lmerControl(
      optimizer = "optimx", optCtrl=list(method = "nlminb") # solve failed convergence
    )
  ) 

lmm_mod_f3 %>%
  lmerTest::as_lmerModLmerTest() %>%
  lmerTest:::summary.lmerModLmerTest() 
```

```{r}
# unpredictable_outcome

lmm_mod_f4 <-  
  lme4::lmer(
    data = df_lmm,
    formula = 
      unpredictable_outcome ~ problem + time + (1 | id), 
    REML = FALSE,
    control = lme4::lmerControl(
      optimizer = "optimx", optCtrl=list(method = "nlminb") # solve failed convergence
    )
  ) 

lmm_mod_f4 %>%
  lmerTest::as_lmerModLmerTest() %>%
  lmerTest:::summary.lmerModLmerTest() 
```

```{r}
# confident_winning

lmm_mod_f5 <-  
  lme4::lmer(
    data = df_lmm,
    formula = 
      confident_winning ~ problem + time + (1 | id), 
    REML = FALSE,
    control = lme4::lmerControl(
      optimizer = "optimx", optCtrl=list(method = "nlminb") # solve failed convergence
    )
  ) 

lmm_mod_f5 %>%
  lmerTest::as_lmerModLmerTest() %>%
  lmerTest:::summary.lmerModLmerTest() 
```

```{r}
# overwhelming

lmm_mod_f6 <-  
  lme4::lmer(
    data = df_lmm,
    formula = 
      overwhelming ~ problem + time + (1 | id), 
    REML = FALSE,
    control = lme4::lmerControl(
      optimizer = "optimx", optCtrl=list(method = "nlminb") # solve failed convergence
    )
  ) 

lmm_mod_f6 %>%
  lmerTest::as_lmerModLmerTest() %>%
  lmerTest:::summary.lmerModLmerTest() 
```

```{r}

for(mod in paste0("lmm_mod_f", 3:6)) {
  mod_obj <- get(mod)
  lmerTest::as_lmerModLmerTest(mod_obj) %>%
  lmerTest:::summary.lmerModLmerTest() %>% 
  print()
}  
  

# sjPlot::tab_model(lmm_mod_f3)
# sjPlot::tab_model(lmm_mod_f4)
# sjPlot::tab_model(lmm_mod_f5)
# sjPlot::tab_model(lmm_mod_f6)

sjPlot::tab_model(lmm_mod_f3, lmm_mod_f4, lmm_mod_f5, lmm_mod_f6)
```

```{r}
m1 <- lme4::lmer(unpredictable_outcome ~ time + (1|id), data=df_lmm)
m2 <- lme4::lmer(`off-balance` ~ time + (1|id), data=df_lmm)
m3 <- lme4::lmer(`off-balance` ~ time + unpredictable_outcome + (1|id), data=df_lmm)

m1 %>%
  lmerTest::as_lmerModLmerTest() %>%
  lmerTest:::summary.lmerModLmerTest() 
m2 %>%
  lmerTest::as_lmerModLmerTest() %>%
  lmerTest:::summary.lmerModLmerTest() 
m3 %>%
  lmerTest::as_lmerModLmerTest() %>%
  lmerTest:::summary.lmerModLmerTest() 
```


## Mediation

```{r}
library(mediation)

df_lmm$time_num <- as.numeric(df_lmm$time)

m1 <- lme4::lmer(unpredictable_outcome ~ time_num + (1|id), data=df_lmm)
m2 <- lme4::lmer(`off-balance` ~ time_num + unpredictable_outcome + (1|id), data=df_lmm)

med <- mediation::mediate(
  m1, m2,
  treat = "time_num",
  mediator = "unpredictable_outcome",
  boot = FALSE,
  sims = 2000
)

summary(med)
plot(med)
```




## Full Model

```{r}
lmm_mod_full_1 <-
  lme4::lmer(
    data = df_lmm,
    formula =
      tilt ~
        # problem +
        # time +
        certain_continuation +
        confident_winning +
        in_control +
        unpredictable_outcome +
        overwhelming +
        MTI_total +
        (1|id),
    REML = FALSE,
    control = lme4::lmerControl(
      optimizer = "optimx", optCtrl=list(method = "nlminb") # solve failed convergence
    )
  )

parameters::select_parameters(lmm_mod_full_1, direction = "backward")
cAIC4::stepcAIC(lmm_mod_full_1, direction = "backward", data = df_lmm)


lmm_mod_full_1 %>%
  lmerTest::as_lmerModLmerTest() %>%
  lmerTest:::summary.lmerModLmerTest()


lmm_mod_full_2 <-
  lme4::lmer(
    data = df_lmm,
    formula =
      `off-balance` ~
        confident_winning +
        in_control +
        unpredictable_outcome +
        overwhelming +
        MTI_total +
        (1|id),
    REML = FALSE,
    control = lme4::lmerControl(
      optimizer = "optimx", optCtrl=list(method = "nlminb") # solve failed convergence
    )
  )

lmm_mod_full_2 %>%
  lmerTest::as_lmerModLmerTest() %>%
  lmerTest:::summary.lmerModLmerTest()

lmm_mod_full_3 <-
  lme4::lmer(
    data = df_lmm,
    formula =
      frustrating ~
        confident_winning +
        in_control +
        unpredictable_outcome +
        overwhelming +
        MTI_total +
        (1|id),
    REML = FALSE,
    control = lme4::lmerControl(
      optimizer = "optimx", optCtrl=list(method = "nlminb") # solve failed convergence
    )
  )

lmm_mod_full_3 %>%
  lmerTest::as_lmerModLmerTest() %>%
  lmerTest:::summary.lmerModLmerTest()
```

```{r}
report::report(lmm_mod_full_1)

# statAPA::apa_multilevel(lmm_mod_full_1, output = "latex")
# setwd(here::here()); statAPA::apa_multilevel(lmm_mod_full_2, output = "word", file = "2.docx")

sjPlot::tab_model(lmm_mod_full_1)
sjPlot::tab_model(lmm_mod_full_2)
sjPlot::tab_model(lmm_mod_full_3)
```








# Wacky data stories

```{r}
df_story <- df %>% 
  filter(rank %in% c("1Dan-2Dan", "3Dan-5Dan"))  
  
df_story %>%   
  select(id, rank, MTI_total) %>% 
  arrange(MTI_total)   # mean 33 vs mean 43

df_story <- 
  df_story %>% 
  mutate(rank_cat = droplevels(rank)) %>% 
  mutate(MTI_cat = case_when(MTI_total <= 40 ~ "medium", MTI_total > 40 ~ "high", .unmatched = "error")) %>% 
  mutate(MTI_cat = factor(MTI_cat, ordered = TRUE, levels = c("medium", "high")))

table(df_story$rank_cat, df_story$MTI_cat)

```

### 1-3

```{r}
# create_ggwithinstats_plots(df_story, var_names = EG_colnames, problems = 1:3)

create_trajectory_plots(df_story, var_names = EG_colnames, problems = 1:3)
```


### 4-6

```{r}
# create_ggwithinstats_plots(df_story, var_names = EG_colnames, problems = 4:6)

create_trajectory_plots(df_story, var_names = EG_colnames, problems = 4:6)
```

### Looking more closely at combined plots 

```{r}
for(var in EG_colnames) {
  p1 <- get(paste0("traj_", var, "_123"))   # adjust suffix as needed
  p2 <- get(paste0("traj_", var, "_456"))
  combined <- cowplot::plot_grid(p1, p2, ncol = 2)
  print(combined)
  # optionally assign
  assign(paste0("combined_", var), combined)
}
```



### Composites 14, 25, 36

```{r}
create_ggwithinstats_plots(df_story, var_names = EG_colnames, problems = c(14, 25, 36))
```

```{r}
create_trajectory_plots(df_story, var_names = EG_colnames, problems = c(14, 25, 36))
```



<!-- Session Info and License -->

<br>

# Session Info
```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->
&nbsp;
<hr />
<p style="text-align: center;">A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a></p>
<p style="text-align: center;"><span style="color: #808080;"><em>claudiu.papasteri@gmail.com</em></span></p>
&nbsp;
