---
title: "<br> Drama Exercises" 
subtitle: "Report for Theater Group and Psychology Group"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    # pdf_document: 
            # toc: true
            #  toc_depth: 2
            #  number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---


<!-- Setup -->


```{r setup, include=FALSE}
# kintr options
knitr::opts_chunk$set(
  comment = "#",
  collapse = TRUE,
  echo = TRUE, warning = FALSE, message = TRUE, cache = TRUE       # echo = False for github_document, but will be folded in html_notebook
)

# General R options and info
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation

# Load packages
if (!require("pacman")) install.packages("pacman")
packages <- c(
  "papaja",
  "tidyverse", "plyr",      
  "psych", "PerformanceAnalytics",          
  "broom", "rstatix",
  "summarytools", "tadaatoolbox",           
  "ggplot2", "ggpubr", "scales",        
  "rio"
  # , ...
)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(char = packages)

# Themes for ggplot2 ploting (here used APA style)
theme_set(theme_apa())
```





<!-- Report -->


# Read, Clean, Recode, Merge

```{r red_clean_recode_merge, results='hide'}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Read, Clean, Recode, Unite
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

## Read files
folder_teatru <- "E:/Cinetic idei noi/A13/Date grup teatru"
folder_psiho <- "E:/Cinetic idei noi/A13/Date grup psiho"
file_teatru <- "A13 Tabel date COMPLET28ian.xlsx"
file_psiho <- "A13P Tabel centralizat.xlsx"

setwd(folder_teatru)
Data_teatru <- rio::import(file.path(folder_teatru, file_teatru),
                           skip = 1)
setwd(folder_psiho)
Data_psiho <- rio::import(file.path(folder_psiho, file_psiho),
                           skip = 1)


## Tidy up data
# Function coalesce rows: colapse when NA, unite with "_" when not NA
coalesce2 <- function(...) {
  Reduce(function(x, y) {
    i <- which(is.na(x))
    j <- which(!is.na(x) & !is.na(y))
    x[i] <- y[i]
    x[j] <- paste(x[j], y[j], sep = "_")
    x},
    list(...))
}

colnames(Data_teatru) <- coalesce2(Data_teatru[2,], Data_teatru[3,])
Data_teatru <- Data_teatru[-c(1:3),]

colnames(Data_psiho) <- coalesce2(Data_psiho[2,], Data_psiho[3,])
Data_psiho <- Data_psiho[-c(1:3),]


## Check if both data sets have exact same column names
all.equal(colnames(Data_teatru), colnames(Data_psiho))           # not the same
diff_colname <- setdiff(colnames(Data_teatru), colnames(Data_psiho))
ind <- which(colnames(Data_teatru) ==  diff_colname)

colnames(Data_psiho)[ind] <- diff_colname                       # replace with same colname from Data_teatru
all.equal(colnames(Data_teatru), colnames(Data_psiho))           # now they are the same


## Solve duplicate names due to excel double header
# Function to paste a string before column name if it doesnt already start with that string
paste_tocolnames <- function(vec_colnames, string_paste){
  ind <- grep(pattern = string_paste, vec_colnames)                   # ignore column that already has string patterm
  vec_colnames[-ind] <- paste0(string_paste, vec_colnames[-ind])      # paste pattern to the rest of them
  return(vec_colnames)
}

colnames(Data_teatru)[6:21] <- paste_tocolnames(colnames(Data_teatru)[6:21], "APS pre_")
colnames(Data_teatru)[22:35] <- paste_tocolnames(colnames(Data_teatru)[22:35], "PPS pre_")
colnames(Data_teatru)[36:55] <- paste_tocolnames(colnames(Data_teatru)[36:55], "PANAS pre_")
colnames(Data_teatru)[76:79] <- paste_tocolnames(colnames(Data_teatru)[76:79], "SRS post_")
colnames(Data_teatru)[80:99] <- paste_tocolnames(colnames(Data_teatru)[80:99], "PANAS post_")
colnames(Data_teatru)[100:113] <- paste_tocolnames(colnames(Data_teatru)[100:113], "PPS post_")
colnames(Data_teatru)[114:129] <- paste_tocolnames(colnames(Data_teatru)[114:129], "APS post_")

colnames(Data_psiho)[6:21] <- paste_tocolnames(colnames(Data_psiho)[6:21], "APS pre_")
colnames(Data_psiho)[22:35] <- paste_tocolnames(colnames(Data_psiho)[22:35], "PPS pre_")
colnames(Data_psiho)[36:55] <- paste_tocolnames(colnames(Data_psiho)[36:55], "PANAS pre_")
colnames(Data_psiho)[76:79] <- paste_tocolnames(colnames(Data_psiho)[76:79], "SRS post_")
colnames(Data_psiho)[80:99] <- paste_tocolnames(colnames(Data_psiho)[80:99], "PANAS post_")
colnames(Data_psiho)[100:113] <- paste_tocolnames(colnames(Data_psiho)[100:113], "PPS post_")
colnames(Data_psiho)[114:129] <- paste_tocolnames(colnames(Data_psiho)[114:129], "APS post_")
# as.data.frame(colnames(Data_psiho))
# as.data.frame(colnames(Data_teatru))

colnames(Data_teatru) <- enc2native(colnames(Data_teatru))      # fix encoding
colnames(Data_psiho) <- enc2native(colnames(Data_psiho))


## Recode known missing values
# str(Data_psiho, list.len = ncol(Data_psiho))
# str(Data_psiho, list.len = ncol(Data_psiho))
Data_teatru <-
  Data_teatru %>%
  replace(. == "/", NA) %>%                                     # missing values are coded "/"
  replace(. == "-", NA) %>%                                     # missing values are coded "-"
  replace(. == "NA", NA)                                        # missing values are coded "NA"

Data_psiho <-
  Data_psiho %>%
  replace(.=="/", NA) %>%                                       # missing values are coded "/"
  replace(.=="-", NA) %>%                                       # missing values are coded "-"
  replace(. == "NA", NA)                                        # missing values are coded "NA"

  
## Check for non-numeric elements in data sets
check_numeric1 <- as.data.frame(sapply(Data_teatru, varhandle::check.numeric)) 
check_numeric2 <- as.data.frame(sapply(Data_psiho, varhandle::check.numeric))
# sapply(check_numeric1, function(x) length(which(!x)))     # look at columns with non-numeric and count of non-numeric values
# sapply(check_numeric2, function(x) length(which(!x)))

nonnumeric1 <- sapply(check_numeric1, function(x) which(!x, arr.ind = TRUE))    # find row numbers for non-numeric values
nonnumeric2 <- sapply(check_numeric2, function(x) which(!x, arr.ind = TRUE)) 
nonnumeric1[lapply(nonnumeric1, length) > 0]                                   # return only columns and rown numbers were non-numeric
nonnumeric2[lapply(nonnumeric2, length) > 0]

## Recode to numeric
Data_teatru[, -c(1:5)] <- sapply(Data_teatru[, -c(1:5)], as.numeric)    
Data_psiho[, -c(1:5)] <- sapply(Data_psiho[, -c(1:5)], as.numeric)     # cant do this because of encoding:  mutate_at(-c(1:5), ~as.numeric(.))
  
## Correct typos in IDs
#unique(Data_teatru$`Indicativ subiect`)
#unique(Data_psiho$`Indicativ subiect`)
Data_teatru$`Indicativ subiect`[Data_teatru$`Indicativ subiect` == "18.A.1:3"] <- "18.A.1.3"
Data_teatru$`Indicativ subiect`[Data_teatru$`Indicativ subiect` == "26.A.1.3."] <- "26.A.1.3"
Data_teatru$`Indicativ subiect`[Data_teatru$`Indicativ subiect` == "27.A.1.3."] <- "27.A.1.3"

Data_psiho$`Indicativ subiect` <- gsub(".P", "", Data_psiho$`Indicativ subiect`)               # delete .P from IDs
Data_psiho$`Indicativ subiect`[Data_psiho$`Indicativ subiect` == "16.A.A.1.3"] <- "16.A.1.3"
Data_psiho$`Indicativ subiect`[Data_psiho$`Indicativ subiect` == "1.A.1.3"] <- "01.A.1.3"
Data_psiho$`Indicativ subiect`[Data_psiho$`Indicativ subiect` == "2.A.1.3"] <- "02.A.1.3"
Data_psiho$`Indicativ subiect`[Data_psiho$`Indicativ subiect` == "4.A.1.3"] <- "04.A.1.3"
Data_psiho$`Indicativ subiect`[Data_psiho$`Indicativ subiect` == "0.4.A.1.3"] <- "04.A.1.3"
Data_psiho$`Indicativ subiect`[Data_psiho$`Indicativ subiect` == "5.A.1.3"] <- "05.A.1.3"
Data_psiho$`Indicativ subiect`[Data_psiho$`Indicativ subiect` == "6.A.1.3"] <- "06.A.1.3"
Data_psiho$`Indicativ subiect`[Data_psiho$`Indicativ subiect` == "7.A.1.3"] <- "07.A.1.3"
Data_psiho$`Indicativ subiect`[Data_psiho$`Indicativ subiect` == "8.A.1.3"] <- "08.A.1.3"
Data_psiho$`Indicativ subiect`[Data_psiho$`Indicativ subiect` == "9.A.1.3"] <- "09.A.1.3"
Data_psiho$`Indicativ subiect` <- paste0(Data_psiho$`Indicativ subiect`, ".P")                # add .P to all IDs

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Scoring Questionnaire and Unite
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## Define function that calculates RowSums but only for rows with less than 10% NAs; and return NA if all row values are NA 
SpecialRowSums <- function(df, napercent = .1) {
  ifelse(rowSums(is.na(df)) > ncol(df) * napercent,
         NA,
         rowSums(df, na.rm = TRUE) * NA ^ (rowSums(!is.na(df)) == 0)
  )
}

## APS: simple sum
Data_teatru$`APS pre_Total` <- SpecialRowSums(Data_teatru[ ,sprintf("APS pre_%d", 1:16)], napercent = .13)  # not more than 2 NAs for 16 items
Data_teatru$`APS post_Total` <- SpecialRowSums(Data_teatru[ ,sprintf("APS post_%d", 1:16)], napercent = .13)
Data_psiho$`APS pre_Total` <- SpecialRowSums(Data_psiho[ ,sprintf("APS pre_%d", 1:16)], napercent = .13)
Data_psiho$`APS post_Total` <- SpecialRowSums(Data_psiho[ ,sprintf("APS post_%d", 1:16)], napercent = .13)

## PSS-SF 14: Items 4, 5, 6, 7, 9, 10, and 13 are scored in reverse direction.
keys_PSS <- c(1,1,1,-1,-1,-1,-1,1,-1,-1,1,1,-1,1)

Data_teatru$`PPS pre_Total` <- 
  SpecialRowSums(
  psych::reverse.code(items = Data_teatru[ ,sprintf("PPS pre_%d", 1:14)], keys = keys_PSS,  mini = 0, maxi = 4),
  napercent = .1)  # not more than 1 NAs for 14 items 
Data_teatru$`PPS post_Total` <- 
  SpecialRowSums(
    psych::reverse.code(items = Data_teatru[ ,sprintf("PPS post_%d", 1:14)], keys = keys_PSS,  mini = 0, maxi = 4),
    napercent = .1)
Data_psiho$`PPS pre_Total` <- 
  SpecialRowSums(
    psych::reverse.code(items = Data_psiho[ ,sprintf("PPS pre_%d", 1:14)], keys = keys_PSS,  mini = 0, maxi = 4),
    napercent = .1)  # not more than 1 NAs for 14 items 
Data_psiho$`PPS post_Total` <- 
  SpecialRowSums(
    psych::reverse.code(items = Data_psiho[ ,sprintf("PPS post_%d", 1:14)], keys = keys_PSS,  mini = 0, maxi = 4),
    napercent = .1)

## PANAS: Positive Affect Score = sum items 1, 3, 5, 9, 10, 12, 14, 16, 17, 19. Negative Affect Score = sum items 2, 4, 6, 7, 8, 11, 13, 15, 18, 20.
Data_teatru$`PA pre_Total` <- SpecialRowSums(Data_teatru[ ,35 + c(1,3,5,9,10,12,14,16,17,19)], napercent = .11) # not more than 1 NAs for 10 items
Data_teatru$`NA pre_Total` <- SpecialRowSums(Data_teatru[ ,35 + c(2,4,6,7,8,11,13,15,18,20)], napercent = .11)
Data_psiho$`PA pre_Total` <- SpecialRowSums(Data_psiho[ ,35 + c(1,3,5,9,10,12,14,16,17,19)], napercent = .11) 
Data_psiho$`NA pre_Total` <- SpecialRowSums(Data_psiho[ ,35 + c(2,4,6,7,8,11,13,15,18,20)], napercent = .11)

Data_teatru$`PA post_Total` <- SpecialRowSums(Data_teatru[ ,79 + c(1,3,5,9,10,12,14,16,17,19)], napercent = .11) 
Data_teatru$`NA post_Total` <- SpecialRowSums(Data_teatru[ ,79 + c(2,4,6,7,8,11,13,15,18,20)], napercent = .11)
Data_psiho$`PA post_Total` <- SpecialRowSums(Data_psiho[ ,79 + c(1,3,5,9,10,12,14,16,17,19)], napercent = .11) 
Data_psiho$`NA post_Total` <- SpecialRowSums(Data_psiho[ ,79 + c(2,4,6,7,8,11,13,15,18,20)], napercent = .11)


# Define other grouping varibles
Data_teatru <- 
  Data_teatru %>%
    mutate(Etapa = case_when(`Etapă, zi` %in% c("I.1", "I.2") ~ "I",
                             `Etapă, zi` %in% c("II.1",  "II.2") ~ "II",
                             `Etapă, zi` %in% c("III.1", "III.2") ~ "III",
                             `Etapă, zi` %in% c("IV.1", "IV.2") ~ "IV",
                             TRUE ~ NA_character_),
           Zi = case_when(`Etapă, zi` == "I.1" ~ "zi1", 
                          `Etapă, zi` == "I.2" ~ "zi2",  
                          `Etapă, zi` == "II.1" ~ "zi3", 
                          `Etapă, zi` == "II.2" ~ "zi4",
                          `Etapă, zi` == "III.1" ~ "zi5", 
                          `Etapă, zi` == "III.2" ~ "zi6", 
                          `Etapă, zi` == "IV.1" ~ "zi7", 
                          `Etapă, zi` == "IV.2" ~ "zi8", 
                          TRUE ~ NA_character_)) %>%
  unite(col = "Etapa_Zi", Etapa, Zi, remove = FALSE)

Data_psiho <- 
  Data_psiho %>%
  mutate(Etapa = case_when(`Etapă, zi` %in% c("I.1", "I.2") ~ "I",
                           `Etapă, zi` %in% c("II.1",  "II.2") ~ "II",
                           `Etapă, zi` %in% c("III.1", "III.2") ~ "III",
                           `Etapă, zi` %in% c("IV.1", "IV.2") ~ "IV",
                           TRUE ~ NA_character_),
         Zi = case_when(`Etapă, zi` == "I.1" ~ "zi1", 
                        `Etapă, zi` == "I.2" ~ "zi2",  
                        `Etapă, zi` == "II.1" ~ "zi3", 
                        `Etapă, zi` == "II.2" ~ "zi4",
                        `Etapă, zi` == "III.1" ~ "zi5", 
                        `Etapă, zi` == "III.2" ~ "zi6", 
                        `Etapă, zi` == "IV.1" ~ "zi7", 
                        `Etapă, zi` == "IV.2" ~ "zi8", 
                        TRUE ~ NA_character_)) %>%
  unite(col = "Etapa_Zi", Etapa, Zi, remove = FALSE)

## Unite data sets
Data_teatru$Dataset <- rep("teatru", nrow(Data_teatru))
Data_psiho$Dataset <- rep("psiho", nrow(Data_psiho))

Data_United <- rbind(Data_teatru, Data_psiho)
```


# Sample descriptives

```{r sample_desc}
cat("## Number of subjects")
Data_United %>% 
 dplyr::rename(ID = `Indicativ subiect`) %>% 
 dplyr::summarise(count = dplyr::n_distinct(ID))

cat("## Number of subjects by Teatru/Psiho")
Data_United %>%
 dplyr::rename(ID = `Indicativ subiect`) %>% 
 group_by(Dataset) %>%
 dplyr::summarise(count = dplyr::n_distinct(ID))
```

# Outcomes Pre-Post Intervention

```{r outcomes_aps_pps, fig.width=6, fig.align='center', fig.height=5, results='asis'}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~   OUTCOMES PRE-POST INTERVENTION   ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## Function to run all for teatru, psiho and United
func_prepost_tot <- function(df){
  
  Data_melt <-
    df[, c("Indicativ subiect", "Grupa", "Nume Prenume", "Etapă, zi", 
           "APS pre_Total", "APS post_Total", 
           "PPS pre_Total", "PPS post_Total")] %>% 
    gather("APS pre_Total":"PPS post_Total", key = "variable", value = "value")  %>% 
    mutate_at(vars(c(1:5)), funs(as.factor)) %>% 
    mutate(variable = factor(variable, levels = c("APS pre_Total", "APS post_Total", 
                                                  "PPS pre_Total", "PPS post_Total")))
  
  # APS t test - paired
  aps_ttest <- 
    df %>%
    select(`Indicativ subiect`, `APS pre_Total`, `APS post_Total`) %>%
    group_by(`Indicativ subiect`) %>%
    summarise_all(funs(na.omit(.)[1])) %>%                        # squash rows with NAs per id
    # filter_all(all_vars(!is.na(.))) %>%                         # drop row if any column is NA -- dont use here
    do(broom::tidy(t.test(.$`APS pre_Total`,
                          .$`APS post_Total`,
                          mu = 0,
                          alt = "two.sided",
                          paired = TRUE,
                          conf.level = 0.95))) 
  aps_ttest_out <- knitr::kable(aps_ttest, caption = paste0(deparse(substitute(df)), " APS"), format = 'pandoc')
  
  # APS plot t test - unpaired
  aps_plot <-   
    Data_melt %>%
    filter(variable %in% c("APS pre_Total", "APS post_Total")) %>%
    #group_by(`Etapă, zi`) %>%
    ggplot(aes(x = variable, y = value)) +
    geom_boxplot() +
    stat_summary(fun.data = mean_se,  colour = "darkred") +
    xlab("") +
    ggtitle(deparse(substitute(df))) +
    #facet_wrap(~`Etapă, zi`) +
    ggpubr::stat_compare_means(method = "t.test", 
                               label = "p.signif",                                         # to avoid scientific notation of very small p-values
                               #paired = TRUE, 
                               comparisons = list(c("APS pre_Total", "APS post_Total")))  
  
  
  # PPS t test - paired
  pps_ttest <- 
    df %>%
    select(`Indicativ subiect`, `PPS pre_Total`, `PPS post_Total`) %>%
    group_by(`Indicativ subiect`) %>%
    summarise_all(funs(na.omit(.)[1])) %>%                        # squash rows with NAs per id
    # filter_all(all_vars(!is.na(.))) %>%                         # drop row if any column is NA -- dont use here
    do(broom::tidy(t.test(.$`PPS pre_Total`,
                          .$`PPS post_Total`,
                          mu = 0,
                          alt = "two.sided",
                          paired = TRUE,
                          conf.level = 0.95)))
  pps_ttest_out <- knitr::kable(pps_ttest, caption = paste0(deparse(substitute(df)), " PPS"), format = 'pandoc') 
  
  # PPS plot t test - unpaired
  pps_plot <-
    Data_melt %>%
    filter(variable %in% c("PPS pre_Total", "PPS post_Total")) %>%
    #group_by(`Etapă, zi`) %>%
    ggplot(aes(x = variable, y = value)) +
    geom_boxplot() +
    stat_summary(fun.data = mean_se,  colour = "darkred") +
    xlab("") +
    ggtitle(deparse(substitute(df))) +
    #facet_wrap(~`Etapă, zi`) +
    ggpubr::stat_compare_means(method = "t.test", 
                               label = "p.signif",                                         # to avoid scientific notation of very small p-values
                               #paired = TRUE, 
                               comparisons = list(c("PPS pre_Total", "PPS post_Total"))) 
  
  print(aps_ttest_out)
  print(aps_plot)
  print(pps_ttest_out)
  print(pps_plot)
}


cat("### Teatru")
func_prepost_tot(Data_teatru)
cat("### Psiho")
func_prepost_tot(Data_psiho)
cat("### United")
func_prepost_tot(Data_United)
```


# PANAS (PANAS for zi1, zi3, zi5, zi7 are Pre; zi2, zi4, zi6, zi8 are Post )

```{r outcome_panas, fig.width=12, fig.height=9, results='asis'}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~   OUTCOMES PRE-POST for PANAS    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# PANAS for zi1, zi3, zi5, zi7 are Pre; zi2, zi4, zi6, zi8 are Post 
## Function plot PANAS, compare by zi
plot_panas_zi <- function(df, pre_var, post_var){
  df_modif <-
    df %>%
    gather(pre_var, post_var, key = "variable", value = "value") 
  
  stat.test <-
    df_modif %>%
    select(value, variable, Zi) %>%
    tidyr::drop_na() %>%                          # need to remove NAs so factor level of condition can be droped as well         
    rstatix::t_test(value ~ Zi) %>%                # automatically does pairwise, but has problems were factor levels of grouping with NA
    # rstatix::adjust_pvalue() %>%                          
    rstatix::add_significance("p") %>%                                                       
    filter(p.signif != "ns") 
  
  p<-
    ggplot(df_modif, aes(y = value, x = Zi)) +
    ggtitle(paste0(deparse(substitute(df)), " : ", pre_var, " - " ,post_var)) + 
    geom_boxplot() + stat_summary(fun.data = mean_se,  colour = "darkred") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
  
  if(nrow(stat.test) > 0){
    p <- 
      p + stat_pvalue_manual(stat.test, label = "p.signif", 
                             y.position = seq(max(df_modif$value, na.rm = TRUE)+2, max(df_modif$value, na.rm = TRUE)*1.4, 
                                          length.out = nrow(stat.test)))                             # very hacky
  }
  
  return(stat.test) %>% print(n = Inf)
  print(p)
}

cat("### Teatru")
plot_panas_zi(Data_teatru, "PA pre_Total", "PA post_Total")
plot_panas_zi(Data_teatru, "NA pre_Total", "NA post_Total")
cat("### Psiho")
plot_panas_zi(Data_psiho, "PA pre_Total", "PA post_Total")
plot_panas_zi(Data_psiho, "NA pre_Total", "NA post_Total")
cat("### United")
plot_panas_zi(Data_United, "PA pre_Total", "PA post_Total")
plot_panas_zi(Data_United, "NA pre_Total", "NA post_Total")
```


# IOS (Pre on begining of Etapa, Post on end of Etapa)

```{r ios, fig.width=13, fig.height=11, results='asis'}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~   IOS - pre on begining of etapa, post on end  ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## Function plot pre post data faceted by zi
plot_prepost_zi <- function(df, pre_var, post_var){
  df %>%
    gather(pre_var, post_var, key = "variable", value = "value") %>%
    mutate(variable = factor(variable, levels = c(pre_var, post_var))) %>%
    ggplot(aes(y = value, x = variable)) +
    facet_wrap(~Zi, nrow = 1) + 
    ggtitle(deparse(substitute(df))) + 
    geom_boxplot() + stat_summary(fun.data = mean_se,  colour = "darkred")  +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ggpubr::stat_compare_means(method = "t.test",
                               label = "p.signif",                                         # to avoid scientific notation of very small p-values
                               #paired = TRUE,
                               comparisons = list(c(pre_var, post_var)))
}


## Function plot pre post data adjusted comparisons of all 
plot_prepost_zi2 <- function(df, pre_var, post_var){
  df_modif <- 
    df %>%
    gather(pre_var, post_var, key = "variable", value = "value") %>%
    mutate(variable = factor(variable, levels = c(pre_var, post_var)),
           condition = interaction(variable, Zi),
           condition = as.factor(condition)) 
  
  stat.test <-
    df_modif %>%
    # group_by(`Indicativ subiect`) %>%
    rstatix::t_test(value ~ condition) %>%
    # rstatix::adjust_pvalue() %>%
    rstatix::add_significance("p") %>%
    filter(p.signif != "ns") 
  
  p <- 
    ggplot(df_modif, aes(y = value, x = condition)) +
      ggtitle(deparse(substitute(df))) + 
      geom_boxplot() + stat_summary(fun.data = mean_se,  colour = "darkred") +
      theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
      stat_pvalue_manual(stat.test, label = "p.signif", 
                         y.position = seq(max(df_modif$value, na.rm = TRUE)+2, max(df_modif$value, na.rm = TRUE)*2, 
                                          length.out = nrow(stat.test)))                                                  # very hacky
  
  print(p)
  return(stat.test) %>% print(n = Inf)
  
}


# cat("## By Zi")
cat("### Teatru")
plot_prepost_zi(Data_teatru, "IOS pre", "IOS post")
plot_prepost_zi2(Data_teatru, "IOS pre", "IOS post")
cat("### Psiho")
plot_prepost_zi(Data_psiho, "IOS pre", "IOS post")
plot_prepost_zi2(Data_psiho, "IOS pre", "IOS post")
cat("### United")
plot_prepost_zi(Data_United, "IOS pre", "IOS post")
plot_prepost_zi2(Data_United, "IOS pre", "IOS post")


cat("## ANOVA for Baseline each Etapa")
plot_anova_base <- function(df, pre_var, post_var){
  df %>%
    select(Etapa, Zi, pre_var, post_var) %>%
    gather(pre_var, post_var, key = "variable", value = "value") %>%
    mutate(variable = factor(variable, levels = c(pre_var, post_var))) %>%
    filter(variable == pre_var)  %>%
      
    jmv::ANOVA(formula = value ~ Zi,
               effectSize = list('eta', 'partEta')) -> anova_base
    
    print(tibble::as.tibble(anova_base$main))
}
plot_anova_base(Data_United, "IOS pre", "IOS post")


cat("## By Etapa")
plot_prepost_etapa <- function(df, pre_var, post_var){
  df_modif <-
    df %>%
      select(Etapa, Zi, pre_var, post_var) %>%
      gather(pre_var, post_var, key = "variable", value = "value") %>%
      mutate(variable = factor(variable, levels = c(pre_var, post_var))) %>%
      filter(variable == pre_var & Zi %in% sprintf("zi%d", seq(1, 8, by = 2))  |
             variable == post_var & Zi %in% sprintf("zi%d", seq(2, 8, by = 2)))  
  
  stat.test <- 
    df_modif %>%     
      group_by(Etapa) %>%
      rstatix::t_test(value ~ Zi) %>%
      # rstatix::adjust_pvalue() %>%
      rstatix::add_significance("p") %>%
      filter(p.signif != "ns")
  
  p <- 
    ggplot(data = df_modif, aes(y = value, x = variable)) +
    facet_wrap(~Etapa, nrow = 1) + 
    ggtitle(deparse(substitute(df))) + 
    geom_boxplot() + stat_summary(fun.data = mean_se,  colour = "darkred")  +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ggpubr::stat_compare_means(method = "t.test",
                               label = "p.signif",                                         # to avoid scientific notation of very small p-values
                               #paired = TRUE,
                               comparisons = list(c(pre_var, post_var)))

  print(p)
  return(stat.test) %>% print(n = Inf)
}
plot_prepost_etapa(Data_teatru, "IOS pre", "IOS post")


```


# VAS variables (multiple measurements on each zi)

```{r vas_variables, fig.width=15, fig.height=11, results='asis'}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~   Variables multiple measurements in zi    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## Function plot pre-ex1-ex2-..-post data faceted by zi
plot_preexpost_zi <- function(df, pre_var, post_x1_var, post_x2_var, post_x3_var){
  df_modif <-
    df %>%
    gather(pre_var, post_x1_var, post_x2_var, post_x3_var, key = "variable", value = "value") %>%
    mutate(variable = factor(variable, levels = c(pre_var, post_x1_var, post_x2_var, post_x3_var)))
    
  stat.test <-
    df_modif %>%
    group_by(Zi) %>%
    tidyr::drop_na(value) %>%                                     # filter so grouping factor levels get droped and we can compare with unevel levels
    rstatix::t_test(value ~ variable) %>%                # pairwise
    rstatix::add_significance("p") %>%                                    
    filter(p.signif != "ns") 
  
  p<-
    ggplot(df_modif, aes(y = value, x = variable)) +
      facet_wrap(~Zi, nrow = 1) + 
      ggtitle(deparse(substitute(df))) + 
      geom_boxplot() + stat_summary(fun.data = mean_se,  colour = "darkred") +
      theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
      stat_pvalue_manual(stat.test, label = "p.signif", 
                         y.position = seq(max(df_modif$value, na.rm = TRUE)+2, max(df_modif$value, na.rm = TRUE)*2, 
                                          length.out = nrow(stat.test)))                                                  # very hacky
  
  return(stat.test) %>% print(n = Inf)
  p
}

cat("## By Zi")
cat("## VAS stres")
cat("### Teatru")
plot_preexpost_zi(Data_teatru, "VAS stres pre", "VAS stres post ex1", "VAS stres post ex2", "VAS stres post ex3")
cat("### Psiho")
plot_preexpost_zi(Data_psiho, "VAS stres pre", "VAS stres post ex1", "VAS stres post ex2", "VAS stres post ex3")
cat("### United")
plot_preexpost_zi(Data_United, "VAS stres pre", "VAS stres post ex1", "VAS stres post ex2", "VAS stres post ex3")


cat("## VAS stare de bine") 
cat("### Teatru")
plot_preexpost_zi(Data_teatru, "VAS stare de bine pre", "VAS stare de bine post ex1", "VAS stare de bine post ex2", "VAS stare de bine post ex3")
cat("### Psiho")
plot_preexpost_zi(Data_psiho, "VAS stare de bine pre", "VAS stare de bine post ex1", "VAS stare de bine post ex2", "VAS stare de bine post ex3")
cat("### United")
plot_preexpost_zi(Data_United, "VAS stare de bine pre", "VAS stare de bine post ex1", "VAS stare de bine post ex2", "VAS stare de bine post ex3")


cat("## VAS corp")
cat("### Teatru")
plot_preexpost_zi(Data_teatru, "VAS corp pre", "VAS corp post ex1", "VAS corp post ex2", "VAS corp post ex3")
cat("### Psiho")
plot_preexpost_zi(Data_psiho, "VAS corp pre", "VAS corp post ex1", "VAS corp post ex2", "VAS corp post ex3")
cat("### United")
plot_preexpost_zi(Data_United, "VAS corp pre", "VAS corp post ex1", "VAS corp post ex2", "VAS corp post ex3")




plot_preexpost_etapa <- function(df, pre_var, post_x1_var, post_x2_var, post_x3_var){
  df_modif <-
    df %>%
    gather(pre_var, post_x1_var, post_x2_var, post_x3_var, key = "variable", value = "value") %>%
    filter((variable == pre_var & Zi %in% sprintf("zi%d", seq(1, 8, by = 2)))  |                           # pre  
           (variable == post_x1_var & Zi %in% c("zi2", "zi8"))  |                                    # post variations
           (variable == post_x2_var & Zi == "zi4")  |
           (variable == post_x3_var & Zi == "zi6"))  %>%
    mutate(variable = case_when(stringr::str_detect(variable, "pre") ~ "pre",
                                stringr::str_detect(variable, "post") ~ "post")) %>%
    mutate(variable = factor(variable, levels = c("pre", "post")))

  stat.test <-
    df_modif %>%
    group_by(Etapa) %>%
    tidyr::drop_na(value) %>%                                     # filter so grouping factor levels get droped and we can compare with unevel levels
    rstatix::t_test(value ~ variable) %>%                # pairwise
    rstatix::add_significance("p") %>%
    filter(p.signif != "ns")

  p<-
    ggplot(df_modif, aes(y = value, x = variable)) +
      facet_wrap(~Etapa, nrow = 1) +
      ggtitle(deparse(substitute(df))) +
      geom_boxplot() + stat_summary(fun.data = mean_se,  colour = "darkred") +
      theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
      stat_pvalue_manual(stat.test, label = "p.signif",
                         y.position = seq(max(df_modif$value, na.rm = TRUE)+2, max(df_modif$value, na.rm = TRUE)*2,
                                          length.out = nrow(stat.test)))                                                  # very hacky

  print(p)
  return(stat.test) %>% print(n = Inf)
}

cat("## By Etapa - Only United")
cat("### VAS Stres")
plot_preexpost_etapa(Data_United, "VAS stres pre", "VAS stres post ex1", "VAS stres post ex2", "VAS stres post ex3")
cat("### VAS St bine")
plot_preexpost_etapa(Data_United, "VAS stare de bine pre", "VAS stare de bine post ex1", "VAS stare de bine post ex2", "VAS stare de bine post ex3")
cat("### VAS St bine corp")
plot_preexpost_etapa(Data_United, "VAS corp pre", "VAS corp post ex1", "VAS corp post ex2", "VAS corp post ex3")
```


# Define function Moderation

```{r def_fun_find_mod}
find_mod <- function(df, dfp = NULL, num_only = TRUE, verbose = TRUE) {
  count = 0
  moderation_model_list <<- list()

  if(num_only == TRUE){
  numeric_cols <- unlist(lapply(df, is.numeric))                                      # get only numeric columns
  df <- df[, numeric_cols]
  }
  
  # restricted permutations for Moderation - Check: choose(len_names, 3)*3
  names <- colnames(df)
  len_names = length(names)
  
  if(is.null(dfp)){
    dfp <- lapply(1:len_names, function(i){
      tmp <- lapply(1:(len_names-1), function(j){
        tmp <- lapply((j+1):len_names, function(k){
          if(j != i & k != i) c(names[i], names[j], names[k])
        })
        do.call(rbind, tmp)
      })
      do.call(rbind, tmp)
    })
    dfp <- do.call(rbind.data.frame, dfp)
    names(dfp) <- paste("var", 1:3, sep = "_")
    dfp[, ] <- lapply(dfp[, ], as.character)    
  } else {
    dfp <- dfp
  }
  
  for (row in 1:nrow(dfp)) {                
    
    results <- medmod::mod(data = df,                                                   # mod does centering automatically
                          dep = dfp[row, 1], mod = dfp[row, 2], pred = dfp[row, 3], 
                          estMethod = "standard", test = TRUE, 
                          simpleSlopeEst = FALSE, simpleSlopePlot = FALSE)             # when testing use estMethod = 'bootstrap', bootstrap = 500 
    
    pmod <- as.data.frame(results$mod)[3,5]

    if(pmod < 0.05 && !is.na(pmod)) {
      count <- count + 1
        if(verbose == TRUE) {
        cat("Dependent Variable:", dfp[row, 1])
        print(results$mod) 
        }
      moderation_model_list[["Model"]][[paste("model", count, sep = "_")]] <<- as.data.frame(results$mod)   # return as list of dataframes
      moderation_model_list[["Syntax"]][[paste("model", count, sep = "_")]] <<- results$modelSyntax
      
    }
  }
  cat("\n","Report: ", count, "significant moderations out of", row, "total tries.")
}

## ex dfp
# dfp <- data.frame(
#   var1 = colnames(Data_med_melt)[grep("_post", colnames(Data_med_melt))],
#   var2 = rep("Condition", 13),
#   var3 = colnames(Data_med_melt)[grep("_pre", colnames(Data_med_melt))],
#   stringsAsFactors = FALSE
# )
# find_med(df = Data_med_melt, dfp = dfp, num_only = FALSE) 

```

# Moderation on PrePost (APS, PSS)

```{r mod_srs, results='asis'}
# Make dataframe of vars and mods
mods <- c("IOS post", "SRS post_Rela<U+021B>ia", "SRS post_Global")  # define moderators
pres <- c("PPS pre_Total", "APS pre_Total")
posts <- c("PPS post_Total", "APS post_Total")   
dfp <- merge(mods, cbind(pres, posts), by = NULL)  # by = NULL causes merge to do simple combinatorial data replication
dfp <- dfp[, c("posts", "x", "pres")]     # reorder columns for find_mod
dfp <- data.frame(lapply(dfp, as.character), stringsAsFactors = FALSE)

# Data - Summarizing gives means for repeated moderators while prepost outcomes are still same values
mod_prepost <- 
  Data_United %>%
  select("Indicativ subiect", "Etapa", "Zi", mods,  pres, posts) %>%
  group_by(`Indicativ subiect`) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE)
  
# For PrePost Outcome (not measured for Etape)
find_mod(df = mod_prepost, dfp = dfp, num_only = FALSE)


###############################################################################

## idea not used here
  # filter(Zi %in% c("zi1", "zi8")) %>% 
  # pivot_longer(cols = matches("pre|post"), names_to = "variable", values_to = "value")



# Data_United %>% 
#   filter(Etapa == "I") %>%
#   medmod::mod(data = ., 
#             dep = "PPS post_Total", mod = "IOS post", pred = "PPS pre_Total", 
#             estMethod = "standard", test = TRUE, 
#             simpleSlopeEst = FALSE, simpleSlopePlot = TRUE)
```




<!-- Session Info and License -->

<br>

# Session Info
```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->
&nbsp;
<hr />
<p style="text-align: center;">A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a></p>
<p style="text-align: center;"><span style="color: #808080;"><em>claudiu.papasteri@gmail.com</em></span></p>
&nbsp;
