---
title: "<br> Scholars wave 1 - partial data" 
subtitle: "Initial Analysis"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    # pdf_document: 
            # toc: true
            # toc_depth: 2
            # number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---


<!-- Setup -->


```{r setup, include=FALSE}
# General R options
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation
options(repos = c(getOption("repos")["CRAN"], CRANextra = "https://mirror.clientvps.com/CRAN/"))  # use CRAN as default, set CRANextra to Nürnberg mirror

if (!require("pacman")) install.packages("pacman", dependencies = TRUE)
if (!require("tidyverse")) install.packages("tidyverse", dependencies = TRUE)
packages <- c(
  "papaja",
  "here", "fs",
  "conflicted",
  "rio",
  "psych",          
  "ggstatsplot",
  "ggplot2", "scales",
  "report",
  "gtsummary",
  "limonaid", "sticky"
  # , ...
)
pacman::p_load(char = packages, update = FALSE)

# Set here to Rnotebook directory
here::set_here()
unloadNamespace("here")                   # need new R session or unload namespace for .here file to take precedence over .Rproj
notebook_name <- fs::path_file(here::here())

# Solve conflicts in favor of tidyverse
conflicted::conflict_prefer("filter", winner = "dplyr")
conflicted::conflict_prefer("select", winner = "dplyr")
conflicted::conflict_prefer("slice", winner = "dplyr")
conflicted::conflict_prefer("rename", winner = "dplyr")
conflicted::conflict_prefer("count", winner = "dplyr")
conflicted::conflict_prefer("recode", winner = "dplyr")
conflicted::conflict_prefer("fill", winner = "tidyr")

# Set kintr options including root.dir pointing to the .here file in Rnotebook directory
knitr::opts_chunk$set(
  root.dir = here::here(),
  #fig.width = 5, fig.asp = 1/3, 
  comment = "#",
  collapse = TRUE,
  echo = TRUE, warning = TRUE, message = TRUE, cache = TRUE       # echo = False for github_document, but will be folded in html_notebook
)

# Themes for ggplot2 plotting (here used APA style)
theme_set(papaja::theme_apa())
```





<!-- Functions -->

# Define functions

```{r}
## Define function that recodes to numeric, but watches out to coercion to not introduce NAs
colstonumeric <- function(df){
  tryCatch({
    df_num <- as.data.frame(
      lapply(df,
             function(x) { as.numeric(as.character(x))})) 
  },warning = function(stop_on_warning) {
    message("Stoped the execution of numeric conversion: ", conditionMessage(stop_on_warning))
  }) 
}
##
## Define function that reverse codes items
ReverseCode <- function(df, tonumeric = FALSE, min = NULL, max = NULL) {
  if(tonumeric) df <- colstonumeric(df)
  df <- (max + min) - df
}
##
## Define function that scores only rows with less than 10% NAs (returns NA if all or above threshold percentage of rows are NA); can reverse code if vector of column indexes and min, max are provided.
ScoreLikert <- function(df, napercent = .1, tonumeric = FALSE, reversecols = NULL, min = NULL, max = NULL, engine = "sum") {
  reverse_list <- list(reversecols = reversecols, min = min, max = max)
  reverse_check <- !sapply(reverse_list, is.null)
  
  # Recode to numeric, but watch out to coercion to not introduce NAs
  colstonumeric <- function(df){
    tryCatch({
      df_num <- as.data.frame(
        lapply(df,
               function(x) { as.numeric(as.character(x))})) 
    },warning = function(stop_on_warning) {
      message("Stoped the execution of numeric conversion: ", conditionMessage(stop_on_warning))
    }) 
  }
  
  if(tonumeric) df <- colstonumeric(df)
  
  if(all(reverse_check)){
    df[ ,reversecols] <- (max + min) - df[ ,reversecols]
  }else if(any(reverse_check)){
    stop("Insuficient info for reversing. Please provide: ", paste(names(reverse_list)[!reverse_check], collapse = ", "))
  }
  
  if(engine == "sum") {
    return(
      ifelse(rowSums(is.na(df)) > ncol(df) * napercent,
             NA,
             rowSums(df, na.rm = TRUE) * NA ^ (rowSums(!is.na(df)) == 0)
      )
    )  
  }
  
  if(engine == "mean") {
    return(
      ifelse(rowMeans(is.na(df)) > ncol(df) * napercent,
             NA,
             rowMeans(df, na.rm = TRUE) * NA ^ (rowSums(!is.na(df)) == 0)
      )       
    )
  }
  
    if(engine == "mean_na") {
      df[is.na(df)] <- 0
      rowMeans(df)
    }
}
```



<!-- Report -->

# Read survey structure

```{r, message=FALSE}
folder <- here::here("Rsyntax&data")
data_name <- "survey_686732_R_data_file.csv"
script_name <- "survey_686732_R_syntax_file.R"
  
# Check most recent .csv file
last_csv_file <- 
  dir(folder, pattern = ".*csv", full.names = TRUE) %>% 
  file.info() %>%
  dplyr::arrange(dplyr::desc(ctime)) %>%
  dplyr::slice(1) %>%
  row.names()
if(identical(last_csv_file, file.path(folder, data_name))) {
  cat("Most recent .csv is used.")
} else {
  cat("NOT using the most recent .csv!")
}

# -------------------------------------------------------------------------
# Read data
library(limonaid)
library(sticky)  # need this for sticky labels

df <- limonaid::ls_import_data(
  datafile = file.path(folder, data_name),
  scriptfile = file.path(folder, script_name),
  massConvertToNumeric = FALSE
)

df_compl <-
  df %>%
  filter(lastpage == 17)

# -------------------------------------------------------------------------
# Labels to factor levels levels ("label" = question text; "labels" = response options text)
# library(labelled)
# library(sjlabelled)
# sjlabelled::get_labels(df$G01Q59_SQ008, attr.only = TRUE, values = "as.prefix")
# sjlabelled::get_values(df$G01Q59_SQ008)
# sjlabelled::as_label(df$G01Q59_SQ008, prefix = TRUE, keep.labels = TRUE) 
# sjlabelled::as_character(df$G01Q59_SQ008, prefix = TRUE, keep.labels = TRUE)
# labelled::var_label(df$G01Q59_SQ008)
# labelled::to_factor(df$G01Q59_SQ008, levels = "values")

lime_label_recode <- function (x, prefix = FALSE) {
  labels <- attr(x, "labels", exact = TRUE)
  if (is.null(labels)) {
    x
  } else {
    labels <- unname(labels)
    values <- names(attr(x, "labels", exact = TRUE))
    if (prefix) {
      labels <- sprintf("[%s] %s", values, labels)
    }
    # No recoding solution preserve attributes, even with sticky
      x_rec <- c(labels, x)[match(x, c(values, x))]
    attributes(x_rec) <- attributes(x)  # reattach attributes
    x_rec
  }
}
# test_df <- cbind(df$G02Q02_SQ021, lime_label_recode(df$G02Q02_SQ021))
# lime_label_recode(df$G01Q59_SQ008)
# lime_label_recode(df$G04Q05_SQ001)

# -------------------------------------------------------------------------
# Recode using labels
# cols_to_recode <- lapply(df, function(x) {!is.null(attr(x, "labels", exact = TRUE))})
# cols_to_recode <- which(unlist(cols_to_recode))

# df_recoded <- df
# list_recoded <- lapply(df_recoded[, cols_to_recode], lime_label_recode)
# df_recoded[, cols_to_recode] <- as.data.frame(do.call(cbind, list_recoded))

# df_recoded <-
#   df %>%
#   mutate(across(all_of(cols_to_recode), lime_label_recode)) 

df_recoded <-
  df %>%
  mutate(across(everything(), lime_label_recode)) %>%   # some values have same labels: df$G01Q60_SQ006
  mutate(across(where(is.character), function(col) iconv(col, to="UTF-8")))  # encoding: df_recoded$G01Q56
```



# Score 3 Questionnaires

```{r, warning=FALSE}
# ------------------------------------------------------------------------------
# Define 3 scales
# ------------------------------------------------------------------------------
# ATSPPH - 10 items (likert 0-3) total sum
atspph_idx <- 184:193  # grep("G06Q13", names(df));  df[, grep("G06Q13", names(df), value = TRUE)]
atspph_labs <- unique(lapply(df[, atspph_idx], attr, "labels"))
atspph_rev <- c(2, 4, 8, 9, 10)

atspph_recode <- function(df, rev) {
  df %>%
    mutate(
      across(everything(),
        ~ case_when(
          . == "AO02" ~ 0,
          . == "AO03" ~ 1,
          . == "AO04" ~ 2,
          . == "AO05" ~ 3
        )
      )       
    ) %>%
    mutate(   # here reverse code
      across(rev,
      ~ 3 - .x 
      )
    )
}  # atspph_recode(df_compl[, atspph_idx], atspph_rev)

# FSozU - 6 items (likert 1-5) total mean
fsozu_idx <- 222:227 # grep("G12Q45", names(df)); df[, grep("G12Q45", names(df), value = TRUE)]  
fsozu_labs <- unique(lapply(df[, fsozu_idx], attr, "labels"))  

fsozu_recode <- function(df) {
  df %>%
    mutate(
      across(everything(),
        ~ case_when(
          . == "AO01" ~ 1,
          . == "AO02" ~ 2,
          . == "AO03" ~ 3,
          . == "AO04" ~ 4,
          . == "AO05" ~ 5
        )
      )       
    ) 
}  # fsozu_recode(df_compl[, fsozu_idx])

# PMHSS - 24 items (likert 1-5) subscale sum
pmhss_idx <- 228:251   # grep("G13Q46", names(df)); df[, grep("G13Q46", names(df), value = TRUE)]
pmhss_labs <- unique(lapply(df[, pmhss_idx], attr, "labels"))

pmhss_aware <- c(2, 4, 5, 6, 8, 10, 11, 12)  
pmhss_agree <- c(14, 16, 17, 18, 20, 22, 23, 24) 
pmhss_posit <- c(1, 3, 7, 9, 13, 15, 19, 21)

pmhss_recode <- function(df) {
  df %>%
    mutate(
      across(everything(),
        ~ case_when(
          . == "AO01" ~ 1,
          . == "AO02" ~ 2,
          . == "AO03" ~ 3,
          . == "AO04" ~ 4,
          . == "AO05" ~ 5
        )
      )       
    )
}  # pmhss_recode(df_compl[, pmhss_idx])

# ------------------------------------------------------------------------------
# Recode & Score
df_compl[, atspph_idx] <- atspph_recode(df_compl[, atspph_idx], atspph_rev)
df_compl[, fsozu_idx] <- fsozu_recode(df_compl[, fsozu_idx])
df_compl[, pmhss_idx] <- pmhss_recode(df_compl[, pmhss_idx])

df_compl$help_seek <- ScoreLikert(df_compl[, atspph_idx], napercent = .5, engine = "sum")
df_compl$soc_supp <- ScoreLikert(df_compl[, fsozu_idx], napercent = .5, engine = "mean")

df_compl$aware <- ScoreLikert(df_compl[, pmhss_idx][pmhss_aware], napercent = .5, engine = "sum") 
df_compl$agree <- ScoreLikert(df_compl[, pmhss_idx][pmhss_agree], napercent = .5, engine = "sum")
df_compl$posit <- ScoreLikert(df_compl[, pmhss_idx][pmhss_posit], napercent = .5, engine = "sum")
```


# Some analyses on 3 Questionnaires

```{r, echo=FALSE}
vars_demog <- c("Q00", "G01Q23", "G01Q24", "G01Q26")
vars_demog_names <- c("sex", "year_birth", "grade", "resid")
lapply(df_compl[, vars_demog], attr, "label")

df_scales <- 
  df_compl %>%
  # labelled::remove_attributes("label") %>%
  # labelled::remove_attributes("labels") %>%
  rename_with(~ c(vars_demog_names), all_of(vars_demog)) %>%
  select(all_of(vars_demog_names),
         help_seek, soc_supp, aware, agree, posit) %>%
  mutate(across(all_of(vars_demog_names), lime_label_recode)) %>%
  mutate(age = 2023 - as.numeric(year_birth))
```

### Just checks

```{r, echo=FALSE, warning=FALSE, fig.height=10, fig.width=10}
plot_scales <- GGally::ggpairs(df_scales[, c(1, 10, 3:9)], progress = FALSE)
plot_scales
```

```{r, echo=FALSE, warning=FALSE, fig.height=7, fig.width=7}
plot_scales2 <- PerformanceAnalytics::chart.Correlation(df_scales[, c(10, 5:9)])
plot_scales2
```


### Mod - just check

```{r mod, cache=TRUE}
# find_mod(df_scales)
# moderation_model_list #1,2,3,6,7,10,11,12

mod_synth <-
  moderation_model_list %>%
  purrr::pluck("Syntax") %>%
  stringr::str_match("# Regressions\\\n(.*?)\\\n\\\n#") %>%   # string between "# Regressions\n" and "\n\n#"
  as.data.frame() %>%
  dplyr::pull(2) %>% 
  stringr::str_remove_all(fixed("b0*1 + ")) 

mod_tabl <- 
  moderation_model_list %>%
  purrr::pluck("Model")

for(i in seq_len(length(mod_tabl))) {print(mod_synth[i]); print(mod_tabl[[i]])}
```

### Med - just check

```{r med, cache=TRUE}
# find_med(df_scales)
# mediation_model_list

for(i in seq_len(length(mediation_model_list$MedEs))) {print(mediation_model_list$MedEs[i]); print(mediation_model_list$PathEs[[i]])}
```

### Odd stigma patterns

```{r, warning=FALSE, fig.height=6, fig.width=7}
ggplot(df_scales, aes(aware, agree, color = posit)) +
  geom_smooth(method = "loess", formula = y ~ x, se = TRUE, alpha = 0.1, color = "red", fill = "red") +
  geom_point() +
  scale_colour_distiller(palette = "Blues", direction = 1)

df_scales %>%
  mutate(posit_cat = cut(posit,
    breaks = c(5, 10, 20, 30, 40))
  ) %>%
  ggplot(aes(aware, agree, color = posit_cat)) +
  geom_point() -> plot_stigma1
plotly::ggplotly(plot_stigma1)

ggplot(df_scales, aes(posit, agree, color = aware)) +
  geom_smooth(method = "loess", formula = y ~ x, se = TRUE, alpha = 0.1, color = "red", fill = "red") +
  geom_point() +
  scale_colour_distiller(palette = "Blues", direction = 1)

df_scales %>%
  mutate(aware_cat = cut(posit,
    breaks = c(5, 10, 20, 30, 40))
  ) %>%
  ggplot(aes(posit, agree, color = aware_cat)) +
  geom_point() -> plot_stigma2
plotly::ggplotly(plot_stigma2)

coplot(agree ~ posit | aware, overlap = 0, data = df_scales,
  panel = function(x, y, ...) {
          points(x, y, ...)
          abline(lm(y ~ x), col = "red")}
)
```

### Partial correlations stigma (partial everything from everything)

```{r}
psych::lowerMat(psych::partial.r(df_scales[, c("agree", "aware", "posit")]))
```


### Interaction stigma

```{r}
mod_stigma_interac <- lm(agree ~ aware * posit, data = df_agree)
interactions::interact_plot(mod_stigma_interac, pred = posit, modx = aware)
# interactions::sim_slopes(mod_stigma_interac, pred = posit, modx = aware)
```

### Gender diff stigma

```{r}
ggstatsplot::ggbetweenstats(df_agree, x = sex, y = agree)
ggstatsplot::ggbetweenstats(df_agree, x = sex, y = aware)
ggstatsplot::ggbetweenstats(df_agree, x = sex, y = posit)
```

### Silly model that works smh (0 m, 1 fem)

```{r}
df_scales %>% 
  mutate(sex = as.numeric(as.factor(sex)) - 1) %>% 
  psych::mediate(posit ~ sex + aware:agree + (aware), data = .)

# psych::mediate(agree ~ posit + (aware), data = df_scales) # silly but works
# psych::mediate(agree ~ posit * aware, data = df_scales)
```

### Reg step - everything about stigma is wacky

```{r}
df_agree <- na.omit(df_scales[, c("agree", "sex", "age", "resid", "aware", "soc_supp", "posit")])
mod_agree <- lm(agree ~ sex + age + resid + aware + soc_supp, data = df_agree)
best_mod_agree <- step(mod_agree, scope = help_seek ~ .^2, direction = "both", data = mod_agree$model, trace = 0) # BIC with k = log(nrow(mod_agree$model))
summary(best_mod_agree)
```


```{r}
df_helpseek <- na.omit(df_scales[, c("help_seek", "sex", "age", "agree", "aware", "soc_supp", "agree", "posit")])
mod_helpseek <- lm(help_seek ~ sex + age + agree  + aware + soc_supp, data = df_helpseek)
best_mod_helpseek <- step(mod_helpseek, scope = help_seek ~ .^2, direction = "both", data = mod_helpseek$model, trace = 0) # BIC with k = log(nrow(mod_helpseek$model))
summary(best_mod_helpseek)


summary(lm(help_seek ~ sex + age * aware, data = df_scales)) 


```






<!-- Session Info and License -->

<br>

# Session Info
```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->
&nbsp;
<hr />
<p style="text-align: center;">A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a></p>
<p style="text-align: center;"><span style="color: #808080;"><em>claudiu.papasteri@gmail.com</em></span></p>
&nbsp;
