---
title: "<br> STAD - Demo and Imitation Metrics" 
subtitle: "Preliminary Analysis"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    # pdf_document: 
            # toc: true
            #  toc_depth: 2
            #  number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---


<!-- Setup -->


```{r setup, include=FALSE}
# kintr options
knitr::opts_chunk$set(
  comment = "#",
  collapse = TRUE,
  echo = TRUE, warning = FALSE, message = TRUE, cache = TRUE       # echo = False for github_document, but will be folded in html_notebook
)

# General R options and info
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation

# Load packages
if (!require("pacman")) install.packages("pacman")
packages <- c(
  "papaja",
  "tidyverse",      
  "psych",          
  "broom", "rstatix",
  "summarytools",            
  "ggplot2", "ggpubr", "scales",        
  "rio"
  # , ...
)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(char = packages)

# Themes for ggplot2 ploting (here used APA style)
theme_set(theme_apa())
```





<!-- Report -->

# Run demoimitMetrics_cleantable script

```{r}
script_folder <- "C:/Users/Mihai/Desktop/R Notebooks/notebooks/STAD-demoimitMetrics/STAD_behavioral_scrips" 
script_name <- "demoimitMetrics_to_cleantable.R"
source(file.path(script_folder, script_name))
```


# Data

## Info:
* Demo scores
    + 1st row for start 
    + 2nd row for flag

* Imitation scores
    + 1st row for start 
    + 2nd row for flag 
    + 3rd row = first object response by navigator (individual score)
    + 4th row = suggestion marker by observer (observer score)     
    + 5th row = 2nd object response by navigator (collaborative score)


```{r}
full_data_output %>%
      DT::datatable(                                  # excel downloadable  DT table
      extensions = 'Buttons',
      options = list(pageLength = 20,
                     scrollX = '500px', 
                     dom = 'Bfrtip', 
                     buttons = c('excel', "csv")))
```





<!-- Session Info and License -->

<br>

# Session Info
```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->
&nbsp;
<hr />
<p style="text-align: center;">A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a></p>
<p style="text-align: center;"><span style="color: #808080;"><em>claudiu.papasteri@gmail.com</em></span></p>
&nbsp;
