---
title: "<br> STAD - Demo and Imitation Metrics" 
subtitle: "Preliminary Analysis"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    # pdf_document: 
            # toc: true
            #  toc_depth: 2
            #  number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---


<!-- Setup -->


```{r setup, include=FALSE}
# kintr options
knitr::opts_chunk$set(
  comment = "#",
  collapse = TRUE,
  echo = TRUE, warning = FALSE, message = TRUE, cache = TRUE       # echo = False for github_document, but will be folded in html_notebook
)

# General R options and info
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation

# Load packages
if (!require("pacman")) install.packages("pacman")
packages <- c(
  "papaja",
  "tidyverse",      
  "psych",          
  "broom", "rstatix",
  "summarytools",            
  "ggplot2", "ggpubr", "scales",        
  "rio"
  # , ...
)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(char = packages)

# Themes for ggplot2 ploting (here used APA style)
theme_set(theme_apa())
```





<!-- Report -->

# Run demoimitMetrics_cleantable script

```{r}
script_folder <- "C:/Users/Mihai/Desktop/R Notebooks/notebooks/STAD-demoimitMetrics/STAD_behavioral_scrips" 
script_name <- "demoimitMetrics_to_cleantable_V.2.R"
source(file.path(script_folder, script_name))
```


```{r}
# Some additional tidying
vars_exclude <- c(
  # General    
  "InputY", "InputX", "xPos", "yPos", "zPos", "xRot", "yRot", "zRot", "wRot", "markerX", "markerY", "markerZ",
  # Demo
  "demoMetrics_playerPosition_x", "demoMetrics_playerPosition_y", "demoMetrics_playerPosition_z", "demoMetrics_markerPosition_x",  
  "demoMetrics_markerPosition_y", "demoMetrics_markerPosition_z", "demoMetrics_distanceFromMarker", "timeStamp_demo",
  # Imit
  "imitMetrics_playerPosition_x", "imitMetrics_playerPosition_y", "imitMetrics_playerPosition_z", "imitMetrics_markerPosition_x", 
  "imitMetrics_markerPosition_y", "imitMetrics_markerPosition_z", "imitMetrics_distanceFromMarker", "timeStamp_imit",
  # syncKey
  "syncKey"
)

full_data_output_clean2 <- 
  full_data_output_clean %>%
  dplyr::select(-all_of(vars_exclude))


full_data_output_clean2 <- 
  full_data_output_clean2 %>%
  dplyr::mutate(demoimitState = dplyr::case_when(newGameState_f %in% 5:11 ~ "Demo",
                                                 newGameState_f %in% 12:20 ~ "Imit",
                                                 TRUE ~ NA_character_)) %>%
  dplyr::mutate(playerType = dplyr::coalesce(demoMetrics_playerType, imitMetrics_playerType),
                markerType = dplyr::coalesce(demoMetrics_markerType, imitMetrics_markerType),
                score = dplyr::coalesce(demoMetrics_score, imitMetrics_score)) %>%
  dplyr::select(-c(demoMetrics_playerType, imitMetrics_playerType, demoMetrics_markerType, imitMetrics_markerType, demoMetrics_score, imitMetrics_score))

```


# Data

## Info:
* Demo scores
    + object response by navigator (individual score) 

* Imitation scores
    + 1st row for start (GameState 14)
    + 2nd row for flag (GameState 15)
    + 3rd row = first object response by navigator (individual score) (GameState 16)
    + 4th row = suggestion marker by observer (observer score) (GameState 17)       
    + 5th row = 2nd object response by navigator (collaborative score) (GameState 18)
    
* Variables:
    + id categorical - unique identifier
    + condition categorical - "social" or "bot"
    + order categorical - 1 or 2 the order of conditions

    + newGameState_f categorical - codes for GameStates (5-11 are Demo, 12-20 are Imit)
    + demoimitState categorical - "Demo" or "Imit" depending on state
    + playerType categorical - 1 or 2 - player that goes first
    + markerType categorical - codes for the object (see documentation), but it actually follows the the above Info (dependes on GameState)
    + score continuous - follows the the above Info (dependes on GameState)



```{r}
full_data_output_clean2 %>%
      DT::datatable(                                  # excel downloadable  DT table
      extensions = 'Buttons',
      options = list(pageLength = 20,
                     scrollX = '500px', 
                     dom = 'Bfrtip', 
                     buttons = c('excel', "csv")))
```





<!-- Session Info and License -->

<br>

# Session Info
```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->
&nbsp;
<hr />
<p style="text-align: center;">A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a></p>
<p style="text-align: center;"><span style="color: #808080;"><em>claudiu.papasteri@gmail.com</em></span></p>
&nbsp;
