---
title: "<br> STAD - Demo and Imitation Metrics for iEEG" 
subtitle: "Preliminary Analysis"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    # pdf_document: 
            # toc: true
            #  toc_depth: 2
            #  number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---

<!-- Setup -->

```{r setup, include=FALSE}
# kintr options
knitr::opts_chunk$set(
  comment = "#",
  collapse = TRUE,
  echo = TRUE, warning = FALSE, message = TRUE, cache = TRUE       # echo = False for github_document, but will be folded in html_notebook
)

options(dplyr.summarise.inform = FALSE)   # annoying summarize messages pass throught message=FALSE

# General R options and info
Sys.setenv(`_R_S3_METHOD_REGISTRATION_NOTE_OVERWRITES_` = "false") # suppress "S3 method overwritten" before loading packages
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation

# Load packages
if (!require("pacman")) install.packages("pacman")
packages <- c(
  "papaja",
  "tidyverse",      
  "psych",          
  "broom", "rstatix",
  "summarytools",            
  "ggplot2", "ggpubr", "scales", "splines", "cowplot", "ggstatsplot",        
  "rio"
  # , ...
)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(char = packages)

# Themes for ggplot2 ploting (here used APA style)
theme_set(theme_apa())
```

<!-- Report -->

# Run demoimitMetrics_cleantable script

```{r, message=FALSE, warning=FALSE}
script_folder <- "C:/Users/Mihai/Desktop/R Notebooks/notebooks/STAD-demoimitMetrics/Scripts" 
script_name <- "demoimitMetrics_to_cleantable_ieeg.R"
source(file.path(script_folder, script_name))
```

```{r}
full_data_output_clean <-
  full_data_output_clean %>%
  tidyr::separate(id, into = c("num_id", "code"), "(?<=[0-9])(?=[a-zA-Z])", remove = FALSE) %>%
  dplyr::mutate(id = as.factor(id),
                code = as.factor(code)
  )
```


# Data

## Info:

-   Demo scores

    -   object response by navigator (individual score) (GameState 9 =\> newGameState 10)

-   Imitation scores

    -   1st row for start (GameState 14 =\> newGameState 15)
    -   2nd row for flag (GameState 15 =\> newGameState 16)
    -   3rd row = first object response by navigator (individual score) (GameState 16 =\> newGameState 17)
    -   4th row = suggestion marker by observer (observer score) (GameState 17 =\> newGameState 18)
    -   5th row = 2nd object response by navigator (collaborative score) (GameState 18 =\> newGameState 19)

-   Variables:

    -   id categorical - unique identifier
    -   code categorical - IC = pacient / PIC = instructor
    -   condition categorical - "social" or "bot"
    -   order categorical - 1 or 2 the order of conditions
    -   who catergorical - 1 or 2 codes for who's recording it is (data only for current id is when: *who == playerType*)

    <!-- + newGameState_f categorical - codes for GameStates (5-11 are Demo, 12-20 are Imit) -->

    <!-- + demoimitState categorical - "Demo" or "Imit" depending on state -->

    -   newGameState_clean categorical - codes for GameStates (5-11 are Demo, 12-20 are Imit)
    -   demoimitState_clean categorical - "Demo" or "Imit" depending on state
    -   playerType categorical - 1 or 2 depending on GameState (should be used together with var *who*)
    -   markerType categorical - codes for the object (see documentation), but it actually follows the the above Info (dependes on GameState)
    -   score continuous - follows the the above Info (depends on GameState)

```{r}
full_data_output_clean %>%
  DT::datatable(                                  # excel downloadable  DT table
  extensions = 'Buttons',
  options = list(pageLength = 10,
                 scrollX = '500px', 
                 dom = 'Bfrtip', 
                 buttons = c('excel', "csv"))) %>%
  DT::formatStyle(names(full_data_output_clean),lineHeight = "60%")    # slimmer rows
```

# Preliminary Analyses

### Functions

```{r}
plot_growth_state_id <- function(data, cond, gamestate, time_lim = 20) {
  data %>%
  dplyr::filter(condition == cond, newGameState_clean == gamestate) %>%
  group_by(id) %>%
  dplyr::mutate(time = dplyr::row_number()) %>%
  dplyr::filter(time < time_lim) %>%  
    ggplot(aes(x = time, y = score)) +
    geom_line() +
    facet_wrap(~id) +
    ylim(0, 100) +
    scale_x_continuous(breaks = 1:14) +
    ggtitle(paste0("Condition: ", cond, ", ", "Game state: ", gamestate))
}

# e.g.
# full_data_output_clean %>%
#   dplyr::filter(condition == "bot", newGameState_clean == "10") %>%
#   group_by(id) %>%
#   dplyr::mutate(time = dplyr::row_number()) %>%
#   ggplot(aes(x = time, y = score)) +
#   geom_line() +
#   facet_wrap(~id)

plot_growth_state_id_by <- function(data, cond, col_by = c("order", "code"), gamestate, time_lim = 20) {
  data %>%
  dplyr::filter(condition == cond, newGameState_clean == gamestate) %>%
  group_by(id) %>%
  dplyr::mutate(time = dplyr::row_number(),
                order = as.factor(order),
                code = as.factor(code)) %>%
  dplyr::filter(time < time_lim) %>%  
    ggplot(aes(x = time, y = score)) +
    geom_line(aes_string(color = col_by)) +
    geom_point(aes_string(color = col_by)) +
    facet_wrap(~id) +
    ylim(0, 100) +
    scale_x_continuous(breaks = 1:14) +
    ggtitle(paste0("Condition: ", cond, ", ", "Game state: ", gamestate))
}




plot_growth_state_loess <- function(data, cond, gamestate, time_lim = 20) {
  data %>%
  dplyr::filter(condition == cond, newGameState_clean == gamestate) %>%
  group_by(id) %>%
  dplyr::mutate(time = dplyr::row_number()) %>%
  dplyr::filter(time < time_lim) %>%   
    ggplot(aes(x = time, y = score)) +
    geom_line(aes(color = as.factor(id)), alpha = .5) +
    geom_smooth(method = "loess", formula = "y ~ x", color = "red", fill = "red") +
    geom_smooth(method = "lm", formula = y ~ splines::bs(x, knots = seq(2 , 16, by = 2), degree = 1), 
                se = FALSE, color = "black", fill = "gray", alpha = 0.8) +
    ylim(0, 100) +
    scale_x_continuous(breaks = 1:14) +
    ggtitle(paste0("Condition: ", cond, ", ", "Game state: ", gamestate)) +
    labs(color = "id")  
}
  
# e.e.
# full_data_output_clean %>%
# dplyr::filter(condition == "bot", newGameState_clean == "10") %>%
# group_by(id) %>%
# dplyr::mutate(time = dplyr::row_number()) %>%
# ggplot(aes(x = time, y = score)) +
# geom_line(aes(color = as.factor(id)), alpha = .5) +
# geom_smooth(method = "loess", formula = "y ~ x")

plot_growth_state1017_id <- function(data, conds = c("social", "bot"), time_lim = 20) {
  data %>%
  dplyr::filter(condition %in% conds, newGameState_clean %in% c("10", "17")) %>%
  dplyr::mutate(newGameState_clean = as.factor(newGameState_clean)) %>%  
  dplyr::group_by(id, condition) %>%
  dplyr::mutate(time = dplyr::row_number()) %>%
  dplyr::filter(time < time_lim) %>% 
    ggplot(aes(x = time, y = score, color = condition)) +
    geom_line() +
    geom_point(aes(shape = newGameState_clean)) +
    facet_wrap(~id) +
    ylim(0, 100) +
    scale_x_continuous(breaks = 1:14) +
    ggtitle("Alternating GameState 10 and 17") + 
    theme(legend.position = "right")
}



my_ggwithinstats2 <- function(data, title = NULL, x, y, gamestate, time_lim = 20, outlier.label, xlab, ylab, 
                              outlier.tagging = FALSE, results.subtitle = TRUE, 
                              centrality.label.args = TRUE, point.path = TRUE,
                              type = "parametric", 
                              ...) {  # ... for limits and breaks
  x <- rlang::enquo(x)
  y <- rlang::enquo(y)
  outlier.label <- rlang::enquo(outlier.label)
  
  if(is.null(title)) {
    title <- paste0("Game state: ", gamestate)
  }
  
  data <-
    data %>%
    dplyr::select(!!outlier.label, !!x, !!y, newGameState_clean) %>%      # newGameState_clean is hardcoded here
    dplyr::filter(newGameState_clean == gamestate) %>%
    group_by(!!outlier.label, !!x) %>%
    dplyr::mutate(time = dplyr::row_number()) %>%
    dplyr::filter(time < time_lim) %>%   
    dplyr::summarise(mean_score = mean(!!y, na.rm = TRUE))
    
  if(centrality.label.args){
    centrality.label.args <- list(size = 3, nudge_x = 0.2, segment.linetype = 5, fill = "#FFF8E7")
  }else{
    centrality.label.args <- list(size = 0, nudge_x = 10, segment.linetype = 0, alpha = 0) # very hacky way of not showing label
  }
  
  data %>%
    ggstatsplot::ggwithinstats(
      x = !!x,
      y = mean_score,              # here we have the mean score for id, not !!y
      title = title,
      xlab = xlab,
      ylab = ylab,
      outlier.tagging = outlier.tagging,                    # whether outlines need to be tagged
      outlier.label = !!outlier.label,                      # variable to be used for tagging outliers
      outlier.coef = 2,
      pairwise.comparisons = TRUE,
      pairwise.display = "all",
      results.subtitle = results.subtitle,
      type = type,
      bf.message = FALSE, 
      p.adjust.method = "none",
      point.path = point.path,
      ggtheme = ggprism::theme_prism(),
      # package = "RColorBrewer",  # "ggsci",
      # palette = "Dark",         # "default_jco",
      violin.args = list(width = 0.9, alpha = 0.2, size = 1, color = "black"),
      centrality.plotting = TRUE,
      centrality.type = "parameteric",
      centrality.point.args = list(size = 5, color = "darkred"),
      centrality.label.args = centrality.label.args,
      ggplot.component = list(
        theme(
          plot.title = element_text(hjust = 0, size = 16),
          plot.subtitle = element_text(hjust = 0, size = 12), 
          plot.caption = element_text(hjust = 0, size = 12), 
          text = element_text(size = 14)
      ))
    ) + scale_colour_grey(start = 0.2, end = 0.2) +  # hacky way to change point color
    ylim(0, 100) +
    scale_y_continuous(...)
}

# e.g.
# my_ggwithinstats2(full_data_output_clean, x = condition, y = score, outlier.label = id, gamestate = 10,
#                   time_lim = 20, xlab = "Condition", ylab = "score")
                   
```

## Check balance

### All participants

```{r}
counts_id_condord <-
  full_data_output_clean %>%
  dplyr::count(id, condition, order)

counts_id_condord %>%      
  print(n = Inf)

counts_id_condord %>%
  dplyr::select(condition, order) %>%
  table() %>%
  knitr::kable(caption = "Order")
```

### Participants with both conditions

```{r}
ids_full_subj <-
  full_data_output_clean %>%
  group_by(id, condition) %>%
  summarise(count = n()) %>%
  dplyr::filter(n() > 1) %>%
  dplyr::pull(id) %>%
  unique()

full_data_output_clean %>%
  dplyr::filter(id %in% ids_full_subj) %>%
  dplyr::count(id, condition, order) %>%
  dplyr::select(condition, order) %>%
  table() %>%
  knitr::kable(caption = "Order")
```


## Individual growth (object not considered)

```{r, warning=FALSE, message=FALSE, fig.height=8, fig.width=10}
plot_growth_state_id_by(full_data_output_clean, "bot", "order", "10")  
plot_growth_state_id_by(full_data_output_clean, "social", "code", "10") %>% print() %>% suppressMessages()

plot_growth_state_id_by(full_data_output_clean, "bot", "order", "15")  
plot_growth_state_id_by(full_data_output_clean, "social", "code", "15") %>% print() %>% suppressMessages()

plot_growth_state_id_by(full_data_output_clean, "bot", "order", "16")  
plot_growth_state_id_by(full_data_output_clean, "social", "code", "16") %>% print() %>% suppressMessages()

plot_growth_state_id_by(full_data_output_clean, "bot", "order", "17")  
plot_growth_state_id_by(full_data_output_clean, "social", "code", "17") %>% print() %>% suppressMessages()

plot_growth_state_id_by(full_data_output_clean, "bot", "order", "18")  
plot_growth_state_id_by(full_data_output_clean, "social", "code", "18") %>% print() %>% suppressMessages()

plot_growth_state_id_by(full_data_output_clean, "bot", "order", "19")  
plot_growth_state_id_by(full_data_output_clean, "social", "code", "19") %>% print() %>% suppressMessages()

# plot_growth_state_id(full_data_output_clean, "bot", "19")
# plot_growth_state_id(full_data_output_clean, "social", "19")
```

## Individual growth (object not considered) - instructors excluded

Red = Loess

Black = Spline regression (1st degree polynomial), knots = every second time point

```{r, fig.height=8, fig.width=8}
full_data_output_clean_ic <-
  full_data_output_clean %>%
  dplyr::filter(code == "IC")

cowplot::plot_grid(
  plot_growth_state_loess(full_data_output_clean_ic, "bot", "10") + theme(legend.position="none"),
  plot_growth_state_loess(full_data_output_clean_ic, "social", "10") + theme(legend.position="none"),
  nrow = 2
)

cowplot::plot_grid(
  plot_growth_state_loess(full_data_output_clean_ic, "bot", "15") + theme(legend.position="none"),
  plot_growth_state_loess(full_data_output_clean_ic, "social", "15") + theme(legend.position="none"),  
  nrow = 2
)

cowplot::plot_grid(
  plot_growth_state_loess(full_data_output_clean_ic, "bot", "16") + theme(legend.position="none"),
  plot_growth_state_loess(full_data_output_clean_ic, "social", "16") + theme(legend.position="none"),  
  nrow = 2
)

cowplot::plot_grid(
  plot_growth_state_loess(full_data_output_clean_ic, "bot", "17") + theme(legend.position="none"),
  plot_growth_state_loess(full_data_output_clean_ic, "social", "17") + theme(legend.position="none"),  
  nrow = 2
)

cowplot::plot_grid(
  plot_growth_state_loess(full_data_output_clean_ic, "bot", "18") + theme(legend.position="none"),
  plot_growth_state_loess(full_data_output_clean_ic, "social", "18") + theme(legend.position="none"), 
  nrow = 2
)
  
cowplot::plot_grid(
  plot_growth_state_loess(full_data_output_clean_ic, "bot", "19") + theme(legend.position="none"),
  plot_growth_state_loess(full_data_output_clean_ic, "social", "19") + theme(legend.position="none"), 
  nrow = 2
)
```


## Alternating GameStates 10 and 17 for each participant by condition

### All participans

```{r, message=FALSE, warning=FALSE, fig.height=10, fig.width=12}
plot_growth_state1017_id(full_data_output_clean)
```

### Partcipants with both conditions

```{r, message=FALSE, warning=FALSE, fig.height=5, fig.width=11}
full_data_output_clean %>%
  dplyr::filter(id %in% ids_full_subj) %>%
  plot_growth_state1017_id()
```


### GameState 19, only first object, individual level average

Order is not accounted for

```{r, fig.height=17, fig.width=7, message=FALSE, warning=FALSE}
plot_gs19_first <- 
  full_data_output_clean %>%
  dplyr::select(id, condition, score, newGameState_clean, markerType) %>%      
  dplyr::filter(newGameState_clean == "19") %>%
  dplyr::group_by(id, condition) %>%  
  dplyr::mutate(first_marker = dplyr::if_else(markerType == dplyr::first(markerType), "yes", "no")) %>%  
  dplyr::filter(first_marker == "yes") %>%
  dplyr::mutate(time = dplyr::row_number()) %>%
    ggplot(aes(x = time, y = score)) +
    geom_line() +
    geom_point() +
    # facet_wrap(score ~ condition, strip.position = "top") +
    # facet_grid(condition ~ id) +    
    facet_grid(rows = vars(id), cols = vars(condition)) + 
    ylim(0, 100) +
    scale_x_continuous(breaks = 1:16) +
    ggtitle(paste0("Game state: ", "19")) +
    theme_bw() 

suppressMessages(print(plot_gs19_first))
```

```{r, fig.height=7, fig.width=7}
full_data_output_clean %>%
dplyr::select(id, condition, score, newGameState_clean, markerType) %>%      
dplyr::filter(newGameState_clean == "19") %>%
dplyr::group_by(id, condition) %>%  
dplyr::mutate(first_marker = dplyr::if_else(markerType == dplyr::first(markerType), "yes", "no")) %>%  
dplyr::filter(first_marker == "yes") %>%
dplyr::summarise(mean_score = mean(score, na.rm = TRUE)) %>%
  ggstatsplot::ggwithinstats(
    x = condition,
    y = mean_score,
    outlier.tagging = TRUE,                   
    outlier.label = id, 
    title = "GameState: 19"
  )
```




<!-- Session Info and License -->

<br>

# Session Info

```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->

 

<hr />

<p style="text-align: center;">

A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a>

</p>

<p style="text-align: center;">

<em>[claudiu.papasteri\@gmail.com](mailto:claudiu.papasteri@gmail.com){.email}</em>

</p>

 
