---
title: "<br> STAD - Demo and Imitation Metrics" 
subtitle: "Preliminary Analysis"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    # pdf_document: 
            # toc: true
            #  toc_depth: 2
            #  number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---


<!-- Setup -->


```{r setup, include=FALSE}
# kintr options
knitr::opts_chunk$set(
  comment = "#",
  collapse = TRUE,
  echo = TRUE, warning = FALSE, message = TRUE, cache = TRUE       # echo = False for github_document, but will be folded in html_notebook
)

# General R options and info
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation

# Load packages
if (!require("pacman")) install.packages("pacman")
packages <- c(
  "papaja",
  "tidyverse",      
  "psych",          
  "broom", "rstatix",
  "summarytools",            
  "ggplot2", "ggpubr", "scales",        
  "rio"
  # , ...
)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(char = packages)

# Themes for ggplot2 ploting (here used APA style)
theme_set(theme_apa())
```





<!-- Report -->

# Run demoimitMetrics_cleantable script

```{r}
script_folder <- "C:/Users/Mihai/Desktop/R Notebooks/notebooks/STAD-demoimitMetrics/STAD_behavioral_scrips" 
script_name <- "demoimitMetrics_to_cleantable_V.2.R"
source(file.path(script_folder, script_name))
```


```{r}
# Some additional tidying
vars_exclude <- c(
  # General    
  "InputY", "InputX", "xPos", "yPos", "zPos", "xRot", "yRot", "zRot", "wRot", "markerX", "markerY", "markerZ",
  # Demo
  "demoMetrics_playerPosition_x", "demoMetrics_playerPosition_y", "demoMetrics_playerPosition_z", "demoMetrics_markerPosition_x",  
  "demoMetrics_markerPosition_y", "demoMetrics_markerPosition_z", "demoMetrics_distanceFromMarker", "timeStamp_demo",
  # Imit
  "imitMetrics_playerPosition_x", "imitMetrics_playerPosition_y", "imitMetrics_playerPosition_z", "imitMetrics_markerPosition_x", 
  "imitMetrics_markerPosition_y", "imitMetrics_markerPosition_z", "imitMetrics_distanceFromMarker", "timeStamp_imit",
  # syncKey
  "syncKey"
)

full_data_output_clean2 <- 
  full_data_output_clean %>%
  dplyr::select(-all_of(vars_exclude))


full_data_output_clean2 <- 
  full_data_output_clean2 %>%
  dplyr::mutate(demoimitState = dplyr::case_when(newGameState_f %in% 5:11 ~ "Demo",
                                                 newGameState_f %in% 12:20 ~ "Imit",
                                                 TRUE ~ NA_character_)) %>%
  dplyr::mutate(playerType = dplyr::coalesce(demoMetrics_playerType, imitMetrics_playerType),
                markerType = dplyr::coalesce(demoMetrics_markerType, imitMetrics_markerType),
                score = dplyr::coalesce(demoMetrics_score, imitMetrics_score)) %>%
  dplyr::mutate(who = dplyr::case_when(stringr::str_detect(fisier_obtinut, "PLAYER_1") ~ 1L,
                                       stringr::str_detect(fisier_obtinut, "PLAYER_2") ~ 2L,
                                       TRUE ~ NA_integer_)) %>%
  dplyr::select(-c(demoMetrics_playerType, imitMetrics_playerType, demoMetrics_markerType, imitMetrics_markerType, demoMetrics_score, imitMetrics_score))

```


# Data

## Info:
* Demo scores
    + object response by navigator (individual score) 

* Imitation scores
    + 1st row for start (GameState 14)
    + 2nd row for flag (GameState 15)
    + 3rd row = first object response by navigator (individual score) (GameState 16)
    + 4th row = suggestion marker by observer (observer score) (GameState 17)       
    + 5th row = 2nd object response by navigator (collaborative score) (GameState 18)
    
* Variables:
    + id categorical - unique identifier
    + condition categorical - "social" or "bot"
    + order categorical - 1 or 2 the order of conditions
    + who catergorical - 1 or 2 codes for who's recording it is (data only for current id is when: _who == playerType_)

    + newGameState_f categorical - codes for GameStates (5-11 are Demo, 12-20 are Imit)
    + demoimitState categorical - "Demo" or "Imit" depending on state
    + playerType categorical - 1 or 2 depending on GameState (should be used together with var _who_)
    + markerType categorical - codes for the object (see documentation), but it actually follows the the above Info (dependes on GameState)
    + score continuous - follows the the above Info (dependes on GameState)



```{r}
full_data_output_clean2 %>%
      DT::datatable(                                  # excel downloadable  DT table
      extensions = 'Buttons',
      options = list(pageLength = 20,
                     scrollX = '500px', 
                     dom = 'Bfrtip', 
                     buttons = c('excel', "csv")))
```



## Insights for Sabin on Player1/Player2 recordings
Some GameStates (e.g. 10 Demo and 17 Imit) with corresponding Metrics are logged only for one of the subject within social condition.
The GameStates that are logged for both participants have identical data (including Metrics).

```{r}
id3_soc <- full_data_output_clean2 %>%
  dplyr::filter(id == "ID3", conditie == "SOCIAL")

id4_soc <- full_data_output_clean2 %>%
  dplyr::filter(id == "ID4", conditie == "SOCIAL")

# rio::export(id3_soc, "id3_soc.xlsx")
# rio::export(id4_soc, "id4_soc.xlsx")
```




<!-- Session Info and License -->

<br>

# Session Info
```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->
&nbsp;
<hr />
<p style="text-align: center;">A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a></p>
<p style="text-align: center;"><span style="color: #808080;"><em>claudiu.papasteri@gmail.com</em></span></p>
&nbsp;
