---
title: "<br> STAD - Demo and Imitation Metrics" 
subtitle: "Test Two Elderly"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    # pdf_document: 
            # toc: true
            #  toc_depth: 2
            #  number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---

<!-- Setup -->

```{r setup, include=FALSE}
# kintr options
knitr::opts_chunk$set(
  comment = "#",
  collapse = TRUE,
  echo = TRUE, warning = FALSE, message = TRUE, cache = TRUE       # echo = False for github_document, but will be folded in html_notebook
)

options(dplyr.summarise.inform = FALSE)   # annoying summarize messages pass throught message=FALSE

# General R options and info
Sys.setenv(`_R_S3_METHOD_REGISTRATION_NOTE_OVERWRITES_` = "false") # suppress "S3 method overwritten" before loading packages
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation

# Load packages
if (!require("pacman")) install.packages("pacman")
packages <- c(
  "papaja",
  "tidyverse",      
  "psych",          
  "broom", "rstatix",
  "summarytools",            
  "ggplot2", "ggpubr", "scales", "splines", "cowplot", "ggstatsplot",        
  "rio"
  # , ...
)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(char = packages)

# Themes for ggplot2 ploting (here used APA style)
theme_set(theme_apa())
```

<!-- Report -->

# Run demoimitMetrics_cleantable script

```{r, message=FALSE, warning=FALSE}
folder <- "C:/Users/Mihai/Desktop/R Notebooks/notebooks/STAD-demoimitMetrics"
setwd(folder)


########################################################

# Read clean table
sessions_clean_data <- readRDS("sessions_clean2batrani.RDS")

# Define function
list_to_nested <- function(list, group_var){
  list %>%
    do.call(dplyr::bind_rows, .) %>%
    dplyr::group_by( {{ group_var }} ) %>%
    tidyr::nest()
}

# Lists of recordings to nested data frames
sessions_clean_data_df <- list_to_nested(sessions_clean_data, file)

sessions_clean_data_df <-
  sessions_clean_data_df %>%
  dplyr::ungroup() %>%       # careful, the df is already grouped
  dplyr::mutate(id = dplyr::row_number())

full_data_output <- sessions_clean_data_df %>%
  dplyr::relocate(id) %>%
  tidyr::unnest(data)


# Some additional tidying
vars_exclude <- c(
  # General    
  "InputY", "InputX", "xPos", "yPos", "zPos", "xRot", "yRot", "zRot", "wRot", "markerX", "markerY", "markerZ",
  # Demo
  "demoMetrics_playerPosition_x", "demoMetrics_playerPosition_y", "demoMetrics_playerPosition_z", "demoMetrics_markerPosition_x",  
  "demoMetrics_markerPosition_y", "demoMetrics_markerPosition_z", "demoMetrics_distanceFromMarker", 
  # Imit
  "imitMetrics_playerPosition_x", "imitMetrics_playerPosition_y", "imitMetrics_playerPosition_z", "imitMetrics_markerPosition_x", 
  "imitMetrics_markerPosition_y", "imitMetrics_markerPosition_z", "imitMetrics_distanceFromMarker", 
  # syncKey
  "syncKey"
)

full_data_output_clean <- 
  full_data_output %>%
  dplyr::select(-any_of(vars_exclude))


full_data_output_clean <- 
  full_data_output_clean %>%
  dplyr::mutate(demoimitState = dplyr::case_when(newGameState_f %in% 5:11 ~ "Demo",
                                                 newGameState_f %in% 12:20 ~ "Imit",
                                                 TRUE ~ NA_character_)) %>%
  dplyr::mutate(timeStamp_demoimit = dplyr::coalesce(timeStamp_demo, timeStamp_imit), 
                playerType = dplyr::coalesce(demoMetrics_playerType, imitMetrics_playerType),
                markerType = dplyr::coalesce(demoMetrics_markerType, imitMetrics_markerType),
                score = dplyr::coalesce(demoMetrics_score, imitMetrics_score)) %>% 
  dplyr::mutate(who = dplyr::case_when(stringr::str_detect(file, "PLAYER_1") ~ 1L,     # changes output_file_clean to file
                                       stringr::str_detect(file, "PLAYER_2") ~ 2L,   
                                       TRUE ~ NA_integer_)) %>%
  dplyr::select(-c(demoMetrics_playerType, imitMetrics_playerType, demoMetrics_markerType, imitMetrics_markerType, demoMetrics_score, imitMetrics_score,
                   timeStamp_demo, timeStamp_imit))


# Keep only data from the actual player (where playerType == who)
full_data_output_clean <-
  full_data_output_clean %>%
  dplyr::filter(playerType == who)


# Exclude multiple timpeStamp_demoimit per timeStamp match (only adjusting tolerance will lose data as matches are not exact)
full_data_output_clean <-
  full_data_output_clean %>%
  dplyr::mutate(timeStamp_diff = abs(timeStamp - timeStamp_demoimit)) %>%
  dplyr::group_by(id, timeStamp_demoimit) %>%
  dplyr::slice_min(timeStamp_diff) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(id, timeStamp) %>%
  dplyr::slice_min(timeStamp_diff) %>%
  dplyr::ungroup()

# Make newGameState_clean --- a bit hacky 
full_data_output_clean <-
  full_data_output_clean %>%
  dplyr::mutate(
    newGameState_clean = 
      dplyr::case_when(newGameState_f == "9" ~ 10L,             # is 9 or 14 when it should be 10 or 15
                       newGameState_f == "14" ~ 15L,
                       newGameState_f %in% as.character(c(10, 15:19)) ~ as.integer(newGameState_f),
                       TRUE ~ NA_integer_
      ),
    newGameState_clean =                                 # some matched the previous frame so GameStates repeat
      dplyr::if_else(newGameState_clean == dplyr::lag(newGameState_clean) & !is.na(dplyr::lag(newGameState_clean)), 
                     newGameState_clean + 1L, 
                     newGameState_clean
     ),
    newGameState_clean =                                 # GameState 10 following another 10 now became 11
      dplyr::if_else(newGameState_clean == 11L, 10L, newGameState_clean)
  ) %>%                                          # !CAREFUL columns computed based on newGameState_f like demoimitState now may be wrong
  dplyr::mutate(demoimitState_clean = dplyr::case_when(newGameState_clean %in% 5:11 ~ "Demo",
                                                       newGameState_clean %in% 12:20 ~ "Imit",
                                                       TRUE ~ NA_character_))

# Check GameStates
check_df <-
  full_data_output_clean %>%
  dplyr::group_by(id) %>%
  dplyr::mutate(grp = as.integer(gl(n(), 6, n()))) %>%    # group every 6 rows
  dplyr::group_by(id, grp) %>%
  dplyr::summarise(pattern = paste0(newGameState_f, collapse = " "),
                   pattern_clean = paste0(newGameState_clean, collapse = " "))
```

## Check GamesStates

```{r}
check_df
```


# Data

```{r}
full_data_output_clean %>%
  DT::datatable(                                  # excel downloadable  DT table
  extensions = 'Buttons',
  options = list(pageLength = 5,
                 scrollX = '500px', 
                 dom = 'Bfrtip', 
                 buttons = c('excel', "csv"))) %>%
  DT::formatStyle(names(full_data_output_clean),lineHeight = "60%")    # slimmer rows
```

# Preliminary Analyses

### Functions

```{r}
plot_growth_state_id <- function(data, gamestate, time_lim = 20) {
  data %>%
  dplyr::filter(newGameState_clean == gamestate) %>%
  group_by(id) %>%
  dplyr::mutate(time = dplyr::row_number()) %>%
  dplyr::filter(time < time_lim) %>%  
    ggplot(aes(x = time, y = score)) +
    geom_line() +
    facet_wrap(~id) +
    ylim(0, 100) +
    scale_x_continuous(breaks = 1:14) +
    ggtitle(paste0("Game state: ", gamestate))
}


plot_growth_state_loess <- function(data, gamestate, time_lim = 20) {
  data %>%
  dplyr::filter(newGameState_clean == gamestate) %>%
  group_by(id) %>%
  dplyr::mutate(time = dplyr::row_number()) %>%
  dplyr::filter(time < time_lim) %>%   
    ggplot(aes(x = time, y = score)) +
    geom_line(aes(color = as.factor(id)), alpha = .5) +
    geom_smooth(method = "loess", formula = "y ~ x", color = "red", fill = NA) +
    # geom_smooth(method = "lm", formula = y ~ splines::bs(x, knots = seq(2 , 16, by = 2), degree = 1), 
    #             se = FALSE, color = "black", fill = "gray", alpha = 0.8) +
    # tidyquant::geom_ma(ma_fun = SMA, n = 1, color = "black") +
    stat_summary(fun = mean, geom = "line", colour = "black", lty = "dashed") +
    ylim(0, 100) +
    scale_x_continuous(breaks = 1:14) +
    ggtitle(paste0("Game state: ", gamestate)) +
    labs(color = "id")  
}

```


## Individual growth (object not considered)

Notes:

1.  Variability is the norm

2.  Trend is not easily discernible

```{r, fig.height=6, fig.width=8}
plot_growth_state_id(full_data_output_clean, "10")

plot_growth_state_id(full_data_output_clean, "15")
plot_growth_state_id(full_data_output_clean, "16")
plot_growth_state_id(full_data_output_clean, "17")
plot_growth_state_id(full_data_output_clean, "18")
plot_growth_state_id(full_data_output_clean, "19")
```

## Individual growth (object not considered)

Red = Loess
Black dashed = Simple Mean

```{r, fig.height=6, fig.width=7}
plot_growth_state_loess(full_data_output_clean, "10") + theme(legend.position = "none")

plot_growth_state_loess(full_data_output_clean, "15") + theme(legend.position = "none")
plot_growth_state_loess(full_data_output_clean, "16") + theme(legend.position = "none")
plot_growth_state_loess(full_data_output_clean, "17") + theme(legend.position = "none")
plot_growth_state_loess(full_data_output_clean, "18") + theme(legend.position = "none")
plot_growth_state_loess(full_data_output_clean, "19") + theme(legend.position = "none")
```


## Alternating GameStates 10 and 17 for each participant by condition


```{r, message=FALSE, warning=FALSE, fig.height=6, fig.width=10}
full_data_output_clean %>%
  dplyr::filter(newGameState_clean %in% c("10", "17")) %>%
  dplyr::mutate(newGameState_clean = as.factor(newGameState_clean)) %>%  
  dplyr::group_by(id) %>%
  dplyr::mutate(time = dplyr::row_number()) %>%
    ggplot(aes(x = time, y = score)) +
    geom_line() +
    geom_point(aes(shape = newGameState_clean)) +
    facet_wrap(~id) +
    ylim(0, 100) +
    scale_x_continuous(breaks = 1:14) +
    ggtitle("Alternating GameState 10 and 17") + 
    theme(legend.position = "right")
```







<!-- Session Info and License -->

<br>

# Session Info

```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->

 

<hr />

<p style="text-align: center;">

A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a>

</p>

<p style="text-align: center;">

<em>[claudiu.papasteri\@gmail.com](mailto:claudiu.papasteri@gmail.com){.email}</em>

</p>

 
