---
title: "<br> O.4 - UCL Poster" 
subtitle: "Preliminary Report for Unice - 3 Pilot Participants"
author: "<br> Claudiu Papasteri"
date: "`r format(Sys.time(), '%d %m %Y')`"
output: 
    html_notebook:
            code_folding: hide
            toc: true
            toc_depth: 2
            number_sections: true
            theme: spacelab
            highlight: tango
            font-family: Arial
            fig_width: 10
            fig_height: 9
    pdf_document: 
            toc: true
            toc_depth: 2
            number_sections: true
            # fontsize: 11pt
            # geometry: margin=1in
            # fig_width: 7
            # fig_height: 6
            # fig_caption: true
    # github_document: 
            # toc: true
            # toc_depth: 2
            # html_preview: false
            # fig_width: 5
            # fig_height: 5
            # dev: jpeg
---


<!-- Setup -->


```{r setup, include=FALSE}
# kintr options
knitr::opts_chunk$set(
  comment = "#",
  collapse = TRUE,
  echo = TRUE, warning = TRUE, message = TRUE, cache = TRUE       # echo = False for github_document, but will be folded in html_notebook
)

# General R options and info
set.seed(111)               # in case we use randomized procedures       
options(scipen = 999)       # positive values bias towards fixed and negative towards scientific notation

# Load packages
if (!require("pacman")) install.packages("pacman")
packages <- c(
  "tidyverse",      # best thing that happend to me
  "psych",          # general purpose toolbox for personality, psychometric theory and experimental psychology
  "papaja",         # for APA style
  "broom",          # for tidy modelling
  "ggplot2",        # best plots
  "ggpubr",         # ggplot2 to publication quality
  "DT",             # nice searchable and downloadable tables
  "summarytools",
  "plyr", 
  "stringr"
  # , ...
)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(char = packages)

# Themes for ggplot2 ploting (here used APA style)
theme_set(theme_apa())
```

```{r working_directory, include = FALSE}
### O.4 R code - Unice and Retatate
### R code for sorting, integrating and analyses 
# Task output files: 
# ID, experimental condition ("oglinda" / "ecran"), condition ("instructor", "solo"), type of task ("unic", "repetat")
wd <- "C:/Users/Mihai/Desktop/EEG_O.4c_1/O.4c - Poster"
setwd(wd)
```


<!-- Report -->


# Arrange folders, sort files, read and merge

## Create folders by conditions, copy files to them

```{r makedir_sortfiles, eval=FALSE}
# !!!!EVAL = FALSE
##################### Read file names ##################################################################################
file_names <- dir(pattern = "\\.xls$")
## if above isn't good enough try the following:
# file_names <- list.files(wd)
# file_names <- sop_files[!file.info(sop_files)$isdir]   # exclude directories
# file_names <- sop_files[grep(".xls", sop_files, fixed = TRUE)]


##################### Create folders with Condition names ###############################################################
# this part of script may be re-run if files from wd are updated
dir_names <- c("Unic_CTRL_Instr", "Unic_CTRL_Solo", "Unic_OGL_Instr", "Unic_OGL_Solo",
              "Repetat_CTRL_Instr", "Repetat_CTRL_Solo", "Repetat_OGL_Instr", "Repetat_OGL_Solo")
             
for(dir in dir_names){
  if(!dir.exists(file.path(wd, dir)))
  dir.create(file.path(wd, dir), showWarnings = FALSE)
}


##################### Use file names to sort them to folders ############################################################
sort_files_to_dirs <- function(wd, pattern, dir) {
  check_pattern <- outer(file_names, pattern, stringr::str_detect)               # if all TRUE bye row then it has full pattern
  index <- which(apply(check_pattern, 1, function(x) all(x==TRUE)))              # get index of file_names where all are TRUE
  sorted_files <- file_names[index]                                              # get names of files from indexes
  
  for(files in sorted_files) {                                                   # copy the files to corresponding folder
    file.copy(from = file.path(wd, files), to = file.path(wd, dir))
  }  
}

sort_files_to_dirs(wd = wd, pattern = c("unic", "ecran", "instructor"), dir = "Unic_CTRL_Instr")
sort_files_to_dirs(wd = wd, pattern = c("unic", "ecran", "solo"), dir = "Unic_CTRL_Solo")
sort_files_to_dirs(wd = wd, pattern = c("unic", "oglinda", "instructor"), dir = "Unic_OGL_Instr")
sort_files_to_dirs(wd = wd, pattern = c("unic", "oglinda", "solo"), dir = "Unic_OGL_Solo")
```


## Read Pilot Data (these are on VAS)
```{r pilot_data, hide=TRUE}
wd <- "C:/Users/Mihai/Desktop/EEG_O.4c_1/O.4c - Poster/Date Pilot"
setwd(wd)
folders <- list.files(wd)
folders <- folders[file.info(folders)$isdir]   # luam doar folderele
datasetnames <- NULL

for (i in 1:length(folders)) {
  datasetname <- folders[i]
  datasetnames <- c(datasetnames, datasetname)
  current_dir <- setwd(file.path(wd, folders[i]))
  print(paste0("current_dir: ", current_dir))
  
  paths <- dir(pattern = "\\.xls$")
  names(paths) <- basename(paths)

  assign( paste(datasetname), plyr::ldply(paths, rio::import) )
}

setwd(wd)

## Function for Pilot Data processing
process_pilot_data <- function(df){
  df_modif <-
    df %>%
    mutate(MarkerStimuli = case_when(`Stimuli order` < 36 ~ 11,                  # Pilot data was correcte due to stimulus ordering problems
                                     `Stimuli order` >=36 & `Stimuli order` <= 70 ~ 21,
                                     `Stimuli order` > 70 ~ 31,
                                     TRUE                 ~ as.numeric(NA))) %>%   
    mutate(`Stimulus type` = case_when(MarkerStimuli %in% c(11, 12) ~ "negativ",           # Left the old coding also altough we have only 11,21,31
                                       MarkerStimuli %in% c(21, 22) ~ "neutru",
                                       MarkerStimuli %in% c(31, 32) ~ "pozitiv",
                                       TRUE                         ~ as.character(NA))) %>%
    filter(`Stimulus type` != "pozitiv")                               # exclude positive stimuly because only 1 subject has them
  
  df <- deparse(substitute(df))
  assign(df, df_modif, envir = globalenv())
}

## Process Pilot Data
process_pilot_data(Pilot_Unic_CTRL_Instr)
process_pilot_data(Pilot_Unic_CTRL_Solo)
process_pilot_data(Pilot_Unic_OGL_Instr)
process_pilot_data(Pilot_Unic_OGL_Solo)

## Now we work only with Pilot Data
Unic_CTRL_Instr <- Pilot_Unic_CTRL_Instr
Unic_CTRL_Solo <- Pilot_Unic_CTRL_Solo
Unic_OGL_Instr <- Pilot_Unic_OGL_Instr
Unic_OGL_Solo <- Pilot_Unic_OGL_Solo
```


## Cleaning the data

```{r clean_data, hide=TRUE}
#################################### Data Cleaning #####################################################################
# Check if ids have > 1 row of data (empty .xls have only 1 row)
# Careful! This function modfies the datasets in the global envinronment
delete_empty_id <- function(df){
  list_empty_id <- 
    df %>%
    dplyr::group_by(.id) %>%
    dplyr::summarise(row_count = n()) %>%
    dplyr::rename("empty_id" = .id) %>%
    mutate(delete_id = if_else(row_count < 3, TRUE, FALSE)) %>%
    filter(delete_id == TRUE)
  
  df_modif <- 
    df %>%
    filter(!.id %in% list_empty_id$empty_id)
  
  if(!identical(df, df_modif)){
    df <- deparse(substitute(df))
    cat("Deleting from ", print(as.name(df))); print(list_empty_id)                    # print out which ids are deleted from which dataset
    assign(df, df_modif, envir = globalenv())                                          # assign modified df to original dataset from Global
  }else cat("No empty datasets. Nothing to delete")
}

# Apply function to all datasets (tricky to do in for loop because of super assignment)
delete_empty_id(Unic_CTRL_Instr)
delete_empty_id(Unic_CTRL_Solo)
delete_empty_id(Unic_OGL_Instr)
delete_empty_id(Unic_OGL_Solo)
```


## Exclude VAS_Resp based on RT outliers

```{r nooutlier_data, eval=FALSE}
# !!!!EVAL = FALSE
############################### Exclude Outliers based on RT (by subject and stimulus type) #######################################
## DONT RUN (unless it is needed) ----> eval=FALSE
# Exclude RT outliers (=- 2SD) - instead of simple filter, makeing them NA  is better for paired comparison
remove_outliers <- function(df) {
  df_modif <-
    df %>%
    dplyr::group_by(.id, `Stimulus type`) %>%                  # we could have done before:  dplyr::rename("Stim_type" = `Stimulus type`) 
    mutate(VAS_Resp = if_else(abs(VAS_RT - mean(VAS_RT, na.rm=TRUE)) > 2*sd(VAS_RT, na.rm=TRUE), as.numeric(NA), VAS_Resp))
  
  if(!identical(df, df_modif)){
    df <- deparse(substitute(df))
    cat("Deleting outliers from ", print(as.name(df)));                               # print out datasets which have been modified
    assign(df, df_modif, envir = globalenv())                                          # assign modified df to original dataset from Global
  }else cat("No outlier")
}

remove_outliers(Unic_CTRL_Instr)
remove_outliers(Unic_CTRL_Solo)
remove_outliers(Unic_OGL_Instr)
remove_outliers(Unic_OGL_Solo)
```


## Test if datasets have same columns

```{r test_cols}
unic_df_obj <- mget(c("Unic_CTRL_Instr", "Unic_CTRL_Solo", "Unic_OGL_Instr", "Unic_OGL_Solo"))
unic_df_obj <-lapply(unic_df_obj, colnames)
outer(unic_df_obj, unic_df_obj, Vectorize(identical))                           # if all are TRUE, all df have same columns
```

<br>
<br>


# Analysis - UNICE

## Descriptives

```{r desc_unice}
##########################################################################################################################
#################################### Analyses - UNICE ####################################################################
## Descriptives by condition dataset
descriptive_func <- function(df, Stim_type, By_ID = FALSE){
  df_name <- deparse(substitute(df))
  suppressWarnings({                                                                # if all NAs in VAS_Resp, NaNs and Infs will be produced
    df_modif <- 
      df %>%
      dplyr::rename("ID" = .id) %>%
      select_all(~gsub("\\s+|\\.", "_", .)) %>%                                     # replaces blancks with "_" in colnames 
      filter(Stimulus_type == Stim_type)                                            # filter by stimulus type
      
    if(isTRUE(By_ID)){                                                              # if true group by id, if not return descriptives for all ids
      by_id_text <- " by subject"
      df_modif %>%
      dplyr::group_by(ID) %>%
      tidystats::describe_data(VAS_Resp, VAS_RT, na.rm = TRUE) %>%
        knitr::kable(caption = paste(as.name(df_name), " ", Stim_type, by_id_text), format = "pandoc", digits = 2)
    }else{ 
      by_id_text <- " all subjects"
      df_modif %>%
      ungroup() %>%  
      tidystats::describe_data(VAS_Resp, VAS_RT, na.rm = TRUE) %>%
        knitr::kable(caption = paste(as.name(df_name), " ", Stim_type, by_id_text), format = "pandoc", digits = 2)
    }
  })
}  


descriptive_func(df = Unic_CTRL_Instr, Stim_type = "negativ", By_ID = FALSE)           # Negative - General
descriptive_func(df = Unic_CTRL_Solo, Stim_type = "negativ", By_ID = FALSE)
descriptive_func(df = Unic_OGL_Instr, Stim_type = "negativ", By_ID = FALSE)
descriptive_func(df = Unic_OGL_Solo, Stim_type = "negativ", By_ID = FALSE)

descriptive_func(df = Unic_CTRL_Instr, Stim_type = "negativ", By_ID = TRUE)            # Negative - by id
descriptive_func(df = Unic_CTRL_Solo, Stim_type = "negativ", By_ID = TRUE)
descriptive_func(df = Unic_OGL_Instr, Stim_type = "negativ", By_ID = TRUE)
descriptive_func(df = Unic_OGL_Solo, Stim_type = "negativ", By_ID = TRUE)

descriptive_func(df = Unic_CTRL_Instr, Stim_type = "neutru", By_ID = FALSE)           # Neutral - General
descriptive_func(df = Unic_CTRL_Solo, Stim_type = "neutru", By_ID = FALSE)
descriptive_func(df = Unic_OGL_Instr, Stim_type = "neutru", By_ID = FALSE)
descriptive_func(df = Unic_OGL_Solo, Stim_type = "neutru", By_ID = FALSE)

descriptive_func(df = Unic_CTRL_Instr, Stim_type = "neutru", By_ID = TRUE)            # Neutral - by id
descriptive_func(df = Unic_CTRL_Solo, Stim_type = "neutru", By_ID = TRUE)
descriptive_func(df = Unic_OGL_Instr, Stim_type = "neutru", By_ID = TRUE)
descriptive_func(df = Unic_OGL_Solo, Stim_type = "neutru", By_ID = TRUE)
```


## Merge

```{r merged_unice_data, hide=TRUE}
############################## Merge condition dataset ############################################################
# Must first rename .id to ID in oder to have .id for df names
ID_rename <- function(df){
  if(".id" %in% colnames(df)) {
    df_modif <- 
      df %>%
      dplyr::rename("ID" = .id)
    df <- deparse(substitute(df))
    cat("Changed .id to ID for: ", as.name(df))
    assign(df, df_modif, envir = globalenv())
  }  
}

ID_rename(Unic_CTRL_Instr)
ID_rename(Unic_CTRL_Solo)
ID_rename(Unic_OGL_Instr)
ID_rename(Unic_OGL_Solo)

# Merge into one df
list_df_merge <- list(Unic_CTRL_Instr, Unic_CTRL_Solo, Unic_OGL_Instr, Unic_OGL_Solo)
names(list_df_merge) <- c("Unic_CTRL_Instr", "Unic_CTRL_Solo", "Unic_OGL_Instr", "Unic_OGL_Solo")
Unic_merged <- plyr::ldply(list_df_merge, data.frame)                    # also works for this job bind_rows(list_df_merge, .id = "column_label")
```


## Analyses on merged (Anova & post-hoc)

```{r anova_unice, results='asis'}
############################## Analyses on Merged ################################################################
## Just a Test 
  # Unic_merged_spread_Neg <- 
  #   Unic_merged %>%
  #   filter(!is.na(VAS_Resp)) %>%                                           # some files had only NA on VAS_Resp and VAS_RT
  #   select(.id, ID, Subj_id, 
  #          Stimuli.order, MarkerStimuli, Stimulus.type, 
  #          VAS_Resp, VAS_RT) %>%
  #   filter(Stimulus.type == "negativ") %>%                                 # dont forget to pick stymulus type
  #   spread(.id, VAS_Resp)
  # 
  # t.test(Unic_merged_spread_Neg$Unic_CTRL_Instr, Unic_merged_spread_Neg$Unic_CTRL_Solo, na.rm = TRUE)
  # t.test(Unic_merged_spread_Neg$Unic_OGL_Instr, Unic_merged_spread_Neg$Unic_OGL_Solo, na.rm = TRUE)
  # t.test(Unic_merged_spread_Neg$Unic_OGL_Instr, Unic_merged_spread_Neg$Unic_CTRL_Instr, na.rm = TRUE)
  # t.test(Unic_merged_spread_Neg$Unic_OGL_Solo, Unic_merged_spread_Neg$Unic_CTRL_Solo, na.rm = TRUE)

## Function prepair data for analyses
prepaire_merged_func <- function(Stim_type){
  Unic_merged %>%
    filter(!is.na(VAS_Resp)) %>%                                           # some files had only NA on VAS_Resp and VAS_RT
    select(.id, ID, Subj_id, 
           Stimuli.order, MarkerStimuli, Stimulus.type, 
           VAS_Resp, VAS_RT) %>%
    dplyr::rename(Cond = .id) %>% 
    filter(Stimulus.type == Stim_type) %>%                                 # dont forget to pick stymulus type
    mutate(Cond = as.factor(Cond))                                         # tunr to factor for aov family functions
}

Unic_merged_Neg <- prepaire_merged_func("negativ")
Unic_merged_Neu <- prepaire_merged_func("neutru")
Unic_merged_Poz <- prepaire_merged_func("pozitiv")


## Anova and Post-Hoc  - NEGATIV
# Stimulus type
cat("### Negativ")

# Normality
cat("#### Normality Test")
Unic_merged_Neg %>%
  select(VAS_Resp) %>%                                                     # must select variables outside function 
  tadaatoolbox::tadaa_normtest(method = "shapiro")                         # , print = "markdown"  for Notebook

# Levene Test (p>.05 = homogeneity of variances)
cat("#### Levene Test")
Unic_merged_Neg %>%
  tadaatoolbox::tadaa_levene(data = ., VAS_Resp ~ Cond)                    # , print = "markdown"  for Notebook

# Anova
cat("#### Anova")
Unic_merged_Neg %>%
  #do(broom::glance(aov(.$VAS_Resp ~ .$Cond)))                             # regular anova do(broom::tidy(aov(.$VAS_Resp ~ .$Cond)))
  tadaatoolbox::tadaa_aov(data = ., VAS_Resp ~ Cond, type = 1)             # , print = "markdown"  for Notebook

# Post-Hoc 
cat("#### Post-Hoc Games Howell")
Unic_merged_Neg %>%
  # Tukey for equal variance 
  tadaatoolbox::tadaa_pairwise_tukey(data = ., VAS_Resp, Cond)             # , print = "markdown"  for Notebook
  # Games Howell does not assume equal variances
  #tadaatoolbox::tadaa_pairwise_gh(data = ., VAS_Resp, Cond)                # , print = "markdown"  for Notebook


## Anova and Post-Hoc  - NEUTRU
# Stimulus type
cat("### Neutru")

# Normality
cat("#### Normality Test")
Unic_merged_Neu %>%
  select(VAS_Resp) %>%                                                     # must select variables outside function 
  tadaatoolbox::tadaa_normtest(method = "shapiro")                         # , print = "markdown"  for Notebook

# Levene Test (p>.05 = homogeneity of variances)
cat("#### Levene Test")
Unic_merged_Neu %>%
  tadaatoolbox::tadaa_levene(data = ., VAS_Resp ~ Cond)                    # , print = "markdown"  for Notebook

# Anova
cat("#### Anova")
Unic_merged_Neu %>%
  #do(broom::glance(aov(.$VAS_Resp ~ .$Cond)))                             # regular anova do(broom::tidy(aov(.$VAS_Resp ~ .$Cond)))
  tadaatoolbox::tadaa_aov(data = ., VAS_Resp ~ Cond, type = 1)             # , print = "markdown"  for Notebook

# Post-Hoc 
cat("#### Post-Hoc Games Howell")
Unic_merged_Neu %>%
  # Tukey for equal variance 
  tadaatoolbox::tadaa_pairwise_tukey(data = ., VAS_Resp, Cond)             # , print = "markdown"  for Notebook
  # Games Howell does not assume equal variances
  #tadaatoolbox::tadaa_pairwise_gh(data = ., VAS_Resp, Cond)                # , print = "markdown"  for Notebook
```


## Plots with p values
```{r plot_unice, fig.height=7}
# by dataset
ggplot(Unic_merged, aes(x = Stimulus.type, y = VAS_Resp)) +
  geom_boxplot() +
  stat_summary(fun.data = mean_se,  colour = "darkred") +
  xlab("") +
  facet_wrap(~.id) +
  ggpubr::stat_compare_means(method = "t.test", 
                             label = "p.signif",                                         # to avoid scientific notation of very small p-values
                             #paired = TRUE, 
                             comparisons = list(c("negativ", "neutru")))  

# by Stimulus type
ggplot(Unic_merged, aes(x = .id, y = VAS_Resp)) +
  geom_boxplot() +
  stat_summary(fun.data = mean_se,  colour = "darkred") +
  xlab("") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~Stimulus.type) +
  ggpubr::stat_compare_means(method = "t.test",
                             label = "p.format",                                         # formated p-values
                             #paired = TRUE, 
                             comparisons = list(c("Unic_CTRL_Instr", "Unic_CTRL_Solo"),
                                                c("Unic_CTRL_Instr", "Unic_OGL_Instr"),
                                                c("Unic_CTRL_Solo", "Unic_OGL_Instr"),
                                                c("Unic_CTRL_Solo", "Unic_OGL_Solo"),
                                                c("Unic_OGL_Instr", "Unic_OGL_Solo"),
                                                c("Unic_CTRL_Instr", "Unic_OGL_Solo"))) 


# drop to CTRL vs OGL - by Stimulus type
Unic_merged %>%
  mutate(.id = case_when(.id %in% c("Unic_CTRL_Instr", "Unic_CTRL_Solo") ~ "Unic_CTRL",
                         .id %in% c("Unic_OGL_Instr", "Unic_OGL_Solo") ~ "Unic_OGL",
                         TRUE ~ as.character(.id))) %>%
    ggplot(aes(x = .id, y = VAS_Resp)) +
    geom_boxplot() +
    stat_summary(fun.data = mean_se,  colour = "darkred") +
    xlab("") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    facet_wrap(~Stimulus.type) +
    ggpubr::stat_compare_means(method = "t.test",
                               label = "p.format",                                         # formated p-values
                               #paired = TRUE, 
                               comparisons = list(c("Unic_CTRL", "Unic_OGL")))          

# drop to Instr vs Solo - by Stimulus type
Unic_merged %>%
  mutate(.id = case_when(.id %in% c("Unic_CTRL_Instr", "Unic_OGL_Instr") ~ "Unic_Instr",
                         .id %in% c("Unic_CTRL_Solo", "Unic_OGL_Solo") ~ "Unic_Solo",
                         TRUE ~ as.character(.id))) %>%
    ggplot(aes(x = .id, y = VAS_Resp)) +
    geom_boxplot() +
    stat_summary(fun.data = mean_se,  colour = "darkred") +
    xlab("") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    facet_wrap(~Stimulus.type) +
    ggpubr::stat_compare_means(method = "t.test",
                               label = "p.format",                                         # formated p-values
                               #paired = TRUE, 
                               comparisons = list(c("Unic_Instr", "Unic_Solo"))) 
```


# Download Data

```{r download_data}
Unic_merged %>% 
    select(-c(3:10)) %>%
    DT::datatable(                                  # excel downloadable  DT table
      extensions = 'Buttons',
      options = list(pageLength = 20,
                     scrollX='500px', 
                     dom = 'Bfrtip', 
                     buttons = c('excel', "csv")))
```




<!-- Session Info and License -->

<br>

# Session Info
```{r session_info, echo = FALSE, results = 'markup'}
sessionInfo()    
```

<!-- Footer -->
&nbsp;
<hr />
<p style="text-align: center;">A work by <a href="https://github.com/ClaudiuPapasteri/">Claudiu Papasteri</a></p>
<p style="text-align: center;"><span style="color: #808080;"><em>claudiu.papasteri@gmail.com</em></span></p>
&nbsp;
